### 2017-03-15 Writing/TrafficAnalysisOn6LoWPAN/conclusion.tex
Moved to this repository.

\section{Conclusion \label{conclusion}}

In this paper, we first reported an implementation issue of 802.15.4 Security in Contiki. Then we presented examples of application of Traffic Analysis over 6LoWPAN network. The first attack shows the content of encrypted ICMP messages could be leak through the packets features such as length and MAC destination. The second attack exploits the time differences in processing a PING Request to distinguish low performance devices used in IoT applications.

%PingProbe Attack
We proposed a new type of side channel attack, PingProbe, in the second half of the paper. This attack exploits the outlier data in PING packets response time to fingerprint different applications running on the target node. We then conducted proof of concept experiments and proved the effectiveness of the attack under our setting.

### 2017-03-15 Writing/TrafficAnalysisOn6LoWPAN/device.tex
Moved to this repository.

\section{Distinguish Hardware}\label{Sec:DistinguishDevice}
%Basic idea of this attack
IoT applications utilise a great variation of devices, with each having different processing power. Consequently, the time required for a specific operation could be exploited as an indicator to the hardware.

The time required to process a PING Request could therefore be exploited to perform such hardware distinguishing attack. Although the same attack could be conducted on various packets, PING is specifically practical and ideal due to:
\begin{enumerate}
	\item PING is processed in a highly predictable manner where nearly no computation is required; thus minimises the noise induced by data dependency.
	\item Support to PING is mandatory according to the standard\cite{rfc4443}, making the attack universally applicable.
\end{enumerate}

For our experiments, the PING Requests are initiated from a Linux machine connected into the 6LoWPAN through a border router. The ``-s 0'' option is specified for the `ping6' command in order to avoid exceeding the MTU of 6LoWPAN (127 bytes).

\subsection{Computing PING Response Time}\label{TimingWithContikiMAC}
%How to process the packets
%ContikiMAC
For energy preservation, Contiki adopts a Radio Duty Cycle (RDC) protocol called Contiki MAC\cite{ContikiMAC}. On receiver's side, Contiki MAC switches off the radio for most of the times and periodically wakes up for a short period for signal detection. If a signal is detected during the awaken period, the radio is kept on to receive a packet, followed by an acknowledgement sent to inform the sender. On sender's side, a packet is repeatedly transmitted until timed out or an acknowledgement is received.

Therefore when ContikiMAC is enabled by default, duplicated packets may be observed in the captured traffic. As an approximation to the PING Request processing time, we define PING Response Interval (PRI) as the time elapsed between the last PING Request and the first PING Response.

\begin{example}
%\paragraph{Example}

\AddFigure{fig/PRI.png}{PRI Example}{PRIExample}

\Cref{PRIExample} shows an example of packets captured by Wireshark\cite{Wireshark}. Duplicated PING Requests, No.$198$ to No.$203$, are replied by a single PING Response, No.$205$, matched by their \textit{seq} field ($16$). The PRI is therefore computed as the difference in time between No.$203$ (last PING Request) and No.$205$ (first PING Response) which is:
\begin{equation*}
PRI = 4.701468 - 4.684369 = 0.017099(s) = 17.099(ms)
\end{equation*}
\end{example}

\subsection{PRIs of TelosB and CC2538} \label{PRI_Devices}

\Cref{PRIs} shows the distributions of PRI collected on TelosB and CC2538. The bar on the right most represents the outliers in the data, with $9.43\%$ on TelosB are $\geq 19$ms and $2.60\%$ on CC2538 $\geq 12$ms respectively.

The result of \Cref{PRIs} suggests that TelosB and CC2538 can be easily distinguished by their PRIs, as they are tightly clustered around $17$ms for TelosB and $9.5$ms for CC2538 respectively.

\begin{figure}[ht!]
	\centering
	\begin{subfigure}{0.45\linewidth}
		\includegraphics[width=\linewidth]{fig/helloworld_sky.png}
		\subcaption{TelosB PRIs}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\includegraphics[width=\linewidth]{fig/helloworld_cc2538.png}
		\subcaption{CC2538 PRIs}
	\end{subfigure}

	\adjustbox{max width = \textwidth}
	{
		\begin{tabular}{|c|c|c|}
			\hline
			              & Mean (ms)     & Median (ms)   \\ \hline
			TelosB  & 33.82 & 17.03 \\ \hline
			CC2538 & 14.27         & 9.56          \\ \hline
		\end{tabular}
	}
	\caption{PRIs for different devices. \label{PRIs}}
\end{figure}

With respect to the outliers, one common cause is the processor being occupied by other tasks when a PING Request is received; thus delayed the processing of PING as illustrated by \Cref{PingProbeExample}. The portion of the outlier is hence affected by the payload on the node and the frequency of PING requests. We discuss further details of the outliers in \Cref{PingProbe}.

\AddFigure{fig/PingProbe_Session.png}{PRI prolonged by Sensor Reading}{PingProbeExample}

\subsection{Factors Affecting PRI} \label{PingDevice}

Despite the clear distinguishability suggested by \Cref{PRI_Devices}, there exists several practical factors the might affect the result.

802.15.4 Security\cite{802154} is a prominent factor to PRIs as it induces several cryptographic operations which are computationally heavy and hence could significantly increase the PRI. \Cref{802154SecPRI} illustrates the PRIs on the same devices when 802.15.4 Security is enabled. Flooding PING could also make an impact on measuring PRIs as it will overrun the low processing power of these resource constrained devices.

\begin{figure}[ht!]
	\centering
	\begin{subfigure}{0.4\textwidth}
	{
		\includegraphics[width=\textwidth]{fig/noncoresec_ping_telosb_sw.png}
	}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
	{
		\includegraphics[width=\textwidth]{fig/noncoresec_ping_telosb_hw.png}
	}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
	{
		\includegraphics[width=\textwidth]{fig/noncoresec_ping_cc2538_sw.png}
	}
	\end{subfigure}

	\adjustbox{max width = \textwidth}
	{
		\begin{tabular}{|c|c|c|}
			\hline
			              & Mean (ms)     & Median (ms)   \\ \hline
			TelosB HW AES & 37.20 & 30.77 \\ \hline
			TelosB SW AES & 105.19        & 87.40          \\ \hline
			CC2538 SW AES & 48.83         & 24.55          \\ \hline
		\end{tabular}
	}

	\caption{PRIs with 802.15.4 security\label{802154SecPRI}}
\end{figure}

### 2017-03-15 Writing/TrafficAnalysisOn6LoWPAN/fingerprint.tex
Moved to this repository.

\section{PingProbe: Application Fingerprint} \label{PingProbe}
\subsection{PRI Outliers}
%Observation of PRI outliers
In \Cref{Sec:DistinguishDevice}  we mentioned the phenomenon that processor occupied by other tasks may prolong the PRI as illustrated in  \Cref{PingProbeExample}. Extracting these outliers on a CC2538 running Helloworld example using threshold of $\geq 11$ms, we show the distribution of these prolonged PRIs in \Cref{PingProbeOutliers}. The histogram suggests the distribution has a strong discrete tendency, with multiple spikes presented in the graph.

\AddFigure{fig/helloworld_cc2538_outlier.png}{Histogram of PRI Outliers on CC2538 running Helloworld Example, using bins of $10$ms}{PingProbeOutliers}

We suppose the cause of such discreteness is that the delay is indeed caused by context switching in the kernel; therefore the impact of remaining time for the current task is indeed negligible. We further suppose the existence of multiple spikes is the result of switching from different contexts take different amounts of time. However, due to practical reasons, we found it difficult to experimentally confirm these hypothesises. Nevertheless, we consider this result as a strong indication that different states of the processor would result into different value of PRI, as illustrated in \Cref{PingProbeTheory}.

\begin{figure}[ht!]
	\center
	\begin{subfigure}{0.8\textwidth}
	{
		\center
		\includegraphics[width=\textwidth]{fig/PingProbe_temperature.png}
	}
	\subcaption{PRI when reading temperature sensor}
	\end{subfigure}
	\begin{subfigure}{0.8\textwidth}
	{
		\center
		\includegraphics[width=\textwidth]{fig/PingProbe_als.png}
		\subcaption{PRI when reading Ambient Light Sensor(ALS)}
	}
	\end{subfigure}
	\caption{An example of reading temperature and ALS sensor results into different PRI.}
	\label{PingProbeTheory}
\end{figure}

\subsection{PingProbe Attack}
%What is PingProbe
The PingProbe attack is proposed to exploit the distribution of PRI outliers as an indicator of different states of the processor. Considering the fact that many IoT applications perform routine operations, e.g. reading temperature sensor periodically, the constitution of processor states can be effectively viewed as a fingerprint to the application running on the node.

To verify the effectiveness of this attack, we performed a proof of concept experiment.

\subsubsection{Experiment Design}

Similar to many Traffic Analysis literature, we adopted the ``closed world'' setting for the experiment. Formally, our experiment simulates the following scenario:
\begin{itemize}
 \item The adversary is given the pre-knowledge of $n$ potential candidate applications, denote as $\mathbb{A} = \{A_1, A_2, ..., A_n\}$, and a target node running an unknown application $A_{x^*}$ where $A_{x^*} \in \mathbb{A}$. The adversary is also given the exact same hardware of target as well as the power to send PING packets to the target.
 \item The adversary eventually outputs $x$ as the guess of $x^*$. The attack is considered effective if $P(x = x^*) > \frac{1}{n}$.
\end{itemize}

In reality, such scenario can be motivated as an adversary trying to find out which product a victim might be using among those available on the market.

\subsubsection{Attack Description \label{PingProbeAttackManual}}

The attack can be described into 3 stages:

\begin{description}
	\item[Profiling]
	To set up the attack, the adversary collects PRIs for each application in $\mathbb{A}$. We denote the profiled traces as:
	\begin{equation}
		\mathbb{T}_p = \{T_1, T_2, ..., T_n\}
	\end{equation}
where each $T_i$ is collected by repetitively sending PING Request to the device running application $A_i$. Each trace $T_i$ contains multiple PRIs, denote as:
	\begin{equation}
		T_i = \{t_{(i,1)}, t_{(i,2)}, ..., t_{(i,{m_i})}\} %\text{ for } i \in [1,n]
	\end{equation}
	where $m_i$ is the number of PRIs in $T_i$.

	\item[Collecting Target Trace]
	To identify the secret application $A_{x^*}$, the adversary collects the PRIs on the target node running $A_{x^*}$. We denote the target trace as:
	\begin{equation}
		T_{x^*} = \{ t_{(x^*,1)}, t_{(x^*,2)}, ..., t_{(x^*,{m_x})}\} % PRI_^x_1, $%PRI^x_2, ..., PRI^x_{m_x}\}$.
	\end{equation}

	\item[Matching Fingerprint]
	The first step of matching fingerprint is to filter out the outliers in each trace by a threshold $\alpha$. In practice, such threshold can be easily determined from a trace. For example, for the data we have shown in \Cref{PRIs}, $11$ms is a reasonable choice of $\alpha$ for CC2538, as most PRIs are within the range of $[9,10.5]$(ms).

	We then filter each trace in $\mathbb{T}$ by keeping only PRIs $\geq \alpha$:
	\begin{equation}
		T^{\prime}_{i} = \{t \in T_i | t \geq \alpha\}
	\end{equation}

	We denote the set of filtered profiling traces as:
	\begin{equation}
		\mathbb{T}^{\prime}_{p} = \{ T^{\prime}_1, T^{\prime}_2, ..., T^{\prime}_n\}
	\end{equation}
	Indeed the filtering of profiled traces could also be pre-computed.

	We then apply the same filter on target trace:
	\begin{equation}
		T^{\prime}_{x^*} =  \{t \in T_{x^*} | t > \alpha\}
	\end{equation}

	The adversary then searches for $T^{\prime}_{x} \in \mathbb{T}^{\prime}_p$ that is statistically most similar to $T^{\prime}_{x^*}$. One way is to use Kolmogorov-Smirniov Distance (KS distance) as the measurement of statistical similarity. The adversary then  outputs the index of the trace with minimum KS-distance to the target, i.e. to search $T^{\prime}_x$ such that:
	\begin{equation}
		KSD( T^{\prime}_{x}, T^{\prime}_{x^*}) = min(\{KSD(T^{\prime}_i, T^{\prime}_{x^*}) | i \in [1,n]\})
	\end{equation}
	where $KSD(X, Y)$ represents the KS distance between two distributions $X$ and $Y$.	Finally the adversary outputs $x$ as the guess of $x^*$.
\end{description}

\subsubsection{Experiment Result}

We performed the experiments on CC2538. The ``closed world'' includes 10 applications which are:
\begin{itemize}
	\item \textbf{powertrace}: This Contiki example continuously records the power consumption on the node.
	\item \textbf{broadcast}: This Contiki example broadcasts a test ``Test'' string periodically.
	\item \textbf{sensorpayload} family: These applications periodically read the sensors and report the readings to the root node encrypted. There are $8$ instances of this type of applications corresponding to $8$ different combinations of temperature, light and voltage sensors.
\end{itemize}

The experiments are summarised in \Cref{PingProbeExpSum}.

PING requests are sent from a Linux host with the command  ``ping6 -s 0 -i 0.4''\footnote{No user defined data and with interval of $0.4$ second}. This frequency is chosen to maximise the speed of data generation without flooding the device.

For each application, we collected $2$ packet dumps (pcapng files) with each dump consists of $200000$ packets. Traces of nearly $7000$ PRIs are extracted from each dump.

We applied the threshold $\alpha = 11\text{(ms)}$ for CC2538. Roughly 1000 PRI outliers are filtered from each trace. \Cref{PingProbeApps} summarises the data we used in the experiment.

For each trace in the experiment, there is exactly one other trace among the 20 that is collected on the same application. We applied the KS distances method as described in \Cref{PingProbeAttackManual}, as summarised in \Cref{ksdistances}.

The experiments reported 13 out of 20 ($65$\%) traces have successfully matched to the correct application in our setting.

\subsubsection{Result Analysis}

Let null hypothesis be the attack has no effect, then each trace is uniformly matched to one in the other 19 traces.

Under the null hypothesis, the probability $P_0$ of having 13 out of 20 traces correctly matched is hence:
\begin{equation*}
P_0 = C^{13}_{20} (\frac{1}{19})^{13} (\frac{18}{19})^{7} \approx 1.262 * 10^{-12} \leq 0.01
\end{equation*}

Therefore we reject the null hypothesis and conclude that the experiments have shown positive result to the attack.

### 2017-03-15 Writing/TrafficAnalysisOn6LoWPAN/icmp.tex
Moved to this repository.

\section{Extract ICMP Messages}\label{ICMPAttack}
%What is ICMP?
ICMP messages are used for network maintenance.  Their typical usage include update routing information, network debugging, etc. Further details of ICMP messages are specified in \cite{rfc4443}.

%ICMP in Contiki?
As of the latest Contiki release 3.0, neither IPSec\cite{rfc4301} nor Secure ICMP Messages, i.e. ICMP Messages with encryption and authentication, are implemented; thus leaving 802.15.4 Security the only option for encrypting ICMP messages.

%Why ICMP matters?
Due to the nature of OSI layered model\cite{OSI}, ICMP messages are independent to upper layer applications; thus they hardly contain any information of the application data. Yet from a security perspective, leakage of ICMP messages may still endanger the network. For example, the identity of root node could guide a Denial of Service attack to amplify its damage, and being able filter some specific ICMP messages could be exploited to conduct other attacks such as the Wormhole attacks\cite{Wormhole}, etc.

%Observable ICMP messages in practice
We simulated a 6LoWPAN network constituted of multiple Wismote\cite{Wismote} nodes running Contiki broadcast and unicast examples, with 802.15.4 Security set to the highest level (CCM* with 128 bit MIC). The ICMP messages generated in our simulation includes:
\begin{itemize}
	\item \textbf{DAG Information Object (DIO)} \\
	DIO contains the 6LoWPAN global information. It could be periodically broadcasted for network maintenance, or unicasted to a new joining node as a reply to DIS (see below).
	\item \textbf{DAG Information Solicitation (DIS)} \\
	DIS is sent by a new started node to probe any existing 6LoWPANs. A DIO would be replied if the DIS is received by any neighbour nodes.
	\item \textbf{Destination Advertisement Object (DAO)} \\
	DAO is sent by a child node to its precedents\footnote{The 6LoWPAN DODAG topology is defined in \cite{rfc6550}.} to propagate its routing information.
	\item \textbf{Neighbour Solicitation (NS) and Neighbour Advertisement (NA)} \\
	NS and NA are the ARP replacement in IPv6, where NS queries a translation and NA answers one. In addition, they are also used for local link validity check.
	\item \textbf{Echo Request and Echo Response (PING)} \\
	Echo Request and Echo Response are well known as the PING packets. They are mostly used for diagnostic purposes, such as connectivity test or Round Trip Time (RTT) estimation. Echo Request may contain arbitrary user defined data and Echo Response simply echoes its corresponding request.
\end{itemize}

DIO/DIS/DAO and NS/NA are defined by \cite{rfc6550} and \cite{rfc6775} respectively. PING is defined by \cite{rfc2463}.

%Packet features
Our simulation shows that even though the exact content of these messages are hidden under the encryption provided by 802.15.4 Security, some of them are still distinguishable simply by their packet size and type of MAC destination. We summarise these features in \Cref{ICMPPacketFeature} where $x$ is the size of user defined data in PING packets.

Considering the fact that UDP is the relatively preferable Transportation Layer protocol in IoT applications than TCP, we also attached the packet features of UDP multicast and unicast at the bottom of \Cref{ICMPPacketFeature}.

There are two points may worth be noticed for \Cref{ICMPPacketFeature}:
\begin{itemize}
	\item Both DIO and NS can be sent in either broadcast or unicast. The broadcasted DIO is smaller than unicasted as it uses an abbreviated IPv6 multicast address ``ff02::1a''. Broadcasted NS uses another multicast address ``ff02::1:ff00:0'' which has the same length as unicast. However, both of them are mapped to the same ``0xffff'' Link Layer broadcast address in 802.15.4 MAC Header.
	%ICMP ECHO fragmentation in Wismote network.
	\item The size of PING may vary due to different user defined data. According to \cite{rfc4944}, any packet less than the 802.15.4 MTU, i.e. 127 bytes, should not be fragmented; however, we realised that Contiki fragments PING larger than $107$ bytes. We have not identified the cause but we consider this might be an implementation bug.
	%No NS and NA in Sky network.
	%\item Different ICMPv6 messages maybe observed on different platforms. In our experiments, there is no NS and therefore NA observed in WSN built with TelosB.
\end{itemize}

\begin{table}[ht!]
	\center
	\adjustbox{max width = \textwidth}
	{
		\begin{tabular}{|c|c|c|}
			\hline
			       & Packet Size (bytes) & Type of MAC Destination \\ \hline
			DIS    & 85                  & broadcast                       \\ \hline
			DIO  & 118/123                 & broadcast/unicast                       \\ \hline
			DAO    & 97                  & unicast                      \\ \hline
			NS & 87                  & broadcast/unicast                       \\ \hline
			NA     & 87                  & unicast                      \\ \hline
			PING   & $101+x$               & unicast                      \\ \hline
			UDP Multicast   & $85+x$                  & broadcast               \\ \hline
			UDP Unicast   & $107+x$                  & unicast                       \\ \hline
		\end{tabular}
	}
	\caption{ICMPv6 Packets in Simulated 6LoWPAN with noncoresec, where $x$ is size of user defined data}
	\label{ICMPPacketFeature}
\end{table}

%%UDP packet size.
%In practice, the captured traffic contains noises from upper layer applications. In case of the generally used UDP\cite{rfc768}, the packet features are summarised in \Cref{UDPPacketFeature}.
%
%\begin{table}[ht!]
%	\center
%	\adjustbox{max width = \textwidth}
%	{
%		\begin{tabular}{|c|c|c|}
%			\hline
%			       & Packet Size (bytes) & Type of MAC Destination \\ \hline
%			UDP Multicast   & $85+x$                  & broadcast                       \\ \hline
%			UDP Unicast   & $107+x$                  & unicast                       \\ \hline
%		\end{tabular}
%	}
%	\caption{UDP Packets in Simulated 6LoWPAN with noncoresec, where $x$ is size of user defined data}
%	\label{UDPPacketFeature}
%\end{table}

Observing \Cref{ICMPPacketFeature}, we realised 5 among the ICMP messages can be distinguished from all other packets, as summarised in \Cref{TAICMP}.

\begin{table}[ht!]
	\center
	\adjustbox{max width = \textwidth}
	{
		\begin{tabular}{|c|c|c|}
			\hline
			 & (Size, MAC Destination)\\ \hline
			DIS   & (85, broadcast)                       \\ \hline
			DAO   & (97, unicast)                       \\ \hline
			NS (broadcast)   & (87, broadcast)                       \\ \hline	
			NS (unicast)   & (87, unicast)                       \\ \hline
			NA 	& (87, unicast)                       \\ \hline
		\end{tabular}
	}
	\caption{Distinctive ICMP Packets}
	\label{TAICMP}
\end{table}

Other packets in \Cref{ICMPPacketFeature} may still be distinguishable in the encrypted traffic, unless the upper application happens to generate packets with the exact features.

Packet fragmentation may be a major factor that induces false result when applying this method. However it is likely to be avoided by most applications.

%\subsection{Tracking Root Node}
%\textbf{TO BE DONE...}

### 2017-03-15 Writing/TrafficAnalysisOn6LoWPAN/introduction.tex
Moved to this repository.

\section{Introduction}
Traffic Analysis is a well studied technique that breaches data confidentiality over Internet which exploits the side channel information, such as packet length and timing, to reveal contents in the encrypted traffic. As a matter of fact, Traffic Analysis techniques is often associated with malicious Internet behaviour such as privacy violation and mass surveillance.

%typically targeting protocols including HTTPS\cite{rfc2818} and SSL\cite{rfc6101}/TLS\cite{rfc5246}. This type of attacks works by correlating the encrypted contents to side channel information frequently omitted by cryptographic scheme designs, such as packet length, timing and any other unprotected meta data. Consequently, TA is often associated to Internet privacy violation and Mass Surveillance.

On the other hand, the development of Internet of Things (IoT) has linked ever more private data to the network, with radio being the most extensively used media for data transmission. These factors combined made Traffic Analysis posing even greater threat in the IoT context, as data are made widely open yet its content are juicier than ever.

%The extensive use of radio communication in exposed environment poses a great security challenge to IoT applications, especially against TA attacks as packets containing critical privacy data, e.g. driving information in Vehicular Ad Hoc Networks(VANETs)\cite{VANET} and daily life data in a smart house, can be easily eavesdropped and analysed by adversaries.

In this paper, we revised the applicability of Traffic Analysis in IoT applications by demonstrating simple examples capturing the concept. We made extensive use of Contiki OS\cite{Contiki} in our experiments to build demo applications. A 6LoWPAN\cite{rfc4944} network is built on two models of typical devices, namely TelosB\cite{TelosB} and CC2538\cite{CC2538}, as well as a network constructed by simulated Wismote\cite{Wismote}.

%Finally the paper structure
The paper is structured as follows. We first review the related literatures in \Cref{RelatedWork} and briefly report a security flaw in Contiki source code in \Cref{noncoresec}. We then present the first example that extracts ICMP\footnote{Specifically, the term ICMP we used in this paper refers to ICMPv6.}\cite{rfc4443} messages in \Cref{ICMPAttack}, followed by another example that reveals hardware information in \Cref{Sec:DistinguishDevice}. \Cref{PingProbe} proposes a new type of side channel attack, we named PingProbe, that fingerprints the application running on an IoT node. Finally we conclude the paper in \Cref{conclusion}.

\section{Related Work \label{RelatedWork}}
%Literatures about Traffic Analysis...
Traffic Analysis is a well studied subject in the Internet security and privacy community. \cite{WebSidechannel} summarised several scenario of side channel attacks against web applications, followed by \cite{PinpointWeb} which proposes the use of Mutual Information to pinpoint the potential points of information leakage. \cite{AppleMsg}, \cite{Language} and \cite{VideoTraffic} described attacks against encrypted text, voice and video traffic respectively, while \cite{SuggestBox} instantiated an attack against Google search box. \cite{HClassifier} and \cite{Peekaboo} studied different classifiers when adopting Machine Learning in Traffic Analysis. Different countermeasures are studied by \cite{TrafficMorphing}, \cite{HTTPOS} and \cite{FTE}.

%Literatures about 6LoWPAN security
With respect to 6LoWPAN security issues, \cite{6LoWPANAtk} summarises the known attacks in 6LoWPAN networks, including Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}. In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.

%To our knowledge, this is the first proposal of such type of our fingerprint attack in \Cref{PingProbe}.

### 2017-03-15 Writing/TrafficAnalysisOn6LoWPAN/noncoresec.tex
Moved to this repository.

\section{802.15.4 Security in Contiki\label{noncoresec}}
%Noncoresec
802.15.4 security in implemented by Noncoresec\cite{noncoresec} in the latest Contiki  (release 3.0). One hard-coded network wise key is the only keying model it supports in the current release. Due to the absence of IPSec\cite{rfc4301}, noncoresec is effectively the only applicable approach for securing part of the network metadata, such as IP headers and TCP/UDP headers.

%Platform
%Most of our studies are done on traffic data generated by Cooja simulator\cite{Contiki}. However, TelosB\cite{TelosB} and CC2538\cite{CC2538} are also used to gather performance critical data, such as timings.

%Reset Attack and Anti-Replay
However, examining the code, we realised two issues exist in the current implementation:
\begin{itemize}
	\item \textbf{Nonce Reusing} \\
	\Cref{NoncoresecNonce} illustrates the construction of nonce in 802.15.4 security with AES-128 in CTR and CCM mode. According to the specification\cite{802154}, for a specific source, the Frame Counter is the only variable field among different packets. Noncoresec implemented Frame Counter as a static variable initialised to 0 upon each reboot. Such implementation eventually leads to the nonce being reused upon each reset of  the device, which in many cases could cause severe leakage to the plaintext.

	\begin{figure}[th!]
	\centering
	\adjustbox{max width = \textwidth}
	{
		\begin{tabular}{|c|c|c|c|c|}
			\hline 
			1 (bytes) & 8              & 4             & 1              & 2             \\ \hline
			Flags      & Source Address & Frame Counter & Security Level & Block Counter \\ \hline
		\end{tabular}
	}
	\caption{Nonce Construction in 802.15.4 Security}
	\label{NoncoresecNonce}
	\end{figure}

	\item \textbf{Packet Lost by Anti-replay} \\
	Even though the incompatibility between Anti-replay and network key has been pointed out by \cite{802154SecIssues}, the noncoresec implementation has mitigated the issue by using an extra data structure recording the last Frame Counter from each source address. However, this approach also induces a problem that packets sent by a rebooted device will be labelled as replays and thus dropped by the receiver.
\end{itemize}

Although nonce reusing could be mitigated by initialising Frame Counter to a random value on each reboot, or recording the latest value on a permanent media such as flash memory,  yet the 4 byte space can hardly be considered cryptographically secure. Therefore a full solution may not be achieved without updating the nonce construction specified by the standard\cite{802154}.

The anti-replay issue is closely related to key management which remains an open question in the subject; thus would either be easily to solved without modifying the standard.  As a compromising solution, we simply recommend to disable the anti-replay feature and leave it to upper layer protocols such as TCP and CoAP.

### 2017-03-15 Writing/TrafficAnalysisOn6LoWPAN/src/helloworld.c

@@ -1,0 +1,8 @@
+#include <stdlib.h>
+#include <stdio.h>
+
+int main()
+{
+	printf("hellow,world.\n");
+	return 0;
+}

### 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/characters.tex
A New Hope

\section{Characters of IoT Traffics}
\begin{itemize}
	\item Less random data (ads, user input, etc).
	\item Different protocol suite (UDP instead TCP, hence no dynamic window.)
	\item Real time applications; hence less noise in timing.
\end{itemize}

Therefore more predictable packet features.

\begin{itemize}
	\item Different approaches: sophisticated techniques may not even required, e.g. machine learning, Mutual Information analysis. Leakage is easily observed.
\end{itemize}

Different scenarios have different leakages, e.g. the channels used in  TSCH could also be a leakage source.

Existing security protocols does not protect these side channel information.

### 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/countermeasure.tex
A New Hope

\section{Countermeasures}

The constrained environment makes the countermeasures difficult the practice, as they all greatly impacts the performance.

Relatively practical suggestions:
\begin{itemize}
	\item Packet length: Pad to MTU.
	\item Timing: Attempt to response on a fix timeslot.
	\item Protocol: Only enable PING for debugging.
	\item Others: insert dummy packets, etc.
\end{itemize}

However, each application / IoT system needs to tune the countermeasures.

Lower level protections should also be considered. For example physically protect the channel.

More importantly, product designers need to be aware of these potential security and privacy breach.

### 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/device.tex
A New Hope

@@
-\section{Distinguish Hardware}\label{Sec:DistinguishDevice}
-%Basic idea of this attack
-IoT applications utilise a great variation of devices, with each having different processing power.
-Consequently, the time required for a specific operation could be exploited as an indicator to the hardware.
+\section{Leakage on Device Information}
 
-The time required to process a PING Request could therefore be exploited to perform such hardware distinguishing attack.
-Although the same attack could be conducted on various packets, PING is specifically practical and ideal due to:
-\begin{enumerate}
-	\item PING is processed in a highly predictable manner where nearly no computation is required; thus minimises the noise induced by data dependency.
-	\item Support to PING is mandatory according to the standard\cite{rfc4443}, making the attack universally applicable.
-\end{enumerate}
+Different processors result into different response time to the same message; hence the response time can be correlated to the MCU.
 
-For our experiments, the PING Requests are initiated from a Linux machine connected into the 6LoWPAN through a border router.
-The ``-s 0'' option is specified for the `ping6' command in order to avoid exceeding the MTU of 6LoWPAN (127 bytes).
+\begin{itemize}
+	\item PING is a ideal feature in ICMP to launch this attack.
+\end{itemize}
 
-\subsection{Computing PING Response Time}\label{TimingWithContikiMAC}
-%How to process the packets
-%ContikiMAC
-For energy preservation, Contiki adopts a Radio Duty Cycle (RDC) protocol called Contiki MAC\cite{ContikiMAC}.
-On receiver's side, Contiki MAC switches off the radio for most of the times and periodically wakes up for a short period for signal detection.
-If a signal is detected during the awaken period, the radio is kept on to receive a packet, followed by an acknowledgement sent to inform the sender.
-On sender's side, a packet is repeatedly transmitted until timed out or an acknowledgement is received.
-
-Therefore when ContikiMAC is enabled by default, duplicated packets may be observed in the captured traffic.
-As an approximation to the PING Request processing time, we define PING Response Interval (PRI) as the time elapsed between the last PING Request and the first PING Response.
-
-\begin{example}
-%\paragraph{Example}
-
-\AddFigure{fig/PRI.png}{PRI Example}{PRIExample}
-
-\Cref{PRIExample} shows an example of packets captured by Wireshark\cite{Wireshark}.
-Duplicated PING Requests, No.$198$ to No.$203$, are replied by a single PING Response, No.$205$, matched by their \textit{seq} field ($16$).
-The PRI is therefore computed as the difference in time between No.$203$ (last PING Request) and No.$205$ (first PING Response) which is:
-\begin{equation*}
-PRI = 4.701468 - 4.684369 = 0.017099(s) = 17.099(ms)
-\end{equation*}
-\end{example}
-
-\subsection{PRIs of TelosB and CC2538} \label{PRI_Devices}
-
-\Cref{PRIs} shows the distributions of PRI collected on TelosB and CC2538.
-The bar on the right most represents the outliers in the data, with $9.43\%$ on TelosB are $\geq 19$ms and $2.60\%$ on CC2538 $\geq 12$ms respectively.
-
-The result of \Cref{PRIs} suggests that TelosB and CC2538 can be easily distinguished by their PRIs, as they are tightly clustered around $17$ms for TelosB and $9.5$ms for CC2538 respectively.
-
-\begin{figure}[ht!]
-	\centering
-	\begin{subfigure}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{fig/helloworld_sky.png}
-		\subcaption{TelosB PRIs}
-	\end{subfigure}
-	\begin{subfigure}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{fig/helloworld_cc2538.png}
-		\subcaption{CC2538 PRIs}
-	\end{subfigure}
-
-	\adjustbox{max width = \textwidth}
-	{
-		\begin{tabular}{|c|c|c|}
-			\hline
-			              & Mean (ms)     & Median (ms)   \\ \hline
-			TelosB  & 33.82 & 17.03 \\ \hline
-			CC2538 & 14.27         & 9.56          \\ \hline
-		\end{tabular}
-	}
-	\caption{PRIs for different devices. \label{PRIs}}
-\end{figure}
-
-With respect to the outliers, one common cause is the processor being occupied by other tasks when a PING Request is received; thus delayed the processing of PING as illustrated by \Cref{PingProbeExample}.
-The portion of the outlier is hence affected by the payload on the node and the frequency of PING requests.
-We discuss further details of the outliers in \Cref{PingProbe}.
-
-\AddFigure{fig/PingProbe_Session.png}{PRI prolonged by Sensor Reading}{PingProbeExample}
-
-\subsection{Factors Affecting PRI} \label{PingDevice}
-
-Despite the clear distinguishability suggested by \Cref{PRI_Devices}, there exists several practical factors the might affect the result.
-
-802.15.4 Security\cite{802154} is a prominent factor to PRIs as it induces several cryptographic operations which are computationally heavy and hence could significantly increase the PRI.
-\Cref{802154SecPRI} illustrates the PRIs on the same devices when 802.15.4 Security is enabled.
-Flooding PING could also make an impact on measuring PRIs as it will overrun the low processing power of these resource constrained devices.
-
-\begin{figure}[ht!]
-	\centering
-	\begin{subfigure}{0.4\textwidth}
-	{
-		\includegraphics[width=\textwidth]{fig/noncoresec_ping_telosb_sw.png}
-	}
-	\end{subfigure}
-	\begin{subfigure}{0.4\textwidth}
-	{
-		\includegraphics[width=\textwidth]{fig/noncoresec_ping_telosb_hw.png}
-	}
-	\end{subfigure}
-	\begin{subfigure}{0.4\textwidth}
-	{
-		\includegraphics[width=\textwidth]{fig/noncoresec_ping_cc2538_sw.png}
-	}
-	\end{subfigure}
-
-	\adjustbox{max width = \textwidth}
-	{
-		\begin{tabular}{|c|c|c|}
-			\hline
-			              & Mean (ms)     & Median (ms)   \\ \hline
-			TelosB HW AES & 37.20 & 30.77 \\ \hline
-			TelosB SW AES & 105.19        & 87.40          \\ \hline
-			CC2538 SW AES & 48.83         & 24.55          \\ \hline
-		\end{tabular}
-	}
-
-	\caption{PRIs with 802.15.4 security\label{802154SecPRI}}
-\end{figure}
+The processor can be considered a hint for the adversary to find out the model of target device.

### 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/introduction.tex
A New Hope

@@
 \section{Introduction}
-Traffic Analysis is a well studied technique that breaches data confidentiality over Internet which exploits the side channel information, such as packet length and timing, to reveal contents in the encrypted traffic.
-As a matter of fact, Traffic Analysis techniques is often associated with malicious Internet behaviour such as privacy violation and mass surveillance.
-
-%typically targeting protocols including HTTPS\cite{rfc2818} and SSL\cite{rfc6101}/TLS\cite{rfc5246}.
-This type of attacks works by correlating the encrypted contents to side channel information frequently omitted by cryptographic scheme designs, such as packet length, timing and any other unprotected meta data.
-Consequently, TA is often associated to Internet privacy violation and Mass Surveillance.
-
-On the other hand, the development of Internet of Things (IoT) has linked ever more private data to the network, with radio being the most extensively used media for data transmission.
-These factors combined made Traffic Analysis posing even greater threat in the IoT context, as data are made widely open yet its content are juicier than ever.
-
-%The extensive use of radio communication in exposed environment poses a great security challenge to IoT applications, especially against TA attacks as packets containing critical privacy data, e.g.
-driving information in Vehicular Ad Hoc Networks(VANETs)\cite{VANET} and daily life data in a smart house, can be easily eavesdropped and analysed by adversaries.
-
-In this paper, we revised the applicability of Traffic Analysis in IoT applications by demonstrating simple examples capturing the concept.
-We made extensive use of Contiki OS\cite{Contiki} in our experiments to build demo applications.
-A 6LoWPAN\cite{rfc4944} network is built on two models of typical devices, namely TelosB\cite{TelosB} and CC2538\cite{CC2538}, as well as a network constructed by simulated Wismote\cite{Wismote}.
-
-%Finally the paper structure
-The paper is structured as follows.
-We first review the related literatures in \Cref{RelatedWork} and briefly report a security flaw in Contiki source code in \Cref{noncoresec}.
-We then present the first example that extracts ICMP\footnote{Specifically, the term ICMP we used in this paper refers to ICMPv6.}\cite{rfc4443} messages in \Cref{ICMPAttack}, followed by another example that reveals hardware information in \Cref{Sec:DistinguishDevice}.
-\Cref{PingProbe} proposes a new type of side channel attack, we named PingProbe, that fingerprints the application running on an IoT node.
-Finally we conclude the paper in \Cref{conclusion}.
-
-\section{Related Work \label{RelatedWork}}
-%Literatures about Traffic Analysis...
-Traffic Analysis is a well studied subject in the Internet security and privacy community.
-\cite{WebSidechannel} summarised several scenario of side channel attacks against web applications, followed by \cite{PinpointWeb} which proposes the use of Mutual Information to pinpoint the potential points of information leakage.
-\cite{AppleMsg}, \cite{Language} and \cite{VideoTraffic} described attacks against encrypted text, voice and video traffic respectively, while \cite{SuggestBox} instantiated an attack against Google search box.
-\cite{HClassifier} and \cite{Peekaboo} studied different classifiers when adopting Machine Learning in Traffic Analysis.
-Different countermeasures are studied by \cite{TrafficMorphing}, \cite{HTTPOS} and \cite{FTE}.
-
-%Literatures about 6LoWPAN security
-With respect to 6LoWPAN security issues, \cite{6LoWPANAtk} summarises the known attacks in 6LoWPAN networks, including Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}.
-In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.
-
-%To our knowledge, this is the first proposal of such type of our fingerprint attack in \Cref{PingProbe}.
+\begin{itemize}
+	\item Motivation
+	\item Related Work
+\end{itemize}

### 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/plaintext.tex
A New Hope

\section{Leakage on Plaintext}

Examples.

\subsection{ICMP}

Types of ICMP messages can be distinguished by looking at the destination and/or source address together with packet length.

Knowing the ICMP messages may reveal information of the network topology.

\subsection{Sensor Readings with CoAP}

Reading different sensors results into different responding time which can be observed through the packets.

### 2017-03-21 Writing/TrafficAnalysisOn6LoWPAN/characters.tex
Removed temporary files. Update characters.tex.

@@
-\section{Characters of IoT Traffics}
+\section{Characteristics of Sensor Network Traffics}
+
+Due to the difference ecology of sensor network comparing to the Internet, the traffic data possesses several significant characteristics:
+
 \begin{itemize}
-	\item Less random data (ads, user input, etc).
-	\item Different protocol suite (UDP instead TCP, hence no dynamic window.)
-	\item Real time applications; hence less noise in timing.
+	\item Different protocol suites are proposed for sensor networks where different choices result into different traffic meta data.
+For example, when using ContikiMAC\cite{ContikiMAC} by default in the Contiki OS, the traffic meta data is very similar to those we have for the Internet, but in case of TSCH\cite{rfc7554} there will be additional channel information.
+	\item Unlike the dominant usage of TLS/SSL over Internet, encryption is considered on different layers for sensor networks, which affects the information that an eavesdropping adversary can learn.
+For instance the IPv6 header is public under DTLS\cite{rfc6347} but is hidden under 802.15.4 Security\cite{802154}.
+	\item Unreliable transmission is more preferable than reliable transmission on constrained devices.
+Specifically by replacing TCP with UDP, the channel loses features such as Acknowledgements(ACKs), Dynamic Window, etc, which increases the entropy in traffic meta data.
+Detection of plaintext signal would be eased without such features.
+	\item "Random" data, such as ads, does not exist in sensor networks.
+The random data naturally adds more noises to the signal of plaintext and hence served a countermeasure against traffic analysis attacks.
+Without such noises, signals of plaintext would be more easily detected.
+	%\item Real time applications; hence less noise in timing.
 \end{itemize}

### 2017-03-22 Writing/TrafficAnalysisOn6LoWPAN/characters.tex
Update

--- 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/characters.tex
@@
-\section{Characters of IoT Traffics}
-\begin{itemize}
-	\item Less random data (ads, user input, etc).
-	\item Different protocol suite (UDP instead TCP, hence no dynamic window.)
-	\item Real time applications; hence less noise in timing.
-\end{itemize}
+\section{Characteristics of Sensor Network Traffics}
 
-Therefore more predictable packet features.
+Due to the chracteristic ecology, traffic data in sensor networks need to be considered differently comparing to Internet.
 
-\begin{itemize}
-	\item Different approaches: sophisticated techniques may not even required, e.g. machine learning, Mutual Information analysis. Leakage is easily observed.
-\end{itemize}
+First of all, various protocol suites are proposed for sensor networks for different application.
+The choice of different protocols results into different traffic meta data.
+For example, when using ContikiMAC\cite{ContikiMAC} (default in Contiki OS), the traffic meta data is similar to those we have for the Internet, whereas for TSCH\cite{rfc7554} there will be additional channel information.
 
-Different scenarios have different leakages, e.g. the channels used in  TSCH could also be a leakage source.
+Secondly, unlike the dominant usage of TLS/SSL over Internet, encryption is considered on different layers for sensor networks, which also affects the information for an eavesdropping adversary.
+For instance the IPv6 header is visible for DTLS\cite{rfc6347} but is hidden when using 802.15.4 Security\cite{802154}.
 
-Existing security protocols does not protect these side channel information.
+Also that unreliable transmission is more preferable than reliable transmission for the constrained devices.
+This implies that, like UDP comparing to TCP, there might be no flow control which dynamically reassembles data into multiple packets.
+As a result, the actual size of data can be accurately observed from the packet size, which could provide more information to the adversary.
+
+The absence of "random" data, such as ads, is another factor.
+The random data naturally randomises the traffic and hence served a countermeasure against the attacks.
+The leakage would be more easily observed without these noise.
+
+%Real time applications; hence less noise in timing.
+In aspect of packet timings, the constrained devices have extremely limited processor frequency and their system entropies are also relatively lower; therefore the correlation between response latency and code execution time would be stronger than those of Internet servers.
+
+%More targets in addition to encrypted contents.
+
+%Therefore more predictable packet features.
+
+%\begin{itemize}
+%	\item Different approaches: sophisticated techniques may not even required, e.g. machine learning, Mutual Information analysis. Leakage is easily observed.
+%\end{itemize}
+
+%Different scenarios have different leakages, e.g. the channels used in  TSCH could also be a leakage source.
+
+%Existing security protocols does not protect these side channel information.

### 2017-03-23 Writing/TrafficAnalysisOn6LoWPAN/characters.tex
First draft for "Obeservations to Sensor Network Traffic".

--- 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/characters.tex
@@
-\section{Characters of IoT Traffics}
-\begin{itemize}
-	\item Less random data (ads, user input, etc).
-	\item Different protocol suite (UDP instead TCP, hence no dynamic window.)
-	\item Real time applications; hence less noise in timing.
-\end{itemize}
+\section{Observations to Sensor Network Traffic}
 
-Therefore more predictable packet features.
+Sensor network traffic has several different points comparing to Internet traffic.
 
-\begin{itemize}
-	\item Different approaches: sophisticated techniques may not even required, e.g. machine learning, Mutual Information analysis. Leakage is easily observed.
-\end{itemize}
+Various protocol stacks are proposed for different applications, some of them compete to each other.
+Different protocol generates different traffic meta data.
+For example, when using ContikiMAC\cite{ContikiMAC}\footnote{Default by Contiki OS.}, the types of traffic meta data is basically the same as of Internet; whereas for TSCH\cite{rfc7554} there will be additional channel information.
 
-Different scenarios have different leakages, e.g. the channels used in  TSCH could also be a leakage source.
+Unlike the dominant usage of TLS/SSL over Internet, encryption could be applied on different layers of the protocol stack.
+Information the adversary has access to is therefore differs for each setting.
+For instance, the IPv6 header is visible under DTLS\cite{rfc6347} but is hidden under 802.15.4 Security\cite{802154}.
 
-Existing security protocols does not protect these side channel information.
+Unreliable transmission is preferable than reliable one due to the constrained resources.
+This implies that there might be no flow control which dynamically reassembles data into multiple packets, for example comparing UDP to TCP.
+Without the reassembling, number of packets is constant and the actual size of data can be accurately observed from the packet size, which could provide more information to the adversary.
+Although packet fragmentation is also provided by IPv6 but this feature is usually disabled for various reasons.
+
+The absence of ``random" data, such as ads, is another major difference.
+The random data naturally randomises the traffic and hence complicates traffic analysis attacks.
+The leakage would be more easily observed without these noise.
+
+%Real time applications; hence less noise in timing.
+Timing measurements are also more accurate in sensor networks.
+Firstly, sensors are physically more close to each other and uses RF to communicate.
+This enables the adversary to remove the RTT noises by directly measure the server side response time of each packet.
+Secondly, the processor frequencies are also lower for the constrained devices and hence gives a better resolution on code execution time.
+
+%More targets in addition to encrypted contents.
+Finally, information other than encrypted contents could also be interested targets in case of sensor network.
+For example, network structure may help the adversary to launch DoS attacks more efficiently, and hardware information might be exploited to launch attacks against devices with specific vulnerabilities.
+
+%Therefore more predictable packet features.
+In summary, many natural of sensor network has only made it even more vulnerable against traffic analysis attacks.
+As a matter of fact, later in this paper, we demonstrate some examples of information leakage that can be directly observed through a sniffer, without utilising many sophisticated techniques developed for Internet such as machine learning classifiers.

### 2017-03-24 Writing/TrafficAnalysisOn6LoWPAN/plaintext.tex
Update

@@
-\section{Leakage on Plaintext}
+\section{Leakage on Encrypted Contents}
 
-Examples.
+A primary target of traffic analysis attacks is the plaintext in the encrypted contents.
+These attacks normally requires the adversary to have the pre-knowledge of a finite set of the potential plaintext; therefore each attack is strongly dependent to a specific application.
 
-\subsection{ICMP}
+However, as of this study, it would be inappropriate to make further assumptions about the data being transmitted due to the variety of sensor network applications.
+Without loss of generality, in this section we demonstrate the concept of attack through two examples.
+The first targets the standardised ICMP\cite{rfc4443} messages and the second aims to distinguish some market available devices.
 
-Types of ICMP messages can be distinguished by looking at the destination and/or source address together with packet length.
+\subsection{ICMP Leakage}
 
-Knowing the ICMP messages may reveal information of the network topology.
+Internet Control Message Protocol (ICMP) performs the management tasks in the network, such as connection establishment and routing information exchange.
+Contiki OS supports the following ICMP messages:
+
+\begin{itemize}
+	\item \textbf{DAG Information Object (DIO)} \\
+	DIO contains the 6LoWPAN global information. It could be periodically broadcasted for network maintenance, or unicasted to a new joining node as a reply to DIS (see below).
+	\item \textbf{DAG Information Solicitation (DIS)} \\
+	DIS is sent by a newly started node to probe any existing 6LoWPANs. A DIO would be replied if the DIS is received by any neighbour nodes.
+	\item \textbf{Destination Advertisement Object (DAO)} \\
+	DAO is sent by a child node to its precedents\footnote{The 6LoWPAN DODAG topology is defined in \cite{rfc6550}.} to propagate its routing information.
+	\item \textbf{Neighbour Solicitation (NS) and Neighbour Advertisement (NA)} \\
+	NS and NA are the ARP replacement in IPv6, where NS queries a translation and NA answers one. In addition, they are also used for local link validity check.
+	\item \textbf{Echo Request and Echo Response (PING)} \\
+	Echo Request and Echo Response are well known as the PING packets.
+They are mostly used for diagnostic purposes, such as connectivity test or Round Trip Time (RTT) estimation.
+Echo Request may contain arbitrary user defined data and Echo Response simply echoes its corresponding request.
+\end{itemize}
+
+Generally, ICMP messages can be protected by either using the optional secure ICMP messages instead or relying on lower layer encryption.
+Since Contiki OS does not have the former implemented, the 802.15.4 Security became the only option to protect the ICMP messages.
+
+Although leakage in ICMP messages does not directly lead to any leakage of application data, it would still provide the adversary with information such as the topology of network which could then be exploited to launch other attacks.
+
+We simulated a 6LoWPAN network with 802.15.4 Security enabled\footnote{Security level is set to the highest 0x07.}.
+In addition to ICMP messages, the nodes also generate some UDP packets with random data.
+We noticed that several ICMP messages can be identified simply by looking at the combination of packet size and the type of MAC Destination.
+We summarised the packet features in \Cref{IcmpPacketFeature}.
+We use $x$ to denote the size of user defined data in bytes.
+
+\begin{table}
+	\center
+	\input{tbl/icmpmeta.tex}
+	\caption{6LoWPAN Packet Features\label{IcmpPacketFeature}}
+\end{table}
+
+The first thing we noticed is that DIS is the smallest packet which has an unique 85 bytes. It means that it can be identified simply by the packet size.
+
+We also noticed that unicast packets can also be easily identified.
+Since PING and UDP unicast packets have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}, DAO can be uniquely identified by unicast packets of size $97$ bytes.
+For the same reason NA and NS can also be distinguished from other packets by filtering unicast packets of $87$ bytes.
+Considering NA is always sent as a response to NS, one can always identify the first packet being NS and the second NA.
+The similar strategy can also be applied on identifying unicast  DIO by associating with the previous DIS, although DIO is potentially obfuscated by carefully crafted PING or UDP packets.
+
+Even though broadcast packets other than DIS could also be obfuscated by carefully crafted user defined data, information might still leak through jointly inspecting the packets.
+Broadcast NS can be identified by the followed characteristic NA response; packets of 118 bytes that being periodically broadcasted are likely to be DIOs.
+%Types of ICMP messages can be distinguished by looking at the destination and/or source address together with packet length.
+%Knowing the ICMP messages may reveal information of the network topology.
 

### 2017-03-26 Writing/TrafficAnalysisOn6LoWPAN/plaintext.tex
Update

@@
 However, as of this study, it would be inappropriate to make further assumptions about the data being transmitted due to the variety of sensor network applications.
-Without loss of generality, in this section we demonstrate the concept of attack through two examples.
-The first targets the standardised ICMP\cite{rfc4443} messages and the second aims to distinguish some market available devices.
+Without loss of generality, in this section we demonstrate the concept of attacks through two examples.
 
-\subsection{ICMP Leakage}
+\paragraph{Example 1: Types ICMP Messages}
 
-Internet Control Message Protocol (ICMP) performs the management tasks in the network, such as connection establishment and routing information exchange.
+Internet Control Message Protocol(ICMP)\cite{rfc4443} performs the management tasks in the network, such as connection establishment and routing information exchange.
 Contiki OS supports the following ICMP messages:
@@
 
-The first thing we noticed is that DIS is the smallest packet which has an unique 85 bytes. It means that it can be identified simply by the packet size.
+The first thing we noticed is that DIS is the smallest packet which has an unique 85 bytes; hence it can be simply identified by the packet size.
 
-We also noticed that unicast packets can also be easily identified.
+We also noticed that most of the unicast packets can also be identified.
 Since PING and UDP unicast packets have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}, DAO can be uniquely identified by unicast packets of size $97$ bytes.
@@
 Considering NA is always sent as a response to NS, one can always identify the first packet being NS and the second NA.
-The similar strategy can also be applied on identifying unicast  DIO by associating with the previous DIS, although DIO is potentially obfuscated by carefully crafted PING or UDP packets.
+The similar strategy can also be applied on identifying unicast DIO as it is triggered by DIS, which can be unambiguously identified, as a response.
+However, unicast DIO could still be obfuscated by carefully crafted PING or UDP packets.
+PING is also likely to be recognised by its pair-wised appearance, as the echoed PING response would have nearly the same meta data as the original request.
 
-Even though broadcast packets other than DIS could also be obfuscated by carefully crafted user defined data, information might still leak through jointly inspecting the packets.
-Broadcast NS can be identified by the followed characteristic NA response; packets of 118 bytes that being periodically broadcasted are likely to be DIOs.
+Broadcast packets other than DIS are relatively obfuscated due to user defined data, but some of them might still be identified by inspecting multiple packets.
+For instance, broadcast NS can be identified by the followed characteristic NA response; packets of 118 bytes those are periodically broadcasted are likely to be DIOs.
 %Types of ICMP messages can be distinguished by looking at the destination and/or source address together with packet length.
@@
 
-\subsection{Sensor Readings with CoAP}
+\paragraph{Example 2: Sensor Readings with CoAP}
+%Reading different sensors results into different responding time which can be observed through the packets.
+CoAP\cite{rfc7252} is a protocol designed for constraied devices that provides an universal interface for accessing resources.
+Our second example demonstrates a realistic case where a node with multiple sensors using CoAP\cite{rfc7252} to provide the measurements.
 
-Reading different sensors results into different responding time which can be observed through the packets.
+CC2538 is the platform for our experiments.
+We combined the code in er-rest-example and cc2538-demo of Contiki OS to implement the sensor node.
+Three resources are implemented, namely are Vdd, temperature and Ambient Light Sensor (ALS).
+
+Our experiments showed that ALS readings can be distinguished from others by inspecting the response latency, despite the fact that we have carefully crafted any other traffic meta data, including URIs and data representations, to be uniform.
+
+\begin{table}
+	\center
+	\input{tbl/coapsensors.tex}
+	\caption{CoAP Response Latency for Sensor Readings on CC2538\label{CoapTiming}}
+\end{table}
+
+Our data is summarised in \Cref{CoapTiming}. Vdd and temperature readings take roughly the same amount of time. However, ALS readings take nearly $2$ms longer and hence can be easily distinguished.
+
+To summarise, the above examples confirmed the applicability of classic traffic analysis attacks in case sensor networks.
+The leakages are significant enough to be observed without utilising any sophisticated analytical tools.

### 2017-03-27 Writing/device.tex
Update

\section{Leakage on Device Information}

%Different processors result into different response time to the same message; hence the response time can be correlated to the MCU.

Hardware information is generally not considered to be an interested target in Internet traffic analysis attacks. However, in case of sensor network, such 
information could be valuable. For example, hardware information might be exploited to identify devices with specific vulnerabilities, or to be used as an indicative information for other attacks.

Although packets are generally considered to be hardware independent, there are still ways the hardware information could leak. An obvious example is that, when default MAC address is used, one can be immediately look up the manufacturer of using the Burned-In Address (BIA)\cite{BIA}.

Different driver implementations is also a factor. Among the platforms we tested, we realised that TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.}, whereas CC2538 is capable of handling packets even up to 160 bytes; therefore an adversary can immediately rule out TelosB if she/he sees a packet larger than 127 bytes.

%Now it comes to PING.

%\begin{itemize}
%	\item PING is a ideal feature in ICMP to launch this attack.
%\end{itemize}

%The processor can be considered a hint for the adversary to find out the model of target device.

### 2017-03-28 Writing/plaintext.tex
Improved readability...

\section{Leakage on Encrypted Contents}

%A primary target of traffic analysis attacks is the plaintext in the encrypted contents. These attacks normally requires the adversary to have the pre-knowledge of a finite set of the potential plaintext; therefore each attack is strongly dependent to a specific application.

Many traffic analysis attacks rely heavily on pre-knowledge of communication contents. However, as of this study, it would be inappropriate to make further assumptions about the data being transmitted due to the variety of sensor network applications. Without loss of generality, in this section, we study   two cases of relatively mature standards in the community, namely ICMPv6 and CoAP, respectively.

\paragraph{Types of ICMP Messages}

Internet Control Message Protocol(ICMP)\cite{rfc4443} performs the management tasks in the network, such as link establishment and routing information exchange. Contiki OS supports the following ICMP messages:

\begin{itemize}
	\item \textbf{DAG Information Object (DIO)} \\
	DIO contains the 6LoWPAN global information. It could be periodically broadcasted for network maintenance, or unicasted to a new joining node as a reply to DIS (see below).
	\item \textbf{DAG Information Solicitation (DIS)} \\
	DIS is sent by a newly started node to probe any existing 6LoWPANs. A DIO would be replied if the DIS is received by any neighbour nodes.
	\item \textbf{Destination Advertisement Object (DAO)} \\
	DAO is sent by a child node to its precedents\footnote{The 6LoWPAN DODAG topology is defined in \cite{rfc6550}.} to propagate its routing information.
	\item \textbf{Neighbour Solicitation (NS) and Neighbour Advertisement (NA)} \\
	NS and NA are the ARP replacement in IPv6, where NS queries a translation and NA answers one. In addition, they are also used for local link validity check.
	\item \textbf{Echo Request and Echo Response (PING)} \\
	Echo Request and Echo Response are well known as the PING packets. They are mostly used for diagnostic purposes, such as connectivity test or Round Trip Time (RTT) estimation. Echo Request may contain arbitrary user defined data and Echo Response simply echoes its corresponding request.
\end{itemize}

Generally, ICMP messages can be protected by either using the secure ICMP messages, or relying on lower layer encryption. Since Contiki OS does not have the former implemented, 802.15.4 Security became the only option currently.

Although leakage in ICMP messages does not directly lead to any breach of application data, it would still be harmful by providing the adversary with information including network topology. These informations could then be exploited to, say, identify critical targets of DoS attacks.

We simulated a 6LoWPAN network with 802.15.4 Security enabled\footnote{Security level is set to the highest 0x07.}. The nodes are configured to also generate random UDP packets.

Despite the ICMP messages are encrypted by 802.15.4 Security, our experiment shows that several ICMP messages can still be identified by the packet size and MAC destination.

\Cref{IcmpPacketFeature} summarises the packet features. $x$ to denotes the size of user defined data in bytes.

\begin{table}
	\center
	\input{tbl/icmpmeta.tex}
	\caption{6LoWPAN Packet Features\label{IcmpPacketFeature}}
\end{table}

%First of all, a DIS has the unique smallest packet size of 85 bytes, indicating it can be easily identified.

Among the unicast packets, since PING and UDP have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}, DAO can therefore uniquely identified as unicast packets of $97$ bytes.

For the same reason NA and unicast NS can also be distinguished from other packets by filtering packets of $87$ bytes. Considering NA is sent as a response to NS according to the protocol, one can always identify the first being NS and second NA.

Similarly, unicast DIO can be identified as the 123 bytes packet followed by DIS, where the later has a unique 85 bytes size. However, there is a potential of false positive induced by carefully crafted PING or UDP packets.

PING could be recognised by its pair-wised appearance, as the response would have nearly the same meta data as the original request, except the exchanged source and destination.

For broadcast packets, DIS can be easily identified by its unique 85 bytes packet size. Others like broadcast NS can be identified by the followed characteristic NA response; and packets of 118 bytes those are periodically broadcasted are likely to be DIOs.

In summary, among all the packets, DAO, NA, NS, DIS can be identified with certain. DIO and PING cannot be certainly identified by they both have significant characters. Notice that the above contained all ICMPv6 messages supported; therefore UDP packets can be reversely filtered, although in some cases mixed with DIO and PING.

\paragraph{Sensor Readings with CoAP}

CoAP\cite{rfc7252} is a protocol designed for constraied devices that provides an universal interface for accessing resources. CoAPs is the secure version which stands for CoAP with DTLS.

Due to the different physical characters of sensors, there could be a variance of time when reading the measurements. The idea is to investigate whether such variance can be observed through the packet response latency.

We implemented the experiment on CC2538, using all three sensors from ``cc2538-demo", namely Vdd, temperature and Ambient Light Sensor (ALS). We used CoAP from the ``er-rest-example" in the Contiki OS source code, as there is no CoAPs implementation available.

Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result would hold even in case of CoAPs.

We have carefully crafted other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.

\begin{table}
	\center
	\input{tbl/coapsensors.tex}
	\caption{CoAP Response Latency for Sensor Readings on CC2538\label{CoapTiming}}
\end{table}

\Cref{CoapTiming} summarises the result. It is shown that ALS takes about $2$ms longer and hence can be easily distinguished. Vdd and temperature might be difficult to distinguish by response latency as they have similar results.

%To summarise, the above examples confirmed the applicability of classic traffic analysis attacks in case sensor networks. The leakages are significant enough to be observed without utilising any sophisticated analytical tools.

### 2017-03-28 Writing/device.tex
Update.

@@
 
-Hardware information is generally not considered to be an interested target in Internet traffic analysis attacks. However, in case of sensor network, such 
-information could be valuable. For example, hardware information might be exploited to identify devices with specific vulnerabilities, or to be used as an indicative information for other attacks.
+Hardware informations are generally not considered interested in Internet traffic analysis attacks. In case of sensor network, such 
+information might become be valuable.
+For example, hardware information might be exploited to identify devices with specific vulnerabilities, or can be used as a hint of what the target does and hence breaches the communication.
 
-Although packets are generally considered to be hardware independent, there are still ways the hardware information could leak.
-An obvious example is that, when default MAC address is used, one can be immediately look up the manufacturer of using the Burned-In Address (BIA)\cite{BIA}.
+Although network protocols are generally implemented independently to hardware, there are still ways the information could leak through the traffic meta data.
+For instance, when the default MAC address of a device is used, one can be immediately look up the manufacturer by the Burned-In Address (BIA)\cite{BIA}.
 
-Different driver implementations is also a factor.
-Among the platforms we tested, we realised that TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.}, whereas CC2538 is capable of handling packets even up to 160 bytes; therefore an adversary can immediately rule out TelosB if she/he sees a packet larger than 127 bytes.
+Different driver implementations may also leak.
+Among the platforms we tested, we realised that TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.}; whereas CC2538 is capable of handling packets even up to 160 bytes.
+Therefore an adversary can immediately rule out TelosB when any packet larger than 127 bytes is observed.
 
 %Now it comes to PING.
+A more general leakage is the response latency to a specific message, as different processors would have different computational power and thus different time to process the message.
+The ICMP messages turns out to vulnerable targets against this attack for they are standardised and widely supported.
+For adveries capable to join the network, PING is especially ideal for such attacks, as
+\begin{itemize}
+	\item PING is mandatory according to the ICMP standard.
+\end{itemize}
 

### 2017-03-29 Writing/device.tex
Update

@@
 The ICMP messages turns out to vulnerable targets against this attack for they are standardised and widely supported.
-For adveries capable to join the network, PING is especially ideal for such attacks, as
-\begin{itemize}
-	\item PING is mandatory according to the ICMP standard.
-\end{itemize}
+PING is especially ideal for two reasons:
+\begin{enumerate}
+	\item It is mandatory in the ICMP standard.
+	\item It only swaps the source and destination address of the packet; thus minimises different code path in protocol processing.
+\end{enumerate}
+
+\begin{table}{r}{0.5\textwidth}
+	\center
+	\input{tbl/pingresponse}
+	\caption{PING Response Latency\label{PingResponse}}
+\end{table}
+
+\Cref{PingResponse} shows the PING response latency on CC2538 and TelosB. The result confirms that these devices can be distinguished by PING response latency.
 

### 2017-03-29 Writing/device.tex
Update

@@
 
-Hardware informations are generally not considered interested in Internet traffic analysis attacks. In case of sensor network, such 
-information might become be valuable.
-For example, hardware information might be exploited to identify devices with specific vulnerabilities, or can be used as a hint of what the target does and hence breaches the communication.
+The nature of sensor networks suggests that hardware information might became valuable in terms of security.
+For example, leakage of hardware information could help the adversary to identify devices with specific vulnerabilities, or provides hints of target's functionality which relates to the encrypted communication.
 

### 2017-03-30 Writing/device.tex
Update

@@
 
-Although network protocols are generally implemented independently to hardware, there are still ways the information could leak through the traffic meta data.
-For instance, when the default MAC address of a device is used, one can be immediately look up the manufacturer by the Burned-In Address (BIA)\cite{BIA}.
+Although network protocols are generally implemented independently to hardware, information could still leak through various ways.
+For instance, when the default MAC address is used, one can immediately look up the manufacturer by the Burned-In Address (BIA)\cite{BIA}.
 
-Different driver implementations may also leak.
-Among the platforms we tested, we realised that TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.}; whereas CC2538 is capable of handling packets even up to 160 bytes.
+Different driver implementations may also cause leakage.
+During the experiments, we realised that TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.}; whereas CC2538 is capable of handling packets even up to 160 bytes.
 Therefore an adversary can immediately rule out TelosB when any packet larger than 127 bytes is observed.
@@
 %Now it comes to PING.
-A more general leakage is the response latency to a specific message, as different processors would have different computational power and thus different time to process the message.
-The ICMP messages turns out to vulnerable targets against this attack for they are standardised and widely supported.
-PING is especially ideal for two reasons:
+A more general leakage is the response latency to a specific message, as different processors would have different computational power and thus different time to process a same message.
+The ICMP messages turns out to be suitable for this attack since they are standardised and thus universally supported.
+Among the ICMP messages, PING is especially ideal for two reasons:
 \begin{enumerate}

### 2017-03-31 Writing/introduction.tex
Update

\section{Introduction}
\textit{
\begin{itemize}
	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
\end{itemize}
}

### 2017-03-31 Writing/pktlen.tex
Update

--- 2017-03-28 Writing/plaintext.tex
@@
-\section{Leakage on Encrypted Contents}
+\section{Packet Length}
+\textit{
+\begin{itemize}
+	\item TLS Attacks still works and even better against DTLS due to protocol feature.
+\end{itemize}
+}
 
-%A primary target of traffic analysis attacks is the plaintext in the encrypted contents.
-These attacks normally requires the adversary to have the pre-knowledge of a finite set of the potential plaintext; therefore each attack is strongly dependent to a specific application.
-
-Many traffic analysis attacks rely heavily on pre-knowledge of communication contents.
-However, as of this study, it would be inappropriate to make further assumptions about the data being transmitted due to the variety of sensor network applications.
-Without loss of generality, in this section, we study   two cases of relatively mature standards in the community, namely ICMPv6 and CoAP, respectively.
-
-\paragraph{Types of ICMP Messages}
+\subsection{ICMP Leakage}
+%Plaintext recovery.
+%\begin{itemize}
+%	\item The attack combines packet length with MAC address information.
+%	\item Works on 802.15.4 Security. No need for DTLS (ICMP is plaintext when DTLS.)
+%\end{itemize}
 
@@
 
-\paragraph{Sensor Readings with CoAP}
-
-CoAP\cite{rfc7252} is a protocol designed for constraied devices that provides an universal interface for accessing resources. CoAPs is the secure version which stands for CoAP with DTLS.
-
-Due to the different physical characters of sensors, there could be a variance of time when reading the measurements.
-The idea is to investigate whether such variance can be observed through the packet response latency.
-
-We implemented the experiment on CC2538, using all three sensors from ``cc2538-demo", namely Vdd, temperature and Ambient Light Sensor (ALS).
-We used CoAP from the ``er-rest-example" in the Contiki OS source code, as there is no CoAPs implementation available.
-
-Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result would hold even in case of CoAPs.
-
-We have carefully crafted other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.
-
-\begin{table}
-	\center
-	\input{tbl/coapsensors.tex}
-	\caption{CoAP Response Latency for Sensor Readings on CC2538\label{CoapTiming}}
-\end{table}
-
-\Cref{CoapTiming} summarises the result.
-It is shown that ALS takes about $2$ms longer and hence can be easily distinguished.
-Vdd and temperature might be difficult to distinguish by response latency as they have similar results.
-
-%To summarise, the above examples confirmed the applicability of classic traffic analysis attacks in case sensor networks.
-The leakages are significant enough to be observed without utilising any sophisticated analytical tools.
+\subsection{Hardware Leakage}
+%Gain hardware information.
+%\begin{itemize}
+%	\item Some devices can handle longer packets, some can't.
+%	\item Works on both 802.15.4 Security and DTLS.
+%\end{itemize}
+Sometimes the packet length could also leak hardware information, mostly due to hardware limitations or different drivers.
+For instance, TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.} whereas CC2538 handles packets even up to 160 bytes.
+Therefore an adversary can immediately rule out TelosB whenever a packet larger than 127 bytes processed by the target.

### 2017-03-31 Writing/rsptime.tex
Update

--- 2017-03-28 Writing/plaintext.tex
@@
-\section{Leakage on Encrypted Contents}
-
-%A primary target of traffic analysis attacks is the plaintext in the encrypted contents.
-These attacks normally requires the adversary to have the pre-knowledge of a finite set of the potential plaintext; therefore each attack is strongly dependent to a specific application.
-
-Many traffic analysis attacks rely heavily on pre-knowledge of communication contents.
-However, as of this study, it would be inappropriate to make further assumptions about the data being transmitted due to the variety of sensor network applications.
-Without loss of generality, in this section, we study   two cases of relatively mature standards in the community, namely ICMPv6 and CoAP, respectively.
-
-\paragraph{Types of ICMP Messages}
-
-Internet Control Message Protocol(ICMP)\cite{rfc4443} performs the management tasks in the network, such as link establishment and routing information exchange.
-Contiki OS supports the following ICMP messages:
-
+\section{Response Time}
 \begin{itemize}
-	\item \textbf{DAG Information Object (DIO)} \\
-	DIO contains the 6LoWPAN global information. It could be periodically broadcasted for network maintenance, or unicasted to a new joining node as a reply to DIS (see below).
-	\item \textbf{DAG Information Solicitation (DIS)} \\
-	DIS is sent by a newly started node to probe any existing 6LoWPANs. A DIO would be replied if the DIS is received by any neighbour nodes.
-	\item \textbf{Destination Advertisement Object (DAO)} \\
-	DAO is sent by a child node to its precedents\footnote{The 6LoWPAN DODAG topology is defined in \cite{rfc6550}.} to propagate its routing information.
-	\item \textbf{Neighbour Solicitation (NS) and Neighbour Advertisement (NA)} \\
-	NS and NA are the ARP replacement in IPv6, where NS queries a translation and NA answers one. In addition, they are also used for local link validity check.
-	\item \textbf{Echo Request and Echo Response (PING)} \\
-	Echo Request and Echo Response are well known as the PING packets.
-They are mostly used for diagnostic purposes, such as connectivity test or Round Trip Time (RTT) estimation.
-Echo Request may contain arbitrary user defined data and Echo Response simply echoes its corresponding request.
+	\item TLS attacks still works and even better against DTLS for no RTT noise. 
 \end{itemize}
 
-Generally, ICMP messages can be protected by either using the secure ICMP messages, or relying on lower layer encryption.
-Since Contiki OS does not have the former implemented, 802.15.4 Security became the only option currently.
-
-Although leakage in ICMP messages does not directly lead to any breach of application data, it would still be harmful by providing the adversary with information including network topology.
-These informations could then be exploited to, say, identify critical targets of DoS attacks.
-
-We simulated a 6LoWPAN network with 802.15.4 Security enabled\footnote{Security level is set to the highest 0x07.}. The nodes are configured to also generate random UDP packets.
-
-Despite the ICMP messages are encrypted by 802.15.4 Security, our experiment shows that several ICMP messages can still be identified by the packet size and MAC destination.
-
-\Cref{IcmpPacketFeature} summarises the packet features. $x$ to denotes the size of user defined data in bytes.
-
-\begin{table}
-	\center
-	\input{tbl/icmpmeta.tex}
-	\caption{6LoWPAN Packet Features\label{IcmpPacketFeature}}
-\end{table}
-
-%First of all, a DIS has the unique smallest packet size of 85 bytes, indicating it can be easily identified.
-
-Among the unicast packets, since PING and UDP have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}, DAO can therefore uniquely identified as unicast packets of $97$ bytes.
-
-For the same reason NA and unicast NS can also be distinguished from other packets by filtering packets of $87$ bytes.
-Considering NA is sent as a response to NS according to the protocol, one can always identify the first being NS and second NA.
-
-Similarly, unicast DIO can be identified as the 123 bytes packet followed by DIS, where the later has a unique 85 bytes size.
-However, there is a potential of false positive induced by carefully crafted PING or UDP packets.
-
-PING could be recognised by its pair-wised appearance, as the response would have nearly the same meta data as the original request, except the exchanged source and destination.
-
-For broadcast packets, DIS can be easily identified by its unique 85 bytes packet size.
-Others like broadcast NS can be identified by the followed characteristic NA response; and packets of 118 bytes those are periodically broadcasted are likely to be DIOs.
-
-In summary, among all the packets, DAO, NA, NS, DIS can be identified with certain.
-DIO and PING cannot be certainly identified by they both have significant characters.
-Notice that the above contained all ICMPv6 messages supported; therefore UDP packets can be reversely filtered, although in some cases mixed with DIO and PING.
-
-\paragraph{Sensor Readings with CoAP}
+\subsection{Different Sensors}
+%Plaintext recovery.
+%\begin{itemize}
+%	\item Reading different sensors takes different time.
+%	\item Requirement: needs to identify CoAPS packets.
+%	\item Works on both 802.15.4 Seuciryt and DTLS, if the requirement is met. 
+%\end{itemize}
 
@@
 
-%To summarise, the above examples confirmed the applicability of classic traffic analysis attacks in case sensor networks.
-The leakages are significant enough to be observed without utilising any sophisticated analytical tools.
+\subsection{Different Hardware}
+Gain hardware information.
+\begin{itemize}
+	\item Different hardware has different response latency against the same message.
+	\item For 802.15.4: Requires additional information. Can be satisfied by the previous ICMP attack.
+	\item For DTLS: No requirement. The adversary can actively send a message, e.g. PING.
+\end{itemize}
+
+A more general leakage is the response latency to a specific message, as different processors would have different computational power and thus different time to process a same message.
+The ICMP messages turns out to be suitable for this attack since they are standardised and thus universally supported.
+Among the ICMP messages, PING is especially ideal for two reasons:
+\begin{enumerate}
+	\item It is mandatory in the ICMP standard.
+	\item It only swaps the source and destination address of the packet; thus minimises different code path in protocol processing.
+\end{enumerate}
+
+\begin{table}
+	\center
+	\input{tbl/pingresponse}
+	\caption{PING Response Latency\label{PingResponse}}
+\end{table}
+
+\Cref{PingResponse} shows the PING response latency on CC2538 and TelosB. The result confirms that these devices can be distinguished by PING response latency.
+
+\subsection{Running Code Fingerprint}
+Fingerprints the code running on a device, which leads to plaintext recovery.
+\begin{itemize}
+	\item Theory explained in \Cref{FingerprintTheory}.
+	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
+	\item Not for 802.15.4: adversary can't join the network.
+	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
+\end{itemize}
+
+\AddFigure{fig/PingProbe_Session.png}{How fingerprint works}{FingerprintTheory}

### 2017-04-01 Writing/rsptime.tex
Update

@@
 \subsection{Running Code Fingerprint}
-Fingerprints the code running on a device, which leads to plaintext recovery.
-\begin{itemize}
-	\item Theory explained in \Cref{FingerprintTheory}.
-	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
-	\item Not for 802.15.4: adversary can't join the network.
-	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
-\end{itemize}
+%Fingerprints the code running on a device, which leads to plaintext recovery.
+%\begin{itemize}
+%	\item Theory explained in \Cref{FingerprintTheory}.
+%	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
+%	\item Not for 802.15.4: adversary can't join the network.
+%	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
+%\end{itemize}
+The response time of packets can also be exploited to fingerprint the code running on a specific device. \Cref{FingerprintTheory} demonstrates the fundamental idea of the code fingerprinting attack.
 
-\AddFigure{fig/PingProbe_Session.png}{How fingerprint works}{FingerprintTheory}
+\begin{figure}
+	\center
+	\includegraphics[width=\textwidth]{fig/PingProbe_Theory.png}
+	\caption{Variations in PING Response Latency\label{FingerprintTheory}}
+\end{figure}
+
+%How it works
+
+%What can be the Request
+
+%Experiment Result

### 2017-04-02 Writing/rsptime.tex
Update

@@
 %\end{itemize}
-The response time of packets can also be exploited to fingerprint the code running on a specific device. \Cref{FingerprintTheory} demonstrates the fundamental idea of the code fingerprinting attack.
+The response time of packets can also be exploited to fingerprint the code running on a specific device.
 
@@
 %How it works
+\Cref{FingerprintTheory} illustrates two sensors receiving a service request.
+The first node was idle and hence responded immediately, whilst the second postponed the request for reading a sensor.
+As a result, the response time on the second sensor would appear to be longer than the first sensor.
+This scenario applies to the majority of constrained devices as they are mostly single-cored.
+
+The idea of code fingerprinting exploits such extended response time.
+Since different task extends the response time differently, distributions of extended response time can be used as fingerprint to the code running on the device.
+The statistical distance between the distributions can therefore used as an indicator for matching the fingerprints.
 
 %What can be the Request
+To effectively launch the attack, the requests needs to be actively sent by the adversary.
+Since code information is actually contained in extended  length of response time; therefore requests with short constant processing time are preferable as they induce less noise.
+
+In practice, the request can be instantiated by several messages defined in the sensor network protocols.
+PING is ideal as it induces only negligible computation and is compulsory according to the ICMP standard\cite{rfc4433}.
+Other options include Heartbeat message in DTLS\cite{rfc6520}, Reset in CoAP\cite{rfc7252}, etc.
 

### 2017-04-03 Writing/framework.tex
Revert...

\documentclass{article}

\input{packages.tex}
\input{macros.tex}

\title{Traffic Analysis On 6LoWPAN}
\author{Yan Yan}
\date{\today}

\begin{document}

\maketitle

%\tableofcontents
\section{Introduction}

\begin{itemize}
	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
\end{itemize}

\section{Packet Length}
\begin{itemize}
	\item TLS Attacks still works and even better against DTLS due to protocol feature.
\end{itemize}

\subsection{ICMP Leakage}
Plaintext recovery.
\begin{itemize}
	\item The attack combines packet length with MAC address information.
	\item Works on 802.15.4 Security. No need for DTLS (ICMP is plaintext when DTLS.)
\end{itemize}

\subsection{NEW: Hardware Leakage}
Gain hardware information.
\begin{itemize}
	\item Some devices can handle longer packets, some can't.
	\item Works on both 802.15.4 Security and DTLS.
\end{itemize}

\section{Response Time}
\begin{itemize}
	\item TLS attacks still works and even better against DTLS for no RTT noise. 
\end{itemize}

\subsection{Different Sensors}
Plaintext recovery.
\begin{itemize}
	\item Reading different sensors takes different time.
	\item Requirement: needs to identify CoAPS packets.
	\item Works on both 802.15.4 Seuciryt and DTLS, if the requirement is met. 
\end{itemize}

\subsection{Different Hardware}
Gain hardware information.
\begin{itemize}
	\item Different hardware has different response latency against the same message.
	\item For 802.15.4: Requires additional information. Can be satisfied by the previous ICMP attack.
	\item For DTLS: No requirement. The adversary can actively send a message, e.g. PING.
\end{itemize}

\subsection{Running Code Fingerprint}
Fingerprints the code running on a device, which leads to plaintext recovery.
\begin{itemize}
	\item Theory explained in \Cref{FingerprintTheory}.
	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
	\item Not for 802.15.4: adversary can't join the network.
	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
\end{itemize}

\AddFigure{fig/PingProbe_Session.png}{How fingerprint works}{FingerprintTheory}

\section{Conclusion}

\bibliographystyle{IEEEtran}
\bibliography{references,rfc}

%\appendix
%\section{appendix.tex}

\end{document}

### 2017-04-03 Writing/framework.tex
Update

@@
 
+A typical sensor network is built as described in \Cref{Protocols}.
+
+\begin{table}[!h]
+	\centering
+	\input{tbl/protocols.tex}
+	\caption{Protocol stack for sensor networks. (* are optional.)\label{Protocols}}
+\end{table}
+
 \begin{itemize}
 	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
+	\item Eavesdropping is easier for 6LoWPAN.
 \end{itemize}
 
+We discussed packet features independently in this paper but in practice they can be analysed jointly to reveal more leakage.
+
 \section{Packet Length}
-\begin{itemize}
-	\item TLS Attacks still works and even better against DTLS due to protocol feature.
-\end{itemize}
+Packet length is proven to be a major leakage source in Internet traffic analysis attacks.
+Since neither 802.15.4 Security nor DTLS protects packet length, we expect the same attacks would apply to 6LoWPAN traffic as well.
+Further more, we suppose 6LoWPAN applications are even more vulnerable to the leakage as there tends to be less noise in the traffic.
+
+Unreliable transmission is more preferable for 6LoWPAN applications for its low cost.
+Take UDP, the symbolic protocol for unreliable transmission, for example.
+UDP has no flow control; therefore packet size as well as number of packets are deterministic given the same application data.
+This effectively removed the natural noise induced by TCP packet reassembling.
+Although packet fragmentation is also provided by IPv6 but this feature is usually disabled for practical reasons.
+
+``Random" data, such as ads, is another major noise in Internet traffic which does not exist in 6LoWPAN traffic.
+The random data naturally randomises the traffic and hence complicates traffic analysis attacks.
+The leakage would be more easily observed without these noise.
 
@@
 
+\subsection{Countermeasure}
+Pad to MTU is recommended as it completely hides the length of plaintext. This method only induces slight overhead as 6LoWPAN MTU is small and requires only negligible computation.
+
+Unifying the drivers by strictly apply the standard MTU. Applications should be compatible to the standard anyway.
+
+Inserting dummy packets. More overhead to bandwidth and energy.
+
 \section{Response Time}
-\begin{itemize}
-	\item TLS attacks still works and even better against DTLS for no RTT noise. 
-\end{itemize}
+Response time is another major feature exploited in Internet traffic analysis attack.
+Again we would expect the same attacks can be applied to 6LoWPAN traffic and works even better than their counterparts against Internet traffic, as the accuracy of timing measurements can be greatly improved for 6LoWPAN traffic.
+
+Firstly, the devices are physically close to each other and uses RF to communicate. The adversary can remove the RTT noises by measure the packets on the server side.
+
+Secondly, performance of the constrained devices are low; hence gives a better resolution on timing code execution.
 
@@
 
+\subsection{Countermeasure}
+Two options:
+\begin{itemize}
+	\item Randomise response time: needs to be resilient to statistical analysis.
+	\item Threashold response time (discard or reply in a constant time): performance tradeoff. Recommended for unreliable transmissions.
+\end{itemize}
+
 \section{Conclusion}

### 2017-04-03 Writing/pktlen.tex
Update

@@
 \section{Packet Length}
-\textit{
-\begin{itemize}
-	\item TLS Attacks still works and even better against DTLS due to protocol feature.
-\end{itemize}
-}
+Packet length is proven to be a major leakage source in Internet traffic analysis attacks.
+Since neither 802.15.4 Security nor DTLS protects packet length, we expect the same attacks would apply to 6LoWPAN traffic as well.
+Further more, we suppose 6LoWPAN applications are even more vulnerable to the leakage as there tends to be less noise in the traffic.
 
+Unreliable transmission is more preferable for 6LoWPAN applications for its low cost.
+Take UDP, the symbolic protocol for unreliable transmission, for example.
+UDP has no flow control; therefore packet size as well as number of packets are deterministic given the same application data.
+This effectively removed the natural noise induced by TCP packet reassembling.
+Although packet fragmentation is also provided by IPv6 but this feature is usually disabled for practical reasons.
+
+``Random" data, such as ads, is another major noise in Internet traffic which does not exist in 6LoWPAN traffic.
+The random data naturally randomises the traffic and hence complicates traffic analysis attacks.
+The leakage would be more easily observed without these noise.
 \subsection{ICMP Leakage}
@@
 Therefore an adversary can immediately rule out TelosB whenever a packet larger than 127 bytes processed by the target.
+
+\subsection{Countermeasure}
+{\it
+Pad to MTU is recommended as it completely hides the length of plaintext. This method only induces slight overhead as 6LoWPAN MTU is small and requires only negligible computation.
+
+Unifying the drivers by strictly apply the standard MTU. Applications should be compatible to the standard anyway. 
+}

### 2017-04-03 Writing/rsptime.tex
Update

@@
 \section{Response Time}
-\begin{itemize}
-	\item TLS attacks still works and even better against DTLS for no RTT noise. 
-\end{itemize}
+Response time is another major feature exploited in Internet traffic analysis attack.
+Again we would expect the same attacks can be applied to 6LoWPAN traffic and works even better than their counterparts against Internet traffic, as the accuracy of timing measurements can be greatly improved for 6LoWPAN traffic.
+
+Firstly, the devices are physically close to each other and uses RF to communicate. The adversary can remove the RTT noises by measure the packets on the server side.
+
+Secondly, performance of the constrained devices are low; hence gives a better resolution on timing code execution.
 
@@
 \subsection{Different Hardware}
-Gain hardware information.
-\begin{itemize}
-	\item Different hardware has different response latency against the same message.
-	\item For 802.15.4: Requires additional information. Can be satisfied by the previous ICMP attack.
-	\item For DTLS: No requirement. The adversary can actively send a message, e.g. PING.
-\end{itemize}
+%Gain hardware information.
+%\begin{itemize}
+%	\item Different hardware has different response latency against the same message.
+%	\item For 802.15.4: Requires additional information. Can be satisfied by the previous ICMP attack.
+%	\item For DTLS: No requirement. The adversary can actively send a message, e.g. PING.
+%\end{itemize}
 

### 2017-04-04 Writing/rsptime.tex
Update

@@
 %Experiment Result
+We experimented the attack on a CC2538 to verify its practicability.
+PING is chosen as the protocol for request and response.
+We use the term PING Response Interval, PRI, to denote the response time between a PING request and PING response.
+
+Since the attack extracts the information contained in the extended response time of a specific request, the first problem is to see whether such extended response time can be filtered from normal ones.
+
+We collected the PRIs for the  Contiki example ``helloworld''.
+\Cref{HelloworldPri} shows the histogram of the PRIs, where values $\geq$12ms are collected at 12ms.
+The result shows that the majority of PRIs are clustered around 9.5ms, whilst a clear gap exists between the outliers, that is, the extended response time that could be exploited by the attack.
+
+The results suggests that for this device, CC2538, PING is normally responded in [9.0, 10.3]ms, which corresponds to the case of Sensor Node 1 in \Cref{FingerprintTheory}.
+We further plotted the outliers in \Cref{HelloworldPriOutliers}.
+We suppose the outliers are caused by PING request arriving when the processor was performing another task as described by the case of Sensor Node 2 in \Cref{FingerprintTheory}.
+The distribution shown in \Cref{HelloworldPriOutliers} is due to the fact that different tasks delays the PING request differently.
+
+\begin{figure}[!h]
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width=\textwidth]{fig/helloworld_cc2538.png}
+		\caption{PRIs of helloworld\label{HelloworldPri}}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width=\textwidth]{fig/helloworld_cc2538_outlier.png}
+		\caption{PRIs outliers of helloworld\label{HelloworldPriOutliers}}
+	\end{subfigure}
+\end{figure}
+
+We repeated the experiment for different applications on CC2538.
+For PRIs we collected on each application, the majority is clustered near 9.5ms and there exists a clear gap between the normal ones and the upper outliers.
+This implies that an adversary can draw a threshold by simply observing the distribution of PRIs.
+In our experiments the threshold is set to 12ms but we suppose other values that can separate the extended PRIs would also work for the attack.
+
+%Comparing the distribution.

### 2017-04-04 Writing/submission.tex
Update

\documentclass{river-journal}
\usepackage{rivps}
\usepackage[mtbold]{mathtime}

\usepackage{graphicx}
\usepackage{graphics}
\usepackage{subfigure}
\usepackage{cite}

% for alternatives, see appendix of manual

\newtheorem{guess}{Conjecture}

% bibliographies
\bibliographystyle{plain}
% also tested with natbib

\raggedbottom
\sloppy\par

\begin{document}
\begin{opening}
\title{A Sample Document}
\author{Yan Yan \& Elisabeth Oswald \& Theo Tryfonas}
\institute{University of Bristol,  \texttt{y.yan@bristol.ac.uk}}
\end{opening}

\runningtitle{Exploring Potential 6LoWPAN Traffic Side Channels}
\runningauthor{Y. Yan}

\subsection*{Abstract}
The Internet of Things has become a reality: small connected devices feature in everyday objects
including childrens' toys, TVs, fridges, heating control units, etc. Supply chains feature sensors
throughout, and significant investments go into researching next-generation healthcare, 
where sensors monitor wellbeing. A future in which sensors and other (small) devices interact to create sophisticated applications seems just around the corner . All of these applications have a fundamental need for security and privacy and thus we need to deploy cryptography as part an attempt to secure them. In this paper we explore a particular type of flaw, namely side channel information, on the protocol level. Our research investigates the potential for utilising packet length and timing information (both are easily obtained) to extract interesting information from a system, despite the use of cryptography.

\keywords{6LoWPAN, Side Channels, Traffic Analysis}

\section{Introduction}
The expression `Internet of Things' (IoT) can refer to a multitude of objects and protocols, which share that they have been purposefully designed for resource constraint environments. Whereas the typical TCP/IP network stack produces considerable overhead to achieve quality of service for applications that are based on it, the nature of many IoT `things' is such that a full implementation of it would not be practical. Often `things' are sensor, which are devices that have to function on little resources (most importantly power). Thus a whole host of new networking protocols have been developed over the years to cater for such resource constrained devices: 6LoWPAN is the `tiny' version of IPv6, UDP tends to be used instead of TCP/IP, DTLS can be used for end-to-end security or one can directly invoke 802.15.4. security which is part of 6LoWPAN, and finally CoAP(s) is the replacement for HTTP(s). Thus there are two options (802.15.4, and DTLS) to secure communications between the `things' and a server/gateway.

Implementing cryptography correctly and securely has proven to be a massive challenge as evidenced by the multitude of implementation attacks over the years. Triggered off by research that showed how to utilise additional information via timing and power side channels (CITE Kocher), many different flavours of side channel attacks were discovered over the last decade. Many attacks use phyiscal information (such as low level execution timings or power consumption) to recover secret keys, but many other attacks use protocol level information (such as packet lengths, types of packets or protocol messages) to recover information about plaintexts, devices in the network, or the network itself. 
There exists a considerable body of work in the context of conventional, i.e. HTTPs over TCP/IP network, but the applicability of (some) of these attacks in the context of a typical IoT protocol stack is lacking. This is the gap that we would like to address within this submission.

This paper is structured as follows: after reviewing some relevant attack paths for HTTPs over TCP/IP in the following subsection, we provide a brief introduction to the necessary protocol and network features in Section XXX.  We discuss the impact of packet length leakage in Section XX, followed by an analysis of the response time leakage in Section YY. We summarise our work in Section ZZ. 
\subsection{Related Work}

Write about attacks that exploit packet length and response times in the context of TCP/IP. Reflect on web applications and how the same might happen if more interesting applications might be deployed that involve IoT objects.

\section{A Typical IoT Protocol Stack}
A typical sensor network is built as described in \Cref{Protocols}.

\begin{table}[!h]
	\centering
	\input{tbl/protocols.tex}
	\caption{Protocol stack for sensor networks. (* are optional.)\label{Protocols}}
\end{table}

\begin{itemize}
	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
	\item Eavesdropping is easier for 6LoWPAN.
\end{itemize}

\section{Exploiting Packet Length Information}
\section{Exploiting Response Time Information}
\section{Conclusion}

\appendix

And this is my Appendix.

\subsection*{Appendix Subsection}

Some text.

%\nocite{*} % add all entries from sample.bib

\bibliography{references,rfc}
%\begin{thebibliography}{10}

%\end{thebibliography}

%\section*{Biography}
%
%\fbox{\parbox[t]{3cm}{Here is space for \\
%a photograph of \\
%the author. \\
%\vspace*{2cm}
%}}
%
%\medskip
%\noindent
%{\bf Author's name}. A short vitae can be included here.

\end{document}

### 2017-04-05 Writing/rsptime.tex
Update

--- 2017-04-03 Writing/rsptime.tex
@@
 
+\subsubsection{PING Response Time Distribution}
 %Experiment Result
+PING is one of the most known ideal protocol for this attack.
+We measured its response time on CC2538 running Contiki OS.
+Since Contiki MAC\cite{ContikiMAC} sends duplicated PING requests, we define the PING Response Interval, PRI, to be the time between a PING response and its last paired request.
+
+\Cref{ExamplePri} shows an example where Packet 205 and Packet 203 constitute a pair of PING packets, and their PRI is computed as their difference in time.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{fig/PRI_hl.png}
+	\caption{Example PRI\label{ExamplePri}}
+\end{figure}
+
+%Since the attack extracts the information contained in the extended response time of a specific request, the first problem is to see whether such extended response time can be filtered from normal ones.
+
+\Cref{HelloworldPri} shows the histogram of PRIs collected for ``helloworld'' example from Contiki OS.
+Values $\geq$12ms are collected at 12ms.
+The result shows that the majority of PRIs are clustered around 9.5ms, whilst a clear gap exists between the majority and the outliers.
+The majority, which roughly ranged [9.0, 10.3]ms, corresponds to the case of Sensor Node 1 in \Cref{FingerprintTheory}.
+
+\begin{figure}[!h]
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width=\textwidth]{fig/helloworld_cc2538.png}
+		\caption{PRIs of helloworld\label{HelloworldPri}}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width=\textwidth]{fig/helloworld_cc2538_outlier.png}
+		\caption{PRIs outliers of helloworld\label{HelloworldPriOutliers}}
+	\end{subfigure}
+	\caption{PRIs for helloworld}
+\end{figure}
+
+We further plotted the upper outliers, which mostly ranged from [12, 2000]ms, in \Cref{HelloworldPriOutliers}.
+We suppose these outliers corresponds to the case of Sensor Node 2 in \Cref{FingerprintTheory} which PING request arrived when the processor was performing another task.
+We suppose the distribution of PRI shown in \Cref{HelloworldPriOutliers} is due to different tasks delays the PING request differently.
+
+PRIs we collected on other applications showed the same characteristic.
+The majorities are clustered near a medium value.
+A clear proportion of outliers exists, leaving a clear gap between the majority.
+This implies that an adversary can easily draw a threshold by observing the distribution of PRIs to filter the ones corresponds to the extended response time.
+In our experiments the threshold is set to 12ms but any other values within the gap would also work.
+
+\subsubsection{Matching Fingerprint}
+
+%Comparing the distribution.
+As of the hypothesis, we expect an distinctive outlier distribution to be used as a fingerprint of each different application.

### 2017-04-05 Writing/rsptime.tex
Update

@@
 %\end{itemize}
-The response time of packets can also be exploited to fingerprint the code running on a specific device.
+The response time of packets could also be exploited to fingerprint the code running on a specific device.
+
+\subsubsection{Hypothesis}
+%How it works
+\Cref{FingerprintTheory} hypothesises two sensors receiving a service request.
+The first node was idle and hence responded immediately, whilst the second postponed the request for reading a sensor.
+As a result, the response time on the second sensor would appear to be longer than the first sensor.
+This scenario applies to the majority of constrained devices as they are mostly single-cored.
 
@@
 	\includegraphics[width=\textwidth]{fig/PingProbe_Theory.png}
-	\caption{Variations in PING Response Latency\label{FingerprintTheory}}
+	\caption{Variations in Response Time\label{FingerprintTheory}}
 \end{figure}
 
-%How it works
-\Cref{FingerprintTheory} illustrates two sensors receiving a service request.
-The first node was idle and hence responded immediately, whilst the second postponed the request for reading a sensor.
-As a result, the response time on the second sensor would appear to be longer than the first sensor.
-This scenario applies to the majority of constrained devices as they are mostly single-cored.
+Most sensors are programmed to run in a loop.
+The idea of code fingerprinting exploits the fact that each program delays the request differently; thus statistically each program results into a distinctive distribution of delayed response time.
 
-The idea of code fingerprinting exploits such extended response time.
-Since different task extends the response time differently, distributions of extended response time can be used as fingerprint to the code running on the device.
-The statistical distance between the distributions can therefore used as an indicator for matching the fingerprints.
+\begin{definition}
+	We refer the distribution of delayed response time as a \textbf{``fingerprint''} to the program running on the sensor node.
+\end{definition}
+
+We assume the adversary has the pre-knowledge of potential programs, together with a database of all their fingerprints.
+To identify an unknown program, the adversary collects its fingerprint and then searches the database for a match.
 
@@
 Since code information is actually contained in extended  length of response time; therefore requests with short constant processing time are preferable as they induce less noise.
-
 In practice, the request can be instantiated by several messages defined in the sensor network protocols.
@@
 
-\subsubsection{PING Response Time Distribution}
+\subsubsection{Extracting Fingerprint}
 %Experiment Result
-PING is one of the most known ideal protocol for this attack.
-We measured its response time on CC2538 running Contiki OS.
+We measured PING response time on CC2538 running Contiki OS.
 Since Contiki MAC\cite{ContikiMAC} sends duplicated PING requests, we define the PING Response Interval, PRI, to be the time between a PING response and its last paired request.
@@
 
-\Cref{HelloworldPri} shows the histogram of PRIs collected for ``helloworld'' example from Contiki OS.
+\Cref{HelloworldPri} shows the histogram of PRIs collected on ``helloworld'' example from Contiki OS.
 Values $\geq$12ms are collected at 12ms.
 The result shows that the majority of PRIs are clustered around 9.5ms, whilst a clear gap exists between the majority and the outliers.
-The majority, which roughly ranged [9.0, 10.3]ms, corresponds to the case of Sensor Node 1 in \Cref{FingerprintTheory}.
+The majority, roughly ranged [9.0, 10.3]ms, corresponds to the case of Sensor Node 1 in \Cref{FingerprintTheory}.
 
@@
 We suppose these outliers corresponds to the case of Sensor Node 2 in \Cref{FingerprintTheory} which PING request arrived when the processor was performing another task.
-We suppose the distribution of PRI shown in \Cref{HelloworldPriOutliers} is due to different tasks delays the PING request differently.
 
@@
 A clear proportion of outliers exists, leaving a clear gap between the majority.
-This implies that an adversary can easily draw a threshold by observing the distribution of PRIs to filter the ones corresponds to the extended response time.
+This implies that an adversary can easily draw a threshold by observing the whole distribution and then filter the extended ones out.
 In our experiments the threshold is set to 12ms but any other values within the gap would also work.
 
-\subsubsection{Matching Fingerprint}
+According to the hypothesis, the  distribution shown in \Cref{HelloworldPriOutliers} is due to different tasks delays the PING request differently. According to the hypothesis
 
+\subsubsection{Fingerprint Matching}
 %Comparing the distribution.
-As of the hypothesis, we expect an distinctive outlier distribution to be used as a fingerprint of each different application.
+Following the hypothesis, we expect a distinctive outlier PRI distribution for each different program running on the target device which can be used as a fingerprint to the program being ran.
+To identify an unknown program r

### 2017-04-05 Writing/rsptime.tex
Update

@@
 %How it works
-\Cref{FingerprintTheory} hypothesises two sensors receiving a service request.
-The first node was idle and hence responded immediately, whilst the second postponed the request for reading a sensor.
-As a result, the response time on the second sensor would appear to be longer than the first sensor.
-This scenario applies to the majority of constrained devices as they are mostly single-cored.
+\Cref{FingerprintTheory} illustrates two sensors receiving a same service request.
+Sensor Node 1 was idle and hence responded immediately, whilst Sensor Node 2 postponed the request for reading a sensor.
+From the aspect of packets, the response time on Sensor Node 2 would appear longer than that of Sensor Node 1.
 
@@
 
-Most sensors are programmed to run in a loop.
-The idea of code fingerprinting exploits the fact that each program delays the request differently; thus statistically each program results into a distinctive distribution of delayed response time.
+Most sensors are programmed in a loop; therefore the same code fragments are repeated through the life time of a sensor.
+Each code fragment takes different time to execute and hence extends response time differently.
+
+The code fingerprinting attack exploits this phenomenon by statically analysing the distribution of extended response time to reveal information of the program.
 
 \begin{definition}
-	We refer the distribution of delayed response time as a \textbf{``fingerprint''} to the program running on the sensor node.
+	We refer the distribution of extended response time as a \textbf{``fingerprint''} to the program running on the sensor node.
 \end{definition}
 
-We assume the adversary has the pre-knowledge of potential programs, together with a database of all their fingerprints.
-To identify an unknown program, the adversary collects its fingerprint and then searches the database for a match.
+For this attack, we assume the adversary has the pre-knowledge of potential programs, together with a database of all their fingerprints.
+To identify an unknown program running on target sensor, the adversary collects its fingerprint and then matches it to the database.
 
-%What can be the Request
-To effectively launch the attack, the requests needs to be actively sent by the adversary.
-Since code information is actually contained in extended  length of response time; therefore requests with short constant processing time are preferable as they induce less noise.
+To effectively launch the attack, the adversary also needs to be able to send the requests. Further more, requests with short predictable processing time are preferable as they induce less noise.
+
 In practice, the request can be instantiated by several messages defined in the sensor network protocols.
-PING is ideal as it induces only negligible computation and is compulsory according to the ICMP standard\cite{rfc4433}.
-Other options include Heartbeat message in DTLS\cite{rfc6520}, Reset in CoAP\cite{rfc7252}, etc.
+PING is exceptionally ideal as it is mandatory in the ICMP standard\cite{rfc4433} and has only negligible computation.
+Other options but not excluded are Heartbeat in DTLS\cite{rfc6520}, Reset in CoAP\cite{rfc7252}, etc.
 
 \subsubsection{Extracting Fingerprint}
-%Experiment Result
-We measured PING response time on CC2538 running Contiki OS.
-Since Contiki MAC\cite{ContikiMAC} sends duplicated PING requests, we define the PING Response Interval, PRI, to be the time between a PING response and its last paired request.
+The first task of the attack is to construct a fingerprint of a program. We experimented with PING on CC2538 running Contiki OS.
 
-\Cref{ExamplePri} shows an example where Packet 205 and Packet 203 constitute a pair of PING packets, and their PRI is computed as their difference in time.
+\Cref{ExamplePri} shows an example of captured packets.
+Contiki MAC\cite{ContikiMAC} sends duplicated PING requests.
+The response time, refers to PING Response Interval, PRI, is defined to be the time between a PING response and its last paired request.
+The highlighted Packet 205 and Packet 203 shows such an example.
 
@@
 
-\Cref{HelloworldPri} shows the histogram of PRIs collected on ``helloworld'' example from Contiki OS.
+\Cref{HelloworldPriNormal} shows the histogram of PRIs collected on the ``helloworld'' example from Contiki OS.
 Values $\geq$12ms are collected at 12ms.
-The result shows that the majority of PRIs are clustered around 9.5ms, whilst a clear gap exists between the majority and the outliers.
-The majority, roughly ranged [9.0, 10.3]ms, corresponds to the case of Sensor Node 1 in \Cref{FingerprintTheory}.
+The result shows that most PRIs are clustered around 9.5ms which consists with our result in \Cref{PingResponse}.
+The majority, roughly ranged [9.0, 10.3]ms, corresponds to the usual response time as depicted by Sensor Node 1 in \Cref{FingerprintTheory}.
 
@@
 		\includegraphics[width=\textwidth]{fig/helloworld_cc2538.png}
-		\caption{PRIs of helloworld\label{HelloworldPri}}
+		\caption{PRIs of helloworld\label{HelloworldPriNormal}}
 	\end{subfigure}
@@
 	\end{subfigure}
-	\caption{PRIs for helloworld}
+	\caption{helloworld PRIs\label{HelloworldPri}}
 \end{figure}
 
-We further plotted the upper outliers, which mostly ranged from [12, 2000]ms, in \Cref{HelloworldPriOutliers}.
-We suppose these outliers corresponds to the case of Sensor Node 2 in \Cref{FingerprintTheory} which PING request arrived when the processor was performing another task.
+We further plotted the upper outliers, mostly ranged [12, 2000]ms, in \Cref{HelloworldPriOutliers}.
+We suppose these outliers corresponds to the extended response time as depicted by Sensor Node 2 in \Cref{FingerprintTheory}.
+According to the hypothesis, the distribution described by \Cref{HelloworldPriOutliers} is the fingerprint of the ``helloworld'' example.
 
-PRIs we collected on other applications showed the same characteristic.
-The majorities are clustered near a medium value.
-A clear proportion of outliers exists, leaving a clear gap between the majority.
-This implies that an adversary can easily draw a threshold by observing the whole distribution and then filter the extended ones out.
+The result in \Cref{HelloworldPri} showed a clear gap between the usual PRIs and extended PRIs.
+In fact other applications we experimented also showed the same property.
+This implies that an adversary can easily draw a threshold by observing the whole PRI distribution and then filters the fingerprint.
 In our experiments the threshold is set to 12ms but any other values within the gap would also work.
-
-According to the hypothesis, the  distribution shown in \Cref{HelloworldPriOutliers} is due to different tasks delays the PING request differently. According to the hypothesis
 

### 2017-04-05 Writing/appendix.tex
Body draft completed.

\section{Fingerprint Experiment Programs}

\input{tbl/PingProbeExperiments.tex}

\section{Fingerprint Experiment Relative KS-Distances}

\input{tbl/ksdistance.tex}

### 2017-04-05 Writing/pktlen.tex
Body draft completed.

@@
 \subsection{Countermeasure}
-{\it
-Pad to MTU is recommended as it completely hides the length of plaintext. This method only induces slight overhead as 6LoWPAN MTU is small and requires only negligible computation.
+%{\it
+%Pad to MTU is recommended as it completely hides the length of plaintext. This method only induces slight overhead as 6LoWPAN MTU is small and requires only negligible computation.
+%
+%Unifying the drivers by strictly apply the standard MTU. Applications should be compatible to the standard anyway. 
+%}
+A general countermeasure to packet length leakage is padding, as studied in \cite{Peekaboo}. Although Padding to MTU is considered inefficient for Internet, it is recommended for 6LoWPAN as:
+\begin{itemize}
+	\item It completely hides the length of original plaintext.
+	\item 6LoWPAN has only a low MTU of 127 bytes; therefore the overhead is relatively acceptable.
+	\item It induces negligible computational overhead.
+\end{itemize}
 
-Unifying the drivers by strictly apply the standard MTU. Applications should be compatible to the standard anyway. 
-}
+%Resourceful applications can enhance the countermeasure by inserting dummy packets.
+
+With regard to the hardware leakage, we suggest strictly applying the standard MTU to eliminate the differences in drivers.
+Although there is a potential of performance downgrade, but it will also improve the compatibility Samong different devices.

### 2017-04-05 Writing/rsptime.tex
Body draft completed.

@@
 
-\subsection{Running Code Fingerprint}
+\subsection{Program Fingerprint}
 %Fingerprints the code running on a device, which leads to plaintext recovery.
@@
 %Comparing the distribution.
-Following the hypothesis, we expect a distinctive outlier PRI distribution for each different program running on the target device which can be used as a fingerprint to the program being ran.
-To identify an unknown program r
+We collected the fingerprints for three programs taken from the Contiki OS examples:
+\begin{description}
+	\item[broadcast] This is taken as it is from the example which periodically broadcasts a constant message.
+
+	\item[powertrace] This is taken as it is from the example which records the power consumption and broadcasts a constant message.
+
+	\item[Sensorpayload] This program is based on the ``er-rest-example'' embedded together with sensor accesses taken from ``cc2538-demo''.
+It captures a real case scenario where three different sensors, namely Temperature, VDD and ALS, are being access through CoAP.
+\end{description}
+
+Specifically for ``Sensorpayload'' we collected fingerprints for 8 different scenarios where different sensors are being accessed.
+For each program we independently collected 2 fingerprints for comparison.
+
+\Cref{FingerprintApps} summarises the total 20 fingerprints we collected for the experiment.
+
+During the experiments we realised that most of the fingerprints does not subject to any common distributions as expected; therefore we used Kolmogorov-Smirnov Distance as the statistics.
+\Cref{ksdistances} summarises the relative KS distances computed on each pair of fingerprints in our experiments.
+
+Although fingerprints collected on the same application basically failed to pass the Kolmogorov-Smirnov Test, we realised that their KS distance tends to be smaller comparing to fingerprints collected on different programs, as the \textbf{bold} cells marked in \Cref{ksdistances}.
+
+By matching fingerprints with the minimum KS distance, 13 out of 20 fingerprints in our experiments have successfully matched the paired one collected on the same program, which suggests a much better result than random matching.
+
+Further more the mismatch only occur among the ``Sensorpayload'' program and fingerprints collected on the same program still tends to have relatively low KS distances.
+Considering they share most of the code except a slight difference in reading different sensors, the KS distances of fingerprints might also be suggested as a support measurement of similarity of different programs.
+
+\subsection{Countermeasure}
+%Two options:
+%\begin{itemize}
+%	\item Randomise response time: needs to be resilient to statistical analysis.
+%	\item Threashold response time (discard or reply in a constant time): performance tradeoff. Recommended for unreliable transmissions.
+%\end{itemize}
+Timing countermeasures are relatively hard to be implemented due to hardware restrictions. There are two common countermeasures considered:
+\begin{itemize}
+	\item Randomly delay the response. However, the randomness must be carefully chosen to be statistically resilient which indicates potential computational overhead.
+
+	\item Use threshold response time, i.e.
+a request is either responded at a predefined time or not responded at all.
+This method is recommended as most 6LoWPAN application would tolerate missing packets and timer is available on most platforms.
+However, the threshold must be carefully chosen to preserve the functionality of the 6LoWPAN application.
+\end{itemize}

### 2017-04-06 Writing/rsptime.tex
Added a 114 words story to fingerprint...

@@
 %\end{itemize}
-The response time of packets could also be exploited to fingerprint the code running on a specific device.
+The program executing on the target is a valuable information in aspect of security and privacy, as it determines functionality of a device and therefore the contents of encrypted packets associated.
+For instance, knowing a target being an actuator that controls an air conditioner immediately suggests a packet directed to it might  be a controlling command.
+
+Our study shows that the response time of packets could also be exploited to reveal information of the program target is executing.
+To be more specifically, an adversary can collect ``fingerprints'', which we explain in the following section, from products available on the market and then use this information to breach the program running on a target device.
 

### 2017-04-06 Writing/iotprotocols.tex
Update

\section{A Typical IoT Protocol Stack}
%A typical sensor network is built as described in \ref{Protocols}.

\begin{table}[!h]
	\centering
	\input{tbl/protocols.tex}
	\caption{Protocol stack for sensor networks. (* are optional.)\label{Protocols}}
\end{table}

%\begin{itemize}
%	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
%	\item Eavesdropping is easier for 6LoWPAN.
%\end{itemize}

\subsection{Our experimental network}
%Say something about devices, and choice of OS, etc.

### 2017-04-06 Writing/relatedwork.tex
Update

\subsection{Related Work}
%Write about attacks that exploit packet length and response times in the context of TCP/IP. Reflect on web applications and how the same might happen if more interesting applications might be deployed that involve IoT objects.

### 2017-04-06 Writing/submission.tex
Update

@@
-\documentclass{river-journal}
-\usepackage{rivps}
-\usepackage[mtbold]{mathtime}
+\documentclass{article}
+%\documentclass{river-journal}
+%\usepackage{rivps}
+%\usepackage[mtbold]{mathtime}
 
@@
 \usepackage{graphics}
-\usepackage{subfigure}
+%\usepackage{subfigure}
 \usepackage{cite}
-
+\usepackage{url}
+\usepackage{subcaption}
+\usepackage{multirow}
 % for alternatives, see appendix of manual
 
-\newtheorem{guess}{Conjecture}
+%\newtheorem{guess}{Conjecture}
 
@@
 
-\raggedbottom
-\sloppy\par
+\title{Exploring Potential 6LoWPAN Traffic Side Channels}
+\author{Yan Yan \& Elisabeth Oswald \& Theo Tryfonas}
 
 \begin{document}
-\begin{opening}
-\title{A Sample Document}
-\author{Yan Yan \& Elisabeth Oswald \& Theo Tryfonas}
-\institute{University of Bristol,  \texttt{y.yan@bristol.ac.uk}}
-\end{opening}
+\maketitle
+%\begin{opening}
+%\institute{University of Bristol,  \texttt{y.yan@bristol.ac.uk}}
+%\end{opening}
 
-\runningtitle{Exploring Potential 6LoWPAN Traffic Side Channels}
-\runningauthor{Y. Yan}
+%\runningtitle{Exploring Potential 6LoWPAN Traffic Side Channels}
+%\runningauthor{Y. Yan}
 
@@
 
-\keywords{6LoWPAN, Side Channels, Traffic Analysis}
+%\keywords{6LoWPAN, Side Channels, Traffic Analysis}
 
@@
 We summarise our work in Section ZZ.
-\subsection{Related Work}
 
-Write about attacks that exploit packet length and response times in the context of TCP/IP.
+\input{relatedwork}
+%\subsection{Related Work}
+%Write about attacks that exploit packet length and response times in the context of TCP/IP.
 Reflect on web applications and how the same might happen if more interesting applications might be deployed that involve IoT objects.
 
-\section{A Typical IoT Protocol Stack}
-A typical sensor network is built as described in \Cref{Protocols}.
+\input{iotprotocols}
+%\section{A Typical IoT Protocol Stack}
+%A typical sensor network is built as described in \ref{Protocols}.
 
-\begin{table}[!h]
-	\centering
-	\input{tbl/protocols.tex}
-	\caption{Protocol stack for sensor networks. (* are optional.)\label{Protocols}}
+%\begin{table}[!h]
+%	\centering
+%	\input{tbl/protocols.tex}
+%	\caption{Protocol stack for sensor networks. (* are optional.)\label{Protocols}}
+%\end{table}
+
+%\begin{itemize}
+%	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
+%	\item Eavesdropping is easier for 6LoWPAN.
+%\end{itemize}
+
+%\subsection{Our experimental network}
+%Say something about devices, and choice of OS, etc.
+
+\section{Exploiting Packet Length Information}
+
+As our brief survey of traffic analysis via exploiting packet lengths showed in Sect.
+YY, the packet length has proven to be a powerful side channel for the classical Internet protocols.
+It is worth noting that this side channel is `noisy' in the classical Internet setting: websites or web applications in this setting typically feature advertisements, which impact on packet lengths; TCP/IP allows to fragment packets and the reassembles them, a feature which is not present in UDP.
+Thus, due to the nature of UDP exploiting the packet length as side channel should be easier in the IoT setting.
+
+Clearly then, any web application style implementations involving an IoT device will thus be extremely vulnerable to attacks such as CITE.
+In the absence of this scenario for state-of-the art IoT applications, it still sends a cautionary warning to developers: binary responses (e.g.
+`yes' vs.
+`no', or `on' vs.
+`off') must always be coded via a binary variable and not via strings because these will have different lengths, which are directly visible via the packet length.
+
+In the remainder of this section we will highlight further problems that arise if packet lengths leak information.
+
+\subsection{Distinguishing ICMP Messages}
+The Internet Control Message Protocol(ICMP)\cite{rfc4443} performs the management tasks in a network, such as link establishment and routing information exchange.
+As explained before we utilise the open source system Contiki, which supports a (sub)set of the ICMP standard (we list the supported ICMP messages in the following).
+Many ICMP messages are ideal for network discovery and exploration, although the purpose of ICMP is to send error messages to the source IP address if standard IP packets fail to be transmitted correctly.
+
+\begin{itemize}
+	\item \textbf{DAG Information Object (DIO)} \\
+	DIO contains the 6LoWPAN global information. It could be periodically broadcasted for network maintenance, or unicasted to a new joining node as a reply to DIS (see below).
+	\item \textbf{DAG Information Solicitation (DIS)} \\
+	DIS is sent by a newly started node to probe any existing 6LoWPANs. A DIO would be replied if the DIS is received by any neighbour nodes.
+	\item \textbf{Destination Advertisement Object (DAO)} \\
+	DAO is sent by a child node to its precedents (The 6LoWPAN DODAG topology is defined in \cite{rfc6550}). to propagate its routing information.
+	\item \textbf{Neighbour Solicitation (NS) and Neighbour Advertisement (NA)} \\
+	NS and NA are the ARP replacement in IPv6, where NS queries a translation and NA answers one. In addition, they are also used for local link validity check.
+	\item \textbf{Echo Request and Echo Response (PING)} \\
+	Echo Request and Echo Response are well known as the PING packets.
+They are mostly used for diagnostic purposes, such as connectivity test or Round Trip Time (RTT) estimation.
+Echo Request may contain arbitrary user defined data and Echo Response simply echoes its corresponding request.
+\end{itemize}
+
+Generally, ICMP messages can be protected by either using the secure ICMP messages (WHAT ARE THESE, REFERENCE!), or relying on the lower layer encryption provided by 802.15.4.
+Contiki OS does not have the former implemented, hence 802.15.4 security is the only option currently.
+We simulated a 6LoWPAN network with 802.15.4 security enabled (we chose the strongest encryption).
+We configured the nodes to also generate random UDP packets.
+Despite the fact that all ICMP messages were encrypted, our experiments show that several ICMP messages can be identified by their packet size and MAC destination.
+Table \ref{IcmpPacketFeature} summarises the packet features.
+The value $x$ denotes the size of user defined data in bytes.
+
+\begin{table}
+	\center
+	\input{tbl/icmpmeta.tex}
+	\caption{6LoWPAN Packet Features\label{IcmpPacketFeature}}
 \end{table}
 
+%First of all, a DIS has the unique smallest packet size of 85 bytes, indicating it can be easily identified.
+
+Among the unicast packets, PING and UDP have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}.
+Therefore, DAO can be uniquely identified as the shortest unicast packet of $97$ bytes.
+For the same reason NA and unicast NS can also be distinguished from other packets by filtering packets of $87$ bytes.
+Considering that NA is sent as a response to NS according to the protocol, one can always identify the first being NS and second being NA.
+
+Similarly, unicast DIO can be identified as the 123 bytes packet followed by DIS, where the later has a unique 85 byte size.
+However, there is a potential of false positive induced by carefully crafted PING or UDP packets.
+PING could be recognised by its pair-wised appearance, as the response would have nearly the same meta data as the original request, except the exchanged source and destination.
+For broadcast packets, DIS can be easily identified by its unique 85 bytes packet size.
+Others like broadcast NS can be identified by the followed characteristic NA response; and packets of 118 bytes those are periodically broadcasted are likely to be DIOs.
+
+In summary, among all the packets, DAO, NA, NS, DIS can be identified with certainty.
+DIO and PING cannot be certainly identified by they both have significant characters.
+Notice that the above contained all ICMPv6 messages supported by Contiki; therefore UDP packets can be reversely filtered, although in some cases the get mixed with DIO and PING.
+
+Although leakage in ICMP messages does not directly lead to any breach of application data, it would still be harmful by providing the adversary with information about the state of the network, including which nodes recently joined etc.
+
+TODO: why would you get the network topology (do you mean via observing the different MAC addresses alongside what they send out)?
+AFter all the payload is still encrypted and so you don't see the actual DAO for instance??
+
+\subsection{Distinguishing Different Devices}
+%Gain hardware information.
+%\begin{itemize}
+%	\item Some devices can handle longer packets, some can't.
+%	\item Works on both 802.15.4 Security and DTLS.
+%\end{itemize}
+
+In the classical Internet world, ICMP has been well known for its use for OS fingerprinting (CITATION NEEDED).
+In the case of the IoT, this could be possible as well (as different OS support different subsets of ICMP), however an additional attack vector exists.
+This is because different IoT devices have different hardware limitations or drivers.
+We noticed that our TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.} whereas our CC2538 handles packets even up to 160 bytes.
+Therefore an adversary can immediately rule out TelosB whenever a packet larger than 127 bytes processed by the target.
+
+\subsection{Guidance to IoT software developers}
+%{\it
+%Pad to MTU is recommended as it completely hides the length of plaintext. This method only induces slight overhead as 6LoWPAN MTU is small and requires only negligible computation.
+%
+%Unifying the drivers by strictly apply the standard MTU. Applications should be compatible to the standard anyway. 
+%}
+A general countermeasure to avoid leaks related to the packet length leakage is padding, as studied in \cite{Peekaboo}.
+Whilst padding to MTU is considered inefficient for Internet, it is in fact highly appropriate for 6LoWPAN because:
 \begin{itemize}
-	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
-	\item Eavesdropping is easier for 6LoWPAN.
+	\item It completely hides the length of original plaintext.
+	\item 6LoWPAN has only a low MTU of 127 bytes; therefore the overhead is acceptable.
+	\item It induces negligible computational overhead.
 \end{itemize}
 
-\section{Exploiting Packet Length Information}
+%Resourceful applications can enhance the countermeasure by inserting dummy packets.
+
+With regard to the leaking information about the device or OS, we suggest strictly applying the standard MTU to eliminate the differences in drivers.
+Although there is a potential of performance downgrade, but it will also improve the compatibility among different devices.
+
 \section{Exploiting Response Time Information}
+
+The response time is another major feature that has been previously exploited in Internet traffic analysis attacks.
+Like in the case of exploiting packet lengths, we would expect that the same attacks (as in the classical Internet setting) can be applied to 6LoWPAN traffic.
+Indeed, like in the previous section, we would expect that they will work even better because the accuracy of timing measurements can be greatly improved for 6LoWPAN traffic: this is because there are fewer noise sources in the traffic, the devices are physically close to each other and uses RF to communicate, the adversary can remove the RTT noises by measure the packets on the server side, and the performance of the constrained devices is low and hence gives a better resolution of the execution time.
+
+\subsection{Distinguishing Different Sensors}
+The first application of timing analysis that we describe is to distinguish between different sensors that are accessed on a device.
+For this purpose we set up an experiment on a CC2538, which has three on-board sensors: Vdd, temperature, and an Ambient Light Sensor (short ALS).
+We access these via CoAP\cite{rfc7252}, which is a protocol designed for constrained devices that provides an universal interface for accessing resources.
+CoAPs is the secure version which stands for CoAP with DTLS.
+
+Due to the different physical characteristics of the sensors, there could be a variance of time that is required to reading the measurements.
+We investigated whether such variances could be observed through the packet response latency.
+If this was the case, then an adversary could learn the nature/purpose of sensors on a network by observing their response time.
+
+We implemented thus set up an experiment on CC2538, using all three sensors from ``cc2538-demo".
+We used CoAP from the ``er-rest-example" in the Contiki OS source code, as there is no CoAPs implementation available.
+Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result will hold equally for CoAPs.
+We carefully controlled for other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.
+
+\begin{table}
+	\center
+	\input{tbl/coapsensors.tex}
+	\caption{CoAP Response Latency for Sensor Readings on CC2538\label{CoapTiming}}
+\end{table}
+
+Table \ref{CoapTiming} summarises the result.
+It shows that ALS takes about $2$ms longer and hence can be easily distinguished.
+Vdd and temperature have much more strongly overlapping distributions, and thus are more difficult to distinguish.
+Nevertheless these results show that our hypothesis holds: different sensors have different latencies and these leak through the response time.
+An adversary who is interested in finding out information about devices on a network might thus be able to match the (known) behaviour of `interesting' sensors to what they observe on the network.
+We remark that this could be useful even in the setting where the sensors transmit their data unencrypted: after all they might return only some reading without a unit of measurement; thus seeing their return data might not as such reveal their nature.
+
+\subsection{Distinguishing Different Devices}
+%Gain hardware information.
+%\begin{itemize}
+%	\item Different hardware has different response latency against the same message.
+%	\item For 802.15.4: Requires additional information. Can be satisfied by the previous ICMP attack.
+%	\item For DTLS: No requirement. The adversary can actively send a message, e.g. PING.
+%\end{itemize}
+
+As we observed before, different devices have different underlying hardware and thus different computational power.
+This implies that there could be the potential that different devices take different amounts of time to process the same message.
+Because ICMP messages are standardised, they are particularly suitable for this purpose.
+Among the different ICMP messages, PING is especially ideal for two reasons:
+\begin{enumerate}
+	\item It is mandatory in the ICMP standard.
+	\item It only swaps the source and destination address of the packet; thus minimises different code path in protocol processing.
+\end{enumerate}
+
+\begin{table}
+	\center
+	\input{tbl/pingresponse}
+	\caption{PING Response Latency\label{PingResponse}}
+\end{table}
+
+Table \ref{PingResponse} shows the PING response latency on CC2538 and TelosB. The result confirms that these devices can be distinguished by PING response latency.
+
+\subsection{Distinguishing Programs}
+%Fingerprints the code running on a device, which leads to plaintext recovery.
+%\begin{itemize}
+%	\item Theory explained in \Cref{FingerprintTheory}.
+%	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
+%	\item Not for 802.15.4: adversary can't join the network.
+%	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
+%\end{itemize}
+
+We remarked before that the functionality of a sensor is potentially valuable information.
+For instance some sensors might be predominantly passive, e.g.
+they might read the temperature and report it back periodically, whereas some sensors might control something upon receiving commands.
+Thus knowing the functionality enables an adversary to make (more) sense of the observed traffic in the network.
+This could be done if a `fingerprint' could be produced for different programs.
+From an adversaries perspective a positive result would imply that they could `fingerprint' products which are on the market and thus use this information to infer what program is running on a target device.
+
+% program executing on the target is a valuable information in aspect of security and privacy, as it determines functionality of a device and therefore the contents of encrypted packets associated.
+For instance, knowing a target being an actuator that controls an air conditioner immediately suggests a packet directed to it might  be a controlling command.
+
+%Our study shows that the response time of packets could also be exploited to reveal information of the program target is executing.
+To be more specifically, an adversary can collect ``fingerprints'', which we explain in the following section, from products available on the market and then use this information to breach the program running on a target device.
+
+%How it works
+To illustrate why this might work, we now look at Figure\ref{FingerprintTheory}.
+It illustrates two sensors receiving the same service request.
+In our example, st the time of receiving the request, Sensor Node 1 was idle and hence responded immediately, whilst Sensor Node 2 postponed the request for reading a sensor.
+Clearly, the response time on Sensor Node 2 would appear longer than that of Sensor Node 1.
+
+\begin{figure}
+	\center
+	\includegraphics[width=\textwidth]{fig/PingProbe_Theory.png}
+	\caption{Variations in Response Time\label{FingerprintTheory}}
+\end{figure}
+
+In real life, most sensors are programmed in a loop; therefore the same code fragments are repeated through the life time of a sensor.
+Each code fragment takes different time to execute and hence the response times vary.
+This behaviour could be statistically analysed and the resulting distribution could be stored as a `fingerprint' .
+
+For this fingerprinting scenario, we must assume the adversary has the pre-knowledge of potential programs and can fingerprint them (or that they have access to a database that contains this information).
+To identify an unknown program running on target sensor, the adversary collects a new fingerprint and then matches it to available fingerprints.
+Clearly, to effectively launch the attack, the adversary needs to be able to send the request to a targeted sensor (equests with short predictable processing time are preferable as they induce less noise).
+
+In practice, the request can be instantiated by several messages defined in the sensor network protocols.
+PING is exceptionally ideal as it is mandatory in the ICMP standard\cite{rfc4433} and has only negligible computation.
+Other options but not excluded are Heartbeat in DTLS\cite{rfc6520}, Reset in CoAP\cite{rfc7252}, etc.
+
+\subsubsection{Extracting Fingerprints}
+We explored the feasibility of fingerprinting programs on an CC2538 running Contiki OS by using the PING command.
+
+Figure \ref{ExamplePri} shows an example of captured packets.
+Contiki MAC\cite{ContikiMAC} sends duplicated PING requests.
+The response time, which refers to PING Response Interval, PRI, is defined to be the time between a PING response and its last paired request.
+The highlighted Packets 205 and 203 shows such an example.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{fig/PRI_hl.png}
+	\caption{Example PRI\label{ExamplePri}}
+\end{figure}
+
+%Since the attack extracts the information contained in the extended response time of a specific request, the first problem is to see whether such extended response time can be filtered from normal ones.
+
+Figure \ref{HelloworldPriNormal} shows the histogram of PRIs collected on the ``helloworld'' example from Contiki OS.
+Values $\geq$12ms are collected at 12ms.
+The result shows that most PRIs are clustered around 9.5ms which consists with our result in \ref{PingResponse}.
+The majority, roughly ranged [9.0, 10.3]ms, corresponds to the usual response time as depicted by Sensor Node 1 in \ref{FingerprintTheory}.
+
+\begin{figure}[!h]
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width=\textwidth]{fig/helloworld_cc2538.png}
+		\caption{PRIs of helloworld\label{HelloworldPriNormal}}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width=\textwidth]{fig/helloworld_cc2538_outlier.png}
+		\caption{PRIs outliers of helloworld\label{HelloworldPriOutliers}}
+	\end{subfigure}
+	\caption{helloworld PRIs\label{HelloworldPri}}
+\end{figure}
+
+We further plotted the upper outliers, mostly ranged [12, 2000]ms, in \ref{HelloworldPriOutliers}.
+We suppose these outliers correspond to the extended response time as depicted by Sensor Node 2 in \ref{FingerprintTheory}.
+The distribution described by \ref{HelloworldPriOutliers} is the fingerprint of the ``helloworld'' example.
+
+The result in Figure \ref{HelloworldPri} shows a clear gap between the usual PRIs and extended PRIs.
+In fact other applications we experimented also showed the same property.
+This implies that an adversary can easily draw a threshold by observing the whole PRI distribution and then filter out the fingerprint.
+In our experiments the threshold is set to 12ms but any other values within the gap would also work.
+
+We collected the fingerprints for three programs taken from the Contiki OS examples:
+\begin{description}
+	\item[broadcast] This program periodically broadcasts a constant message.
+
+	\item[powertrace] This program records the power consumption and broadcasts a constant message.
+
+	\item[Sensorpayload] This program is based on the ``er-rest-example'' embedded together with sensor accesses taken from ``cc2538-demo''.
+It captures a real case scenario where three different sensors, namely Temperature, VDD and ALS, are being access through CoAP.
+\end{description}
+
+Specifically for ``Sensorpayload'' we collected fingerprints for 8 different scenarios where different sensors are being accessed.
+For each program we independently collected 2 fingerprints for comparison.
+
+Figure \ref{FingerprintApps} summarises the total 20 fingerprints we collected for the experiment.
+
+\subsubsection{Fingerprint Matching}
+%Comparing the distribution.
+
+During the experiments we realised that most of the fingerprints do not adhere to common distributions; therefore we used non parametric test, the Kolmogorov-Smirnov Distance (REFERENCE NEEDED), as our test statistic.
+\ref{ksdistances} summarises the relative KS distances computed on each pair of fingerprints in our experiments.
+
+Although fingerprints collected on the same application were rejected by the Kolmogorov-Smirnov Test, we noticed that their KS distance tends to be smaller comparing to fingerprints collected on different programs, as the \textbf{bold} cells marked in Figure \ref{ksdistances}.
+
+By adapting our distinguisher to utilise the minimum KS distance, we were able to identify 13 out of 20 fingerprints successfully.
+The `overlapping' fingerprints are mainly due to the ``Sensorpayload'' program, which access different sensors, but otherwise has identical program code.
+Thus we did expect that the different instantiations of it would lead to very similar fingerprints.
+
+\subsection{Guidance for IoT software developers}
+%Two options:
+%\begin{itemize}
+%	\item Randomise response time: needs to be resilient to statistical analysis.
+%	\item Threashold response time (discard or reply in a constant time): performance tradeoff. Recommended for unreliable transmissions.
+%\end{itemize}
+It is notoriously difficult to produce time-constant code. But two approaches are available to a software developer:
+\begin{itemize}
+	\item Randomly delay the response. This essentially adds noise to the measurements of the adversary.
+
+	\item Use a threshold response time, i.e. a request is either responded at a predefined time or not responded to at all. 
+\end{itemize}
+Within the context of 6LoWPAN the second method is recommended as most 6LoWPAN application would tolerate missing packets and timer is available on most platforms.
+However, the threshold must be carefully chosen to preserve the functionality of the 6LoWPAN application.
+
 \section{Conclusion}

### 2017-04-06 Writing/relatedwork.tex
First draft of related works.

@@
 Reflect on web applications and how the same might happen if more interesting applications might be deployed that involve IoT objects.
+
+%Literatures about Traffic Analysis...
+Traffic Analysis is well studied in the context of encrypted Internet traffic, especially for web applications based on HTTPs and TCP/IP.
+\cite{WebSidechannel} summarised different side channel attacks against web applications and \cite{SuggestBox} studied the practicability of an attack specifically targeted Google and Bing search boxes.
+\cite{PinpointWeb} proposed the use of Mutual Information to pinpoint the potential leakage points in web traffic.
+For non-HTTPs applications, \cite{AppleMsg}, \cite{Language} and \cite{VideoTraffic} described attacks against encrypted text, voice and video traffic respectively.
+Machine learning is widely used to analyse the traffic and behaviours of different classifiers are studied by \cite{HClassifier} and \cite{Peekaboo}.
+It turns out that packet lengths and response times are the most exploited features among all attacks.
+Different countermeasures are studied by \cite{TrafficMorphing}, \cite{HTTPOS} and \cite{FTE}.
+
+Reflecting to IoT applications, most of the attacks may still be applicable exploiting the same features of packet length and response time, as we intend to demonstrate in this paper.
+Considering the future vision that IoT devices could be connected to the Internet with even more sensitive data flowing over different networks, the task of designing secure IoT applications poses to be ever challenging.
+
+%Literatures about 6LoWPAN security
+With regard to the aspect of protocol design, \cite{6LoWPANAtk} summarised some known flaws of 6LoWPAN, including Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}.
+In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.

### 2017-04-06 Writing/iotprotocols.tex
Update.

@@
 %A typical sensor network is built as described in \ref{Protocols}.
+%IoT Protocols
+Many protocols are proposed for different IoT applications adapting to various requirements.
+For example, some smart houses simply use WiFi for connectivity and VANETs\footnote{Vehicular ad hoc networks} may adopt DSRC\cite{DSRC}.
+
+%WSN Protocols
+In this paper we focused on 6LoWPAN\cite{rfc4944} which is based on 802.15.4\cite{802154}.
+These standards are designated for constrained environments such as Wireless Sensor Networks,  but other competing standards exist at different layers.
+Bluetooth Low Energy(BLE)\cite{BLE} is a strong competitor to 802.15.4 as well as the LiFi\cite{LiFi} technology.
+Zigbee\cite{Zigbee} is originally intended as a collective protocol over 802.15.4 but it has been recently adapted for IP-based network as well in \cite{ZigbeeIp} in order to compete with 6LoWPAN.
+The RIME stack\cite{RIME} proposed a set of non-layered primitive over 802.15.4 but it is likely to be phased-out probably due to the reluctance of interoperability with TCP/IP protocol stack of Internet.
+
+%6LoWPAN OS
+6LoWPAN is supported by several competing IoT Operating Systems, including Contiki OS\cite{Contiki}, OpenWSN\cite{OpenWSN}, FreeRTOS\cite{FreeRTOS} and the latest RIOT\cite{RIOT}.
+Contiki OS is chosen for our experiments for its customisability.
+
+\subsection{Our experimental network}
+%Say something about devices, and choice of OS, etc.
+%Hardware
+Our experiment networks are constructed using hardware of TelosB\cite{TelosB} and CC2538\cite{CC2538}.
+TelosB is a low cost sensor powered by MSP430 with AES co-processor representing the low-end devices.
+CC2538 is the high end device powered by ARM Cortex-M3 with multiple cryptographic processors including AES, RSA, SHA-2 and ECC, suggesting for security usage.
+%Should I cite our previous paper...?
+
+%Software
+On the software aspect, we by principle adopted the default settings of Contiki OS, except enabling the 802.15.4 Security upon its study.
+For Layer 4\cite{OSI} and above protocols, we considered the widely accepted combination of CoAP over DTLS(optional) over UDP\footnote{CoAPs is equivalent to CoAP over DTLS.}.
+\Cref{Protocols} summarises our choice of protocol stack in a simplified OSI\cite{OSI} model.
 
@@
 	\input{tbl/protocols.tex}
-	\caption{Protocol stack for sensor networks. (* are optional.)\label{Protocols}}
+	\caption{Protocol stack for our experiments(* is optinal)\label{Protocols}}
 \end{table}
@@
 
-\subsection{Our experimental network}
-%Say something about devices, and choice of OS, etc.
+%Avaible security options.

### 2017-04-06 Writing/relatedwork.tex
Update.

@@
 Reflecting to IoT applications, most of the attacks may still be applicable exploiting the same features of packet length and response time, as we intend to demonstrate in this paper.
-Considering the future vision that IoT devices could be connected to the Internet with even more sensitive data flowing over different networks, the task of designing secure IoT applications poses to be ever challenging.
+Considering the future vision that IoT devices could be connected to the Internet with even more sensitive data flowing over different networks (imaging to control your door lock from a web browser on your desktop), the task of designing secure IoT applications poses to be ever challenging.
 

### 2017-04-06 Writing/submission.tex
Update.

@@
 \usepackage{multirow}
+
+\input{packages}
+
 % for alternatives, see appendix of manual
@@
 \title{Exploring Potential 6LoWPAN Traffic Side Channels}
-\author{Yan Yan \& Elisabeth Oswald \& Theo Tryfonas}
+\author{Yan Yan \and Elisabeth Oswald \and Theo Tryfonas}
 
@@
 
-\input{relatedwork}
-%\subsection{Related Work}
+\subsection{Related Work}
 %Write about attacks that exploit packet length and response times in the context of TCP/IP.
 Reflect on web applications and how the same might happen if more interesting applications might be deployed that involve IoT objects.
+
+%Literatures about Traffic Analysis...
+Traffic Analysis is well studied in the context of encrypted Internet traffic, especially for web applications based on HTTPs and TCP/IP.
+The landmark study by Chen et al.
+\cite{WebSidechannel} discussed different side channel attacks against web applications and \cite{SuggestBox} studied the practicability of an attack specifically targeted Google and Bing search boxes.
+Later work by Mather and Oswald \cite{PinpointWeb} proposed the use of Mutual Information to pinpoint the potential leakage points in web traffic.
+For non-HTTPs applications, the papers \cite{AppleMsg}, \cite{Language} and \cite{VideoTraffic} described attacks against encrypted text, voice and video traffic respectively.
+Machine learning is widely used to analyse the traffic, and behaviours of different classifiers are studied by \cite{HClassifier} and \cite{Peekaboo}.
+Based on all these published works we can conclude that two features, the packet length and response time, are the most exploited ones among all attacks.
+Different countermeasures were studied by \cite{TrafficMorphing}, \cite{HTTPOS} and \cite{FTE}.
+
+Reflecting on IoT applications, we stipulate that most of these attacks may still be applicable, as we intend to demonstrate in this paper.
+Considering the future vision that IoT devices could be indeed connected to the Internet with even more sensitive data flowing over different networks, the task of designing secure IoT applications becomes increasingly challenging.
+
+%Literatures about 6LoWPAN security
+With regard to the aspect of protocol design, the recent paper \cite{6LoWPANAtk} summarised some known flaws of 6LoWPAN, including its susceptibility to the Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}.
+In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.
+
+TODO: if space and time say some more about these attacks. At least say if they relate to the type of leakage we are exploiting or if they are completely independent (which is what I would guess).
 
@@
 Therefore an adversary can immediately rule out TelosB whenever a packet larger than 127 bytes processed by the target.
-
-\subsection{Guidance to IoT software developers}
-%{\it
-%Pad to MTU is recommended as it completely hides the length of plaintext. This method only induces slight overhead as 6LoWPAN MTU is small and requires only negligible computation.
-%
-%Unifying the drivers by strictly apply the standard MTU. Applications should be compatible to the standard anyway. 
-%}
-A general countermeasure to avoid leaks related to the packet length leakage is padding, as studied in \cite{Peekaboo}.
-Whilst padding to MTU is considered inefficient for Internet, it is in fact highly appropriate for 6LoWPAN because:
-\begin{itemize}
-	\item It completely hides the length of original plaintext.
-	\item 6LoWPAN has only a low MTU of 127 bytes; therefore the overhead is acceptable.
-	\item It induces negligible computational overhead.
-\end{itemize}
-
-%Resourceful applications can enhance the countermeasure by inserting dummy packets.
-
-With regard to the leaking information about the device or OS, we suggest strictly applying the standard MTU to eliminate the differences in drivers.
-Although there is a potential of performance downgrade, but it will also improve the compatibility among different devices.
 
@@
 
-\subsection{Guidance for IoT software developers}
+\section{Conclusion}
+
+In this paper we explore, for the first time, the use of packet lengths and response times, which are protocol level side channels, as means to recover information about IoT `things'.
+We do this via some experiments, which we base on two extremely popular devices running on a popular open source OS, with a typical stack of protocols.
+Whilst we do not cover a wide range of devices, the fact that two of the most popular devices show the characteristics that we hypothesise, gives credibility to our results.
+Our results show that it is possible (in principle) to recover information about a device and its function (i.e.
+the hardware and the software that runs on it) via inspecting encrypted traffic that it produces.
+We also point out that ICMP messages can be distinguished from each other despite the use of encryption.
+
+In order to mitigate the leakage that is given by packet lengths, previous works recommends padding \cite{Peekaboo}.
+We echo this recommendation.
+Whilst padding to MTU is considered inefficient for the Internet, it is in fact highly appropriate for 6LoWPAN because:
+\begin{itemize}
+	\item It completely hides the length of original plaintext.
+	\item 6LoWPAN has only a low MTU of 127 bytes; therefore the overhead is acceptable.
+	\item It induces negligible computational overhead.
+\end{itemize}
+
+%Resourceful applications can enhance the countermeasure by inserting dummy packets.
+
+With regard to the leaking information about the device or OS, we suggest strictly applying the standard MTU to eliminate the differences in drivers.
+Although there is a potential of performance downgrade, but it will also improve the compatibility among different devices.
+
 %Two options:
@@
 %\end{itemize}
-It is notoriously difficult to produce time-constant code. But two approaches are available to a software developer:
+In order to mitigate the leakage given by response times, the natural countermeasure is to write time-constant code, which is known to be notoriously difficult.
+But two approaches are available to a software developer:
 \begin{itemize}
@@
 
-\section{Conclusion}
+%\appendix
 
-\appendix
+%And this is my Appendix.
 
-And this is my Appendix.
+%\subsection*{Appendix Subsection}
 
-\subsection*{Appendix Subsection}
-
-Some text.
+%Some text.
 

### 2017-04-06 Writing/iotprotocols.tex
First draft [IoT Protocols] uploaded. Included packages.tex and appendix in submission.tex.

--- 2017-04-06 Writing/iotprotocols.tex
@@
 %A typical sensor network is built as described in \ref{Protocols}.
+%IoT Protocols
+Many protocols are proposed for different IoT applications adapting to various requirements.
+For example, some smart houses simply use WiFi for connectivity and VANETs\footnote{Vehicular ad hoc networks} may adopt DSRC\cite{DSRC}.
+
+%WSN Protocols
+In this paper we focused on 6LoWPAN\cite{rfc4944} which is based on 802.15.4\cite{802154}.
+These standards are designated for constrained environments such as Wireless Sensor Networks,  but other competing standards exist at different layers.
+Bluetooth Low Energy(BLE)\cite{BLE} is a strong competitor to 802.15.4 as well as the LiFi\cite{LiFi} technology.
+Zigbee\cite{Zigbee} is originally intended as a collective protocol over 802.15.4 but it has been recently adapted to IP-based network in ZigbeeIP\cite{ZigbeeIp} so to compete with 6LoWPAN.
+The RIME stack\cite{RIME} proposed a set of non-layered primitives over 802.15.4 but it is likely to be phased-out probably due to the reluctance of interoperability with the TCP/IP protocol stack of Internet.
+
+%6LoWPAN OS
+6LoWPAN is supported by several competing IoT Operating Systems, including Contiki OS\cite{Contiki}, OpenWSN\cite{OpenWSN}, FreeRTOS\cite{FreeRTOS} and the recent RIOT\cite{RIOT}.
+Contiki OS is chosen for our experiments for its customisability.
+
+\subsection{Our experimental network}
+%Say something about devices, and choice of OS, etc.
+%Hardware
+Our experiment networks are constructed using devices constituted of TelosB\cite{TelosB} and CC2538\cite{CC2538}.
+TelosB is a low cost sensor powered by MSP430 with AES co-processor representing the low-end devices.
+CC2538 is the high end device powered by ARM Cortex-M3 with multiple cryptographic processors including AES, RSA, SHA-2 and ECC, suggesting it for security usage.
+%Should I cite our previous paper...?
+
+%Software
+On the software side, we by principle adopted the default settings of Contiki OS, except enabling 802.15.4 Security\cite{802154} upon its study.
+Note that Contiki MAC\cite{ContikiMAC} is chosen by default over TSCH\cite{TSCH}, albeit we would argue the channel information of TSCH could be an additional leakage source.
+For Layer 4\cite{OSI} and above protocols, we considered the widely accepted combination of CoAP\cite{rfc7252} over DTLS\cite{rfc6347}(optional) over UDP\cite{rfc768}\footnote{CoAPs is equivalent to CoAP over DTLS.}.
+\Cref{Protocols} summarises our choice of protocol stack.
 
@@
 
-\subsection{Our experimental network}
-%Say something about devices, and choice of OS, etc.
+%Avaible security options.
+For our settings, there are two schemes available for packet encryption, namely 802.15.4 Security\cite{802154} and DTLS\cite{rfc6347}.
+802.15.4 Security is provided by noncoresec\cite{noncoresec} which implements 802.15.4 authenticated encryption with AES-128 CCM*\cite{CCM} using a hard-coded key shared by the whole 6LoWPAN network.
+tinyDTLS\cite{tinydtls} provides a minimum DTLS implementation that supports only two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively.
+We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously as the resulting packets exceeded the 802.15.4 MTU\footnote{Maximum Transmission Unit.} and thus not practical.

### 2017-04-06 Writing/iotprotocols.tex
Update  # Changes to be committed:

@@
 tinyDTLS\cite{tinydtls} provides a minimum DTLS implementation that supports only two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively.
-We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously as the resulting packets exceeded the 802.15.4 MTU\footnote{Maximum Transmission Unit.} and thus not practical.
+We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously, as the de facto encryption schemes are both AES-128 CCM* and overlapping them does not enhance the security but only increases the overhead.

### 2017-04-06 Writing/submission.tex
First draft [IoT Protocols] uploaded. Included packages.tex and appendix in submission.tex.
Update  # Changes to be committed:

@@
 In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.
+However we do not discuss further about these designing flaws as they lay into a different aspect of the security issues addressed by this paper.
 
-TODO: if space and time say some more about these attacks. At least say if they relate to the type of leakage we are exploiting or if they are completely independent (which is what I would guess).
+%\textbf{TODO: if space and time say some more about these attacks.
+At least say if they relate to the type of leakage we are exploiting or if they are completely independent (which is what I would guess).
+}
 
@@
 
-%\appendix
-
+\appendix
+\input{appendix}
 %And this is my Appendix.

### 2017-04-06 Writing/iotprotocols.tex
Update

--- 2017-04-06 Writing/iotprotocols.tex
@@
 tinyDTLS\cite{tinydtls} provides a minimum DTLS implementation that supports only two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively.
-We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously as the resulting packets exceeded the 802.15.4 MTU\footnote{Maximum Transmission Unit.} and thus not practical.
+We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously, as the de facto encryption schemes are both AES-128 CCM*.
+Overlapping them does not enhance the security but only increases the overhead.

### 2017-04-07 Writing/submission.tex
Finalised V0.9.

@@
 Often `things' are sensor, which are devices that have to function on little resources (most importantly power).
-Thus a whole host of new networking protocols have been developed over the years to cater for such resource constrained devices: 6LoWPAN is the `tiny' version of IPv6, UDP tends to be used instead of TCP/IP, DTLS can be used for end-to-end security or one can directly invoke 802.15.4.
-security which is part of 6LoWPAN, and finally CoAP(s) is the replacement for HTTP(s).
+Thus a whole host of new networking protocols have been developed over the years to cater for such resource constrained devices: 6LoWPAN is the `tiny' version of IPv6, UDP tends to be used instead of TCP/IP, DTLS can be used for end-to-end security or one can directly invoke 802.15.4 Security which is part of 6LoWPAN, and finally CoAP(s) is the replacement for HTTP(s).
 Thus there are two options (802.15.4, and DTLS) to secure communications between the `things' and a server/gateway.
@@
 Implementing cryptography correctly and securely has proven to be a massive challenge as evidenced by the multitude of implementation attacks over the years.
-Triggered off by research that showed how to utilise additional information via timing and power side channels (CITE Kocher), many different flavours of side channel attacks were discovered over the last decade.
+Triggered off by research that showed how to utilise additional information via timing and power side channels\cite{DPA}, many different flavours of side channel attacks were discovered over the last decade.
 Many attacks use phyiscal information (such as low level execution timings or power consumption) to recover secret keys, but many other attacks use protocol level information (such as packet lengths, types of packets or protocol messages) to recover information about plaintexts, devices in the network, or the network itself.
@@
 
-This paper is structured as follows: after reviewing some relevant attack paths for HTTPs over TCP/IP in the following subsection, we provide a brief introduction to the necessary protocol and network features in Section XXX.
-We discuss the impact of packet length leakage in Section XX, followed by an analysis of the response time leakage in Section YY.
-We summarise our work in Section ZZ.
+This paper is structured as follows: after reviewing some relevant attack paths for HTTPs over TCP/IP in the following subsection, we provide a brief introduction to the necessary protocol and network features in \Cref{sec: IotProtocols}.
+We discuss the impact of packet length leakage in \Cref{sec: PacketLen}, followed by an analysis of the response time leakage in \Cref{sec: ResponseTime}.
+We summarise our work in \Cref{sec: Conclusion}.
 
-\subsection{Related Work}
+\subsection{Related Work\label{subsec: RelatedWork}}
 %Write about attacks that exploit packet length and response times in the context of TCP/IP.
@@
 
-\section{Exploiting Packet Length Information}
+\section{Exploiting Packet Length Information\label{sec: PacketLen}}
 
-As our brief survey of traffic analysis via exploiting packet lengths showed in Sect.
-YY, the packet length has proven to be a powerful side channel for the classical Internet protocols.
-It is worth noting that this side channel is `noisy' in the classical Internet setting: websites or web applications in this setting typically feature advertisements, which impact on packet lengths; TCP/IP allows to fragment packets and the reassembles them, a feature which is not present in UDP.
+As our brief survey of traffic analysis via exploiting packet lengths showed in \Cref{subsec: RelatedWork}, the packet length has proven to be a powerful side channel for the classical Internet protocols.
+It is worth noting that this side channel is `noisy' in the classical Internet setting: websites or web applications in this setting typically feature advertisements, which impact on packet lengths; TCP/IP allows to fragment packets and then reassembles them, a feature which is not presented in UDP.
 Thus, due to the nature of UDP exploiting the packet length as side channel should be easier in the IoT setting.
 
-Clearly then, any web application style implementations involving an IoT device will thus be extremely vulnerable to attacks such as CITE.
+Clearly then, any web application style implementations involving an IoT device will thus be extremely vulnerable to attacks such as \cite{WebSidechannel}.
 In the absence of this scenario for state-of-the art IoT applications, it still sends a cautionary warning to developers: binary responses (e.g.
@@
 	\item \textbf{Destination Advertisement Object (DAO)} \\
-	DAO is sent by a child node to its precedents (The 6LoWPAN DODAG topology is defined in \cite{rfc6550}). to propagate its routing information.
+	DAO is sent by a child node to its precedents (The 6LoWPAN DODAG topology is defined in \cite{rfc6550}) to propagate its routing information.
 	\item \textbf{Neighbour Solicitation (NS) and Neighbour Advertisement (NA)} \\
@@
 
-Generally, ICMP messages can be protected by either using the secure ICMP messages (WHAT ARE THESE, REFERENCE!), or relying on the lower layer encryption provided by 802.15.4.
+Generally, ICMP messages can be protected by either using the secure ICMP messages as described in \cite{rfc4443}, or relying on the lower layer encryption provided by 802.15.4.
 Contiki OS does not have the former implemented, hence 802.15.4 security is the only option currently.
-We simulated a 6LoWPAN network with 802.15.4 security enabled (we chose the strongest encryption).
+We simulated a 6LoWPAN network with 802.15.4 security enabled (with strongest encryption and authentication).
 We configured the nodes to also generate random UDP packets.
 Despite the fact that all ICMP messages were encrypted, our experiments show that several ICMP messages can be identified by their packet size and MAC destination.
-Table \ref{IcmpPacketFeature} summarises the packet features.
+\Cref{IcmpPacketFeature} summarises the packet features.
 The value $x$ denotes the size of user defined data in bytes.
@@
 Although leakage in ICMP messages does not directly lead to any breach of application data, it would still be harmful by providing the adversary with information about the state of the network, including which nodes recently joined etc.
+Specifically DAO is always sent from a child to its parent and can be uniquely identified; therefore together with MAC addresses the adversary may exploit it to draw a graph that shows the parental relations in the network.
 
-TODO: why would you get the network topology (do you mean via observing the different MAC addresses alongside what they send out)?
+%\textbf{
+%TODO: why would you get the network topology (do you mean via observing the different MAC addresses alongside what they send out)?
 AFter all the payload is still encrypted and so you don't see the actual DAO for instance??
-
+%}
 \subsection{Distinguishing Different Devices}
@@
 
-In the classical Internet world, ICMP has been well known for its use for OS fingerprinting (CITATION NEEDED).
+In the classical Internet world, ICMP has been well known for its use for OS fingerprinting\cite{OsFingerprint}.
 In the case of the IoT, this could be possible as well (as different OS support different subsets of ICMP), however an additional attack vector exists.
@@
 
-\section{Exploiting Response Time Information}
+\section{Exploiting Response Time Information\label{sec: ResponseTime}}
 
@@
 
-Due to the different physical characteristics of the sensors, there could be a variance of time that is required to reading the measurements.
+Due to the different physical characteristics of the sensors, there could be a variance of time that is required for reading the measurements.
 We investigated whether such variances could be observed through the packet response latency.
@@
 Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result will hold equally for CoAPs.
-We carefully controlled for other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.
+We carefully controlled other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.
 
@@
 
-Table \ref{CoapTiming} summarises the result.
+\Cref{CoapTiming} summarises the result.
 It shows that ALS takes about $2$ms longer and hence can be easily distinguished.
@@
 
-Table \ref{PingResponse} shows the PING response latency on CC2538 and TelosB. The result confirms that these devices can be distinguished by PING response latency.
+\Cref{PingResponse} shows the PING response latency on CC2538 and TelosB. The result confirms that these devices can be distinguished by PING response latency.
 
@@
 %How it works
-To illustrate why this might work, we now look at Figure\ref{FingerprintTheory}.
+To illustrate why this might work, we now look at \Cref{FingerprintTheory}.
 It illustrates two sensors receiving the same service request.
-In our example, st the time of receiving the request, Sensor Node 1 was idle and hence responded immediately, whilst Sensor Node 2 postponed the request for reading a sensor.
+In our example, at the time of receiving the request, Sensor Node 1 was idle and hence responded immediately, whilst Sensor Node 2 postponed the request for reading a sensor.
 Clearly, the response time on Sensor Node 2 would appear longer than that of Sensor Node 1.
@@
 To identify an unknown program running on target sensor, the adversary collects a new fingerprint and then matches it to available fingerprints.
-Clearly, to effectively launch the attack, the adversary needs to be able to send the request to a targeted sensor (equests with short predictable processing time are preferable as they induce less noise).
+Clearly, to effectively launch the attack, the adversary needs to be able to send the request to a targeted sensor (requests with short predictable processing time are preferable as they induce less noise).
 
@@
 
-Figure \ref{ExamplePri} shows an example of captured packets.
+\Cref{ExamplePri} shows an example of captured packets.
 Contiki MAC\cite{ContikiMAC} sends duplicated PING requests.
@@
 
-Figure \ref{HelloworldPriNormal} shows the histogram of PRIs collected on the ``helloworld'' example from Contiki OS.
+\Cref{HelloworldPriNormal} shows the histogram of PRIs collected on the ``helloworld'' example from Contiki OS.
 Values $\geq$12ms are collected at 12ms.
-The result shows that most PRIs are clustered around 9.5ms which consists with our result in \ref{PingResponse}.
-The majority, roughly ranged [9.0, 10.3]ms, corresponds to the usual response time as depicted by Sensor Node 1 in \ref{FingerprintTheory}.
+The result shows that most PRIs are clustered around 9.5ms which consists with our result in \Cref{PingResponse}.
+The majority, roughly ranged [9.0, 10.3]ms, corresponds to the usual response time as depicted by Sensor Node 1 in \Cref{FingerprintTheory}.
 
@@
 
-We further plotted the upper outliers, mostly ranged [12, 2000]ms, in \ref{HelloworldPriOutliers}.
-We suppose these outliers correspond to the extended response time as depicted by Sensor Node 2 in \ref{FingerprintTheory}.
-The distribution described by \ref{HelloworldPriOutliers} is the fingerprint of the ``helloworld'' example.
+We further plotted the upper outliers, mostly ranged [12, 2000]ms, in \Cref{HelloworldPriOutliers}.
+We suppose these outliers correspond to the extended response time as depicted by Sensor Node 2 in \Cref{FingerprintTheory}.
+The distribution described by \Cref{HelloworldPriOutliers} is the fingerprint of the ``helloworld'' example.
 
-The result in Figure \ref{HelloworldPri} shows a clear gap between the usual PRIs and extended PRIs.
+The result in \Cref{HelloworldPri} shows a clear gap between the usual PRIs and extended PRIs.
 In fact other applications we experimented also showed the same property.
@@
 	\item[Sensorpayload] This program is based on the ``er-rest-example'' embedded together with sensor accesses taken from ``cc2538-demo''.
-It captures a real case scenario where three different sensors, namely Temperature, VDD and ALS, are being access through CoAP.
+It captures a real case scenario where three different sensors, namely Temperature, VDD and ALS, are being accessed through CoAP.
 \end{description}
@@
 
-Figure \ref{FingerprintApps} summarises the total 20 fingerprints we collected for the experiment.
+\Cref{FingerprintApps} summarises the total 20 fingerprints we collected for the experiment.
 
@@
 
-During the experiments we realised that most of the fingerprints do not adhere to common distributions; therefore we used non parametric test, the Kolmogorov-Smirnov Distance (REFERENCE NEEDED), as our test statistic.
-\ref{ksdistances} summarises the relative KS distances computed on each pair of fingerprints in our experiments.
+During the experiments we realised that most of the fingerprints do not adhere to common distributions; therefore we used non parametric test, the Kolmogorov-Smirnov Distance\cite{KsTest}, as our test statistic.
+\Cref{ksdistances} summarises the relative KS distances computed on each pair of fingerprints in our experiments.
 
-Although fingerprints collected on the same application were rejected by the Kolmogorov-Smirnov Test, we noticed that their KS distance tends to be smaller comparing to fingerprints collected on different programs, as the \textbf{bold} cells marked in Figure \ref{ksdistances}.
+Although fingerprints collected on the same application were rejected by the Kolmogorov-Smirnov Test, we noticed that their KS distance tends to be smaller comparing to fingerprints collected on different programs, as the \textbf{bold} cells marked in \Cref{ksdistances}.
 
@@
 
-\section{Conclusion}
+\section{Conclusion\label{sec: Conclusion}}
 
@@
 
-	\item Use a threshold response time, i.e. a request is either responded at a predefined time or not responded to at all. 
+	\item Use a threshold response time, i.e. a request is either responded at a predefined time or not responded at all. 
 \end{itemize}

### 2017-04-07 Writing/submission.tex
Final draft 0.99.

@@
 \subsection*{Abstract}
-The Internet of Things has become a reality: small connected devices feature in everyday objects
+The Internet of Things (IoT) has become a reality: small connected devices feature in everyday objects
 including childrens' toys, TVs, fridges, heating control units, etc. Supply chains feature sensors
@@
 where sensors monitor wellbeing.
-A future in which sensors and other (small) devices interact to create sophisticated applications seems just around the corner .
-All of these applications have a fundamental need for security and privacy and thus we need to deploy cryptography as part an attempt to secure them.
-In this paper we explore a particular type of flaw, namely side channel information, on the protocol level.
-Our research investigates the potential for utilising packet length and timing information (both are easily obtained) to extract interesting information from a system, despite the use of cryptography.
+A future in which sensors and other (small) devices interact to create sophisticated applications seems just around the corner.
+All of these applications have a fundamental need for security and privacy and thus cryptography is deployed as part of an attempt to secure them.
+In this paper we explore a particular type of flaw, namely side channel information, on the protocol level that can exist despite the use of cryptography.
+Our research investigates the potential for utilising packet length and timing information (both are easily obtained) to extract interesting information from a system.
+We find that using these side channels we can distinguish between devices, different programs running on the same device including which sensor is accessed.
+We also find it is possible to distinguish between different types of ICMP messages despite the use of encryption.
+Based on our findings, we provide a set of recommendations to efficiently mitigate these side channels in the IoT context.
 
@@
 Often `things' are sensor, which are devices that have to function on little resources (most importantly power).
-Thus a whole host of new networking protocols have been developed over the years to cater for such resource constrained devices: 6LoWPAN is the `tiny' version of IPv6, UDP tends to be used instead of TCP/IP, DTLS can be used for end-to-end security or one can directly invoke 802.15.4 Security which is part of 6LoWPAN, and finally CoAP(s) is the replacement for HTTP(s).
+Thus a whole host of new networking protocols have been developed over the years to cater for such resource constrained devices: 6LoWPAN is the `tiny' version of IPv6, UDP tends to be used instead of TCP/IP, DTLS can be used for end-to-end security or one can directly invoke 802.15.4 security which is part of 6LoWPAN, and finally CoAP(s) is the replacement for HTTP(s).
 Thus there are two options (802.15.4, and DTLS) to secure communications between the `things' and a server/gateway.
@@
 HTTPs over TCP/IP network, but the applicability of (some) of these attacks in the context of a typical IoT protocol stack is lacking.
-This is the gap that we would like to address within this submission.
+This is the gap that we would like to address with this work.
 
@@
 In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.
-However we do not discuss further about these designing flaws as they lay into a different aspect of the security issues addressed by this paper.
+However we do not discuss further these particular design flaws as they touch on a different aspect of the security issues in 6LoWPAN compared to what we address in this paper.
 
-%\textbf{TODO: if space and time say some more about these attacks.
-At least say if they relate to the type of leakage we are exploiting or if they are completely independent (which is what I would guess).
-}
+\section{A Typical IoT Protocol Stack\label{sec: IotProtocols}}
 
-\input{iotprotocols}
-%\section{A Typical IoT Protocol Stack}
-%A typical sensor network is built as described in \ref{Protocols}.
+%IoT Protocols
+There are large number of protocols, which have been proposed for different IoT applications adapting to various requirements.
+For example, some smart houses simply use WiFi for connectivity and VANETs\footnote{Vehicular ad hoc networks} may adopt DSRC\cite{DSRC}.
 
-%\begin{table}[!h]
-%	\centering
-%	\input{tbl/protocols.tex}
-%	\caption{Protocol stack for sensor networks. (* are optional.)\label{Protocols}}
-%\end{table}
+%WSN Protocols
+In this paper we focus on 6LoWPAN\cite{rfc4944} which is based on the 802.15.4\cite{802154} standard.
+These standards are designated for constrained environments such as Wireless Sensor Networks,  but other competing standards exist at different layers.
+Bluetooth Low Energy(BLE)\cite{BLE} is a strong competitor to 802.15.4 as well as the LiFi\cite{LiFi} technology.
+Zigbee\cite{Zigbee} was originally intended as a collective protocol over 802.15.4 but it has been recently adapted to IP-based network in ZigbeeIP\cite{ZigbeeIp}.
+The RIME stack\cite{RIME} proposes a set of non-layered primitives over 802.15.4 but it is likely to be phased-out due to the lack of of interoperability with the TCP/IP protocol stack.
+
+%6LoWPAN OS
+6LoWPAN thus is the most popular standard for low power networks, and thus it is supported by several competing IoT Operating Systems, including Contiki OS\cite{Contiki}, OpenWSN\cite{OpenWSN}, FreeRTOS\cite{FreeRTOS} and the recent RIOT\cite{RIOT}.
+We chose Contiki OS for our experiments because it is easy to customise.
+
+\subsection{Our experimental network}
+%Say something about devices, and choice of OS, etc.
+%Hardware
+Our experimental network is constructed using two different devices.
+These are a TelosB\cite{TelosB} and a CC2538\cite{CC2538}.
+The TelosB is a low cost sensor powered by an MSP430 with an AES co-processor.
+It represents typical low-end devices.
+The CC2538 is the high end device powered by an ARM Cortex-M3 with multiple cryptographic processors including AES, RSA, SHA-2 and ECC, suggesting that it is suitable to develop secure applications.
+%Should I cite our previous paper...?
+
+%Software
+Both devices are supported by the Contiki OS.
+We adopted the default settings of the Contiki OS, except for enabling 802.15.4 security\cite{802154} for some experiments.
+Note that the Contiki MAC\cite{ContikiMAC} is chosen by default over TSCH\cite{TSCH}.
+For Layer 4\cite{OSI} and above protocols, we went with the widely accepted combination of CoAP\cite{rfc7252}, and DTLS\cite{rfc6347}(optional) over UDP\cite{rfc768}\footnote{CoAPs is equivalent to CoAP over DTLS.}.
+\Cref{Protocols} summarises our choice of protocol stack.
+
+\begin{table}[!h]
+	\centering
+	\begin{tabular}{|c|c|}
+	\hline
+	Physical                        & \multirow{2}{*}{802.15.4} \\ \cline{1-1}
+	Link                          &                           \\ \hline
+	Network                       & 6LoWPAN                   \\ \hline
+	\multirow{2}{*}{Transmission} & UDP                       \\ \cline{2-2} 
+	                              & DTLS*                     \\ \hline
+	Application                   & CoAP / CoAPs*             \\ \hline
+	\end{tabular}
+
+	\caption{Protocol stack for our experiments(* is optinal)\label{Protocols}}
+\end{table}
 
@@
 
-%\subsection{Our experimental network}
-%Say something about devices, and choice of OS, etc.
+%Avaible security options.
+\subsubsection{802.15.4 and DTLS}
+In our setting, there are two standards available for packet encryption, namely 802.15.4 security\cite{802154} and DTLS\cite{rfc6347}.
+802.15.4 security is provided by the noncoresec\cite{noncoresec} API, which implements 802.15.4 authenticated encryption with AES-128 CCM*\cite{CCM} using a hard-coded key shared by the whole 6LoWPAN network.
+We chose tinyDTLS\cite{tinydtls}  as library for the DTLS protocols, because it provides a minimum DTLS implementation that supports two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively.
+Evidently, they both utilise AES-128 CCM* as the packet encryption method.
 
@@
 The Internet Control Message Protocol(ICMP)\cite{rfc4443} performs the management tasks in a network, such as link establishment and routing information exchange.
-As explained before we utilise the open source system Contiki, which supports a (sub)set of the ICMP standard (we list the supported ICMP messages in the following).
+As explained before we utilise the open source system Contiki, which supports a (sub)set of the ICMP standard (we list the supported ICMP messages further below).
 Many ICMP messages are ideal for network discovery and exploration, although the purpose of ICMP is to send error messages to the source IP address if standard IP packets fail to be transmitted correctly.
@@
 Among the unicast packets, PING and UDP have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}.
-Therefore, DAO can be uniquely identified as the shortest unicast packet of $97$ bytes.
+Therefore, DAO can be uniquely identified as the shorter unicast packet of $97$ bytes.
 For the same reason NA and unicast NS can also be distinguished from other packets by filtering packets of $87$ bytes.
@@
 Similarly, unicast DIO can be identified as the 123 bytes packet followed by DIS, where the later has a unique 85 byte size.
-However, there is a potential of false positive induced by carefully crafted PING or UDP packets.
+However, there is a potential of false positive induced by PING or UDP packets with user defined data crafted to have the same packet length\footnote{22 bytes for PING and 16 bytes for UDP.}.
 PING could be recognised by its pair-wised appearance, as the response would have nearly the same meta data as the original request, except the exchanged source and destination.
@@
 In summary, among all the packets, DAO, NA, NS, DIS can be identified with certainty.
-DIO and PING cannot be certainly identified by they both have significant characters.
-Notice that the above contained all ICMPv6 messages supported by Contiki; therefore UDP packets can be reversely filtered, although in some cases the get mixed with DIO and PING.
+DIO and PING cannot be certainly identified but they both have significant characters.
+Notice that the above contained all ICMPv6 messages supported by Contiki; therefore UDP packets can be reversely filtered, although in some cases they get mixed with DIO and PING.
 
@@
 Specifically DAO is always sent from a child to its parent and can be uniquely identified; therefore together with MAC addresses the adversary may exploit it to draw a graph that shows the parental relations in the network.
+In addition, these information can also be exploited by attacks as in \cite{WsnIcmp}.
 
@@
 
-We implemented thus set up an experiment on CC2538, using all three sensors from ``cc2538-demo".
+We thus set up an experiment on CC2538, using all three sensors from ``cc2538-demo".
 We used CoAP from the ``er-rest-example" in the Contiki OS source code, as there is no CoAPs implementation available.
-Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result will hold equally for CoAPs.
+Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result can be equally expected for CoAPs.
 We carefully controlled other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.
@@
 Vdd and temperature have much more strongly overlapping distributions, and thus are more difficult to distinguish.
-Nevertheless these results show that our hypothesis holds: different sensors have different latencies and these leak through the response time.
+Nevertheless these results confirm  our hypothesis: different sensors have different latencies and these leak through the response time.
 An adversary who is interested in finding out information about devices on a network might thus be able to match the (known) behaviour of `interesting' sensors to what they observe on the network.
@@
 This could be done if a `fingerprint' could be produced for different programs.
-From an adversaries perspective a positive result would imply that they could `fingerprint' products which are on the market and thus use this information to infer what program is running on a target device.
+From an adversary's perspective a positive result would imply that they could `fingerprint' products which are on the market and thus use this information to infer what program is running on a target device.
 
@@
 We further plotted the upper outliers, mostly ranged [12, 2000]ms, in \Cref{HelloworldPriOutliers}.
-We suppose these outliers correspond to the extended response time as depicted by Sensor Node 2 in \Cref{FingerprintTheory}.
+Unfortunately we do not have a solution to investigate the exact cause of such delay, as we unable to control the code execution that requires environmental interaction within a timing critical context.
+Nevertheless, we suppose these outliers correspond to the extended response time as depicted by Sensor Node 2 in \Cref{FingerprintTheory}.
 The distribution described by \Cref{HelloworldPriOutliers} is the fingerprint of the ``helloworld'' example.
@@
 	\item[Sensorpayload] This program is based on the ``er-rest-example'' embedded together with sensor accesses taken from ``cc2538-demo''.
-It captures a real case scenario where three different sensors, namely Temperature, VDD and ALS, are being accessed through CoAP.
+It captures a real case scenario where three different sensors, namely Temperature, Vdd and ALS, are being accessed through CoAP.
 \end{description}
@@
 
-During the experiments we realised that most of the fingerprints do not adhere to common distributions; therefore we used non parametric test, the Kolmogorov-Smirnov Distance\cite{KsTest}, as our test statistic.
+During the experiments we realised that most of the fingerprints do not adhere to common distributions; therefore we used a non parametric test, the Kolmogorov-Smirnov Distance\cite{KsTest}, as our test statistic.
+This is a well understood statistic with previous uses in side channel analysis\cite{KsDistanceDistinguisher}.
 \Cref{ksdistances} summarises the relative KS distances computed on each pair of fingerprints in our experiments.
@@
 In this paper we explore, for the first time, the use of packet lengths and response times, which are protocol level side channels, as means to recover information about IoT `things'.
-We do this via some experiments, which we base on two extremely popular devices running on a popular open source OS, with a typical stack of protocols.
+We do this experimentally, which we base on two extremely popular devices running on a popular open source OS, with a typical stack of protocols.
 Whilst we do not cover a wide range of devices, the fact that two of the most popular devices show the characteristics that we hypothesise, gives credibility to our results.
@@
 
-In order to mitigate the leakage that is given by packet lengths, previous works recommends padding \cite{Peekaboo}.
+In order to mitigate the leakage that is given by packet lengths, previous works recommend padding \cite{Peekaboo}.
 We echo this recommendation.
@@
 With regard to the leaking information about the device or OS, we suggest strictly applying the standard MTU to eliminate the differences in drivers.
-Although there is a potential of performance downgrade, but it will also improve the compatibility among different devices.
+Although there is a potential of performance downgrade, it will also improve the compatibility among different devices.
 

### 2017-04-07 Writing/submission.tex
Typo fix.

@@
 We further plotted the upper outliers, mostly ranged [12, 2000]ms, in \Cref{HelloworldPriOutliers}.
-Unfortunately we do not have a solution to investigate the exact cause of such delay, as we unable to control the code execution that requires environmental interaction within a timing critical context.
+Unfortunately we do not have a solution to investigate the exact cause of such delay, as we were unable to control the code execution that requires environmental interaction within a timing critical context.
 Nevertheless, we suppose these outliers correspond to the extended response time as depicted by Sensor Node 2 in \Cref{FingerprintTheory}.

### 2017-04-07 Writing/introduction.tex
Update
River publisher ready version 1.0.

@@
+\subsection*{Abstract}
+The Internet of Things (IoT) has become a reality: small connected devices feature in everyday objects
+including childrens' toys, TVs, fridges, heating control units, etc. Supply chains feature sensors
+throughout, and significant investments go into researching next-generation healthcare, 
+where sensors monitor wellbeing.
+A future in which sensors and other (small) devices interact to create sophisticated applications seems just around the corner.
+All of these applications have a fundamental need for security and privacy and thus cryptography is deployed as part of an attempt to secure them.
+In this paper we explore a particular type of flaw, namely side channel information, on the protocol level that can exist despite the use of cryptography.
+Our research investigates the potential for utilising packet length and timing information (both are easily obtained) to extract interesting information from a system.
+We find that using these side channels we can distinguish between devices, different programs running on the same device including which sensor is accessed.
+We also find it is possible to distinguish between different types of ICMP messages despite the use of encryption.
+Based on our findings, we provide a set of recommendations to efficiently mitigate these side channels in the IoT context.
+
+%\keywords{6LoWPAN, Side Channels, Traffic Analysis}
+
 \section{Introduction}
-\textit{
-\begin{itemize}
-	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
-\end{itemize}
-}
+The expression `Internet of Things' (IoT) can refer to a multitude of objects and protocols, which share that they have been purposefully designed for resource constraint environments.
+Whereas the typical TCP/IP network stack produces considerable overhead to achieve quality of service for applications that are based on it, the nature of many IoT `things' is such that a full implementation of it would not be practical.
+Often `things' are sensor, which are devices that have to function on little resources (most importantly power).
+Thus a whole host of new networking protocols have been developed over the years to cater for such resource constrained devices: 6LoWPAN is the `tiny' version of IPv6, UDP tends to be used instead of TCP/IP, DTLS can be used for end-to-end security or one can directly invoke 802.15.4 security which is part of 6LoWPAN, and finally CoAP(s) is the replacement for HTTP(s).
+Thus there are two options (802.15.4, and DTLS) to secure communications between the `things' and a server/gateway.
+
+Implementing cryptography correctly and securely has proven to be a massive challenge as evidenced by the multitude of implementation attacks over the years.
+Triggered off by research that showed how to utilise additional information via timing and power side channels\cite{DPA}, many different flavours of side channel attacks were discovered over the last decade.
+Many attacks use phyiscal information (such as low level execution timings or power consumption) to recover secret keys, but many other attacks use protocol level information (such as packet lengths, types of packets or protocol messages) to recover information about plaintexts, devices in the network, or the network itself.
+There exists a considerable body of work in the context of conventional, i.e.
+HTTPs over TCP/IP network, but the applicability of (some) of these attacks in the context of a typical IoT protocol stack is lacking.
+This is the gap that we would like to address with this work.
+
+This paper is structured as follows: after reviewing some relevant attack paths for HTTPs over TCP/IP in the following subsection, we provide a brief introduction to the necessary protocol and network features in \Cref{sec: IotProtocols}.
+We discuss the impact of packet length leakage in \Cref{sec: PacketLen}, followed by an analysis of the response time leakage in \Cref{sec: ResponseTime}.
+We summarise our work in \Cref{sec: Conclusion}.
+
+\subsection{Related Work\label{subsec: RelatedWork}}
+%Write about attacks that exploit packet length and response times in the context of TCP/IP.
+Reflect on web applications and how the same might happen if more interesting applications might be deployed that involve IoT objects.
+
+%Literatures about Traffic Analysis...
+Traffic Analysis is well studied in the context of encrypted Internet traffic, especially for web applications based on HTTPs and TCP/IP.
+The landmark study by Chen et al.
+\cite{WebSidechannel} discussed different side channel attacks against web applications and \cite{SuggestBox} studied the practicability of an attack specifically targeted Google and Bing search boxes.
+Later work by Mather and Oswald \cite{PinpointWeb} proposed the use of Mutual Information to pinpoint the potential leakage points in web traffic.
+For non-HTTPs applications, the papers \cite{AppleMsg}, \cite{Language} and \cite{VideoTraffic} described attacks against encrypted text, voice and video traffic respectively.
+Machine learning is widely used to analyse the traffic, and behaviours of different classifiers are studied by \cite{HClassifier} and \cite{Peekaboo}.
+Based on all these published works we can conclude that two features, the packet length and response time, are the most exploited ones among all attacks.
+Different countermeasures were studied by \cite{TrafficMorphing}, \cite{HTTPOS} and \cite{FTE}.
+
+Reflecting on IoT applications, we stipulate that most of these attacks may still be applicable, as we intend to demonstrate in this paper.
+Considering the future vision that IoT devices could be indeed connected to the Internet with even more sensitive data flowing over different networks, the task of designing secure IoT applications becomes increasingly challenging.
+
+%Literatures about 6LoWPAN security
+With regard to the aspect of protocol design, the recent paper \cite{6LoWPANAtk} summarised some known flaws of 6LoWPAN, including its susceptibility to the Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}.
+In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.
+However we do not discuss further these particular design flaws as they touch on a different aspect of the security issues in 6LoWPAN compared to what we address in this paper.

### 2017-04-07 Writing/iotprotocols.tex
Finalised V0.9.
Final draft 0.99.
River publisher ready version 1.0.

--- 2017-04-06 Writing/iotprotocols.tex
@@
-\section{A Typical IoT Protocol Stack}
-%A typical sensor network is built as described in \ref{Protocols}.
+\section{A Typical IoT Protocol Stack\label{sec: IotProtocols}}
+
 %IoT Protocols
-Many protocols are proposed for different IoT applications adapting to various requirements.
+There are large number of protocols, which have been proposed for different IoT applications adapting to various requirements.
 For example, some smart houses simply use WiFi for connectivity and VANETs\footnote{Vehicular ad hoc networks} may adopt DSRC\cite{DSRC}.
@@
 %WSN Protocols
-In this paper we focused on 6LoWPAN\cite{rfc4944} which is based on 802.15.4\cite{802154}.
+In this paper we focus on 6LoWPAN\cite{rfc4944} which is based on the 802.15.4\cite{802154} standard.
 These standards are designated for constrained environments such as Wireless Sensor Networks,  but other competing standards exist at different layers.
 Bluetooth Low Energy(BLE)\cite{BLE} is a strong competitor to 802.15.4 as well as the LiFi\cite{LiFi} technology.
-Zigbee\cite{Zigbee} is originally intended as a collective protocol over 802.15.4 but it has been recently adapted to IP-based network in ZigbeeIP\cite{ZigbeeIp} so to compete with 6LoWPAN.
-The RIME stack\cite{RIME} proposed a set of non-layered primitives over 802.15.4 but it is likely to be phased-out probably due to the reluctance of interoperability with the TCP/IP protocol stack of Internet.
+Zigbee\cite{Zigbee} was originally intended as a collective protocol over 802.15.4 but it has been recently adapted to IP-based network in ZigbeeIP\cite{ZigbeeIp}.
+The RIME stack\cite{RIME} proposes a set of non-layered primitives over 802.15.4 but it is likely to be phased-out due to the lack of of interoperability with the TCP/IP protocol stack.
 
 %6LoWPAN OS
-6LoWPAN is supported by several competing IoT Operating Systems, including Contiki OS\cite{Contiki}, OpenWSN\cite{OpenWSN}, FreeRTOS\cite{FreeRTOS} and the recent RIOT\cite{RIOT}.
-Contiki OS is chosen for our experiments for its customisability.
+6LoWPAN thus is the most popular standard for low power networks, and thus it is supported by several competing IoT Operating Systems, including Contiki OS\cite{Contiki}, OpenWSN\cite{OpenWSN}, FreeRTOS\cite{FreeRTOS} and the recent RIOT\cite{RIOT}.
+We chose Contiki OS for our experiments because it is easy to customise.
 
@@
 %Hardware
-Our experiment networks are constructed using devices constituted of TelosB\cite{TelosB} and CC2538\cite{CC2538}.
-TelosB is a low cost sensor powered by MSP430 with AES co-processor representing the low-end devices.
-CC2538 is the high end device powered by ARM Cortex-M3 with multiple cryptographic processors including AES, RSA, SHA-2 and ECC, suggesting it for security usage.
+Our experimental network is constructed using two different devices.
+These are a TelosB\cite{TelosB} and a CC2538\cite{CC2538}.
+The TelosB is a low cost sensor powered by an MSP430 with an AES co-processor.
+It represents typical low-end devices.
+The CC2538 is the high end device powered by an ARM Cortex-M3 with multiple cryptographic processors including AES, RSA, SHA-2 and ECC, suggesting that it is suitable to develop secure applications.
 %Should I cite our previous paper...?
@@
 %Software
-On the software side, we by principle adopted the default settings of Contiki OS, except enabling 802.15.4 Security\cite{802154} upon its study.
-Note that Contiki MAC\cite{ContikiMAC} is chosen by default over TSCH\cite{TSCH}, albeit we would argue the channel information of TSCH could be an additional leakage source.
-For Layer 4\cite{OSI} and above protocols, we considered the widely accepted combination of CoAP\cite{rfc7252} over DTLS\cite{rfc6347}(optional) over UDP\cite{rfc768}\footnote{CoAPs is equivalent to CoAP over DTLS.}.
+Both devices are supported by the Contiki OS.
+We adopted the default settings of the Contiki OS, except for enabling 802.15.4 security\cite{802154} for some experiments.
+Note that the Contiki MAC\cite{ContikiMAC} is chosen by default over TSCH\cite{TSCH}.
+For Layer 4\cite{OSI} and above protocols, we went with the widely accepted combination of CoAP\cite{rfc7252}, and DTLS\cite{rfc6347}(optional) over UDP\cite{rfc768}\footnote{CoAPs is equivalent to CoAP over DTLS.}.
 \Cref{Protocols} summarises our choice of protocol stack.
@@
 	\centering
-	\input{tbl/protocols.tex}
+	\begin{tabular}{|c|c|}
+		\hline
+		Physical                        & \multirow{2}{*}{802.15.4} \\ \cline{1-1}
+		Link                          &                           \\ \hline
+		Network                       & 6LoWPAN                   \\ \hline
+		\multirow{2}{*}{Transmission} & UDP                       \\ \cline{2-2} 
+		& DTLS*                     \\ \hline
+		Application                   & CoAP / CoAPs*             \\ \hline
+	\end{tabular}
+
 	\caption{Protocol stack for our experiments(* is optinal)\label{Protocols}}
@@
 %Avaible security options.
-For our settings, there are two schemes available for packet encryption, namely 802.15.4 Security\cite{802154} and DTLS\cite{rfc6347}.
-802.15.4 Security is provided by noncoresec\cite{noncoresec} which implements 802.15.4 authenticated encryption with AES-128 CCM*\cite{CCM} using a hard-coded key shared by the whole 6LoWPAN network.
-tinyDTLS\cite{tinydtls} provides a minimum DTLS implementation that supports only two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively.
-We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously as the resulting packets exceeded the 802.15.4 MTU\footnote{Maximum Transmission Unit.} and thus not practical.
+\subsubsection{802.15.4 and DTLS}
+In our setting, there are two standards available for packet encryption, namely 802.15.4 security\cite{802154} and DTLS\cite{rfc6347}.
+802.15.4 security is provided by the noncoresec\cite{noncoresec} API, which implements 802.15.4 authenticated encryption with AES-128 CCM*\cite{CCM} using a hard-coded key shared by the whole 6LoWPAN network.
+We chose tinyDTLS\cite{tinydtls}  as library for the DTLS protocols, because it provides a minimum DTLS implementation that supports two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively.
+Evidently, they both utilise AES-128 CCM* as the packet encryption method.

### 2017-11-21 experiments/NonRootBR/project-conf.h
Moved to project specific repository.

@@ -1,0 +1,56 @@
+/*
+ * Copyright (c) 2010, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ */
+
+#ifndef PROJECT_ROUTER_CONF_H_
[…]

### 2017-11-21 experiments/PingProbe/cc2538-websense/cc2538-websense.c

@@ -1,0 +1,184 @@
+/*
+ * Copyright (c) 2010, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ */
+
+/**
+ * \file
+ *         Light and temperatur sensor web demo
+ * \author
+ *         Niclas Finne    <nfi@sics.se>
+ *         Joakim Eriksson <joakime@sics.se>
+ *         Joel Hoglund    <joel@sics.se>
+ */
+
+#include "contiki.h"
+#include "httpd-simple.h"
[…]

### 2017-11-21 experiments/PingProbe/dtlspingload/dtls-client.c

@@ -1,0 +1,340 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
+#include "sys/etimer.h"
+
+#include <string.h>
+
+#include "tinydtls.h"
+
+#ifndef DEBUG
+#define DEBUG DEBUG_PRINT
+#endif
[…]

### 2017-11-21 experiments/PingProbe/dtlspingload/dtls-server.c

@@ -1,0 +1,352 @@
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
+#include "net/ip/uip-debug.h"
+#include "net/ip/udp-socket.h"
+#include "clock.h"
+#include "watchdog.h"
+
+#ifdef SERVER_RPL_DAG
+#include "net/rpl/rpl.h"
+#endif
+
+#include <string.h>
+#include "tinydtls.h"
+#include "debug.h"
+#include "dtls.h"
+
+#ifndef DEBUG
+#define DEBUG DEBUG_PRINT
+#endif
+
+#define UIP_IP_BUF   ((struct uip_ip_hdr *)&uip_buf[UIP_LLH_LEN])
+#define UIP_UDP_BUF  ((struct uip_udp_hdr *)&uip_buf[UIP_LLIPH_LEN])
+#define INVALID_COMMAND "INVALID COMMAND\r\n"
+#define MAX_PAYLOAD_LEN 120
+#define MAX_BUF 128
+
+//Enable NULL_REPLY to measure the base response time.
+#define NULL_REPLY 0
+//Enable to use alternative ReadSensors().
+#define READ_SENSORS_ADD 0
+#define READ_SENSORS_MUL 0
+#define READ_SENSORS_MOD 1
+
+#define SAMPLING_SPACE 10000
+
+static struct udp_socket server_conn;
+static dtls_context_t *dtls_context = NULL;
+
+#ifdef SERVER_RPL_DAG
+static void create_rpl_dag(uip_ipaddr_t * ipaddr)
+{
+
+    struct uip_ds6_addr *root_if;
+
+    root_if = uip_ds6_addr_lookup(ipaddr);
+    if (root_if != NULL) {
+        rpl_dag_t *dag;
+        uip_ipaddr_t prefix;
+
+        rpl_set_root(RPL_DEFAULT_INSTANCE, ipaddr);
+        dag = rpl_get_any_dag();
+        uip_ip6addr(&prefix, 0xaaaa, 0, 0, 0, 0, 0, 0, 0);
+        rpl_set_prefix(dag, &prefix, 64);
+        PRINTF("created a new RPL dag\n");
+    } else {
+        PRINTF("failed to create a new RPL DAG\n");
+    }
+    return;
+}
+
+static void set_global_address(void)
+{
+    static uip_ipaddr_t ipaddr;
[…]

### 2017-11-21 experiments/PingProbe/dtlspingload/project-conf.h

@@ -1,0 +1,23 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+#define UIP_CONF_TCP                   0
+
+//RDC driver
+//#undef NETSTACK_CONF_RDC
+//#define NETSTACK_CONF_RDC nullrdc_driver
+//#define NETSTACK_CONF_RDC contikimac_driver
+//#define NETSTACK_CONF_RDC sicslowmac_driver
+//#define NETSTACK_CONF_RDC cxmac_driver
+
+//MAC driver
+#if 0
+#undef NETSTACK_CONF_MAC
+#define NETSTACK_CONF_MAC nullmac_driver
+#endif
+
+//#define NETSTACK_CONF_RDC_CHANNEL_CHECK_RATE 8
+
+//#define SERVER_RPL_DAG
+
+#endif

### 2017-11-21 experiments/PingProbe/dtlspingload/sendget.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+sleep 5
+
+while (( 1 ))
+do
+	echo GET
+	sleep 3
+done

### 2017-11-21 experiments/PingProbe/sensorpayload/extract.sh

@@ -1,0 +1,88 @@
+#!/bin/bash
+
+HELPMSG="Usage: extract [-h|--help] [-s|--sort] [-a|--all] [-t|--time] [-n|--nonzero] LOGFILE"
+
+if [ $# -eq 0 ]
+then
+	echo $HELPMSG;
+	exit;
+fi
+
+for arg in "$@"
+do
+	case $arg in
+		-a|--all)
+			ALL=1;
+			;;
+		-t|--time)
+			TIME=1;
+			;;
+		-n|--nonzero)
+			NONZERO=1;
+			;;
+		-s|--sort)
+			SORT=1;
+			;;
+		-r|--responsed)
+			RESPONSED=1;
+			;;
+		-h|--help)
+			echo $HELPMSG;
+			exit;
+			;;
+		*)
+			LOGFILE+="$arg ";
+			;;
+	esac
+done
+
+#printf "Logfile: %s\n" $LOGFILE;
+
+cat $LOGFILE | gawk  '
+#BEGIN{print "---BEGIN---"}
+{
+if($1 !~ /rtt|---|PING/ && $2 != "packets" && $3 ~ /bytes|answer/)
+	{
+		time=$1;
+		seq=$6;
+		ping=$8;
+		if($time!="" && ping=="") ping="time=0";
+		#print time"\t"ping
+		print seq"\t"time"\t"ping
+	}
+}
+#END{print "---END---"}'|\
+sed -r 's/\[//g; s/\]//g; s/icmp_seq=//g; s/time=//g;' | sort -n |\
+gawk -v all=$ALL -v time=$TIME -v nonzero=$NONZERO -v sorted=$SORT -v responsed=$RESPONSED '
+{
+	pingtimes[$1] = $2;
+	pingvalues[$1] = $3;
+}
+END {
+	if ( sorted )
+	{
+		asort(pingvalues);
+		for ( i = 1; i in pingvalues; i++){
+			if( responsed && pingvalues[i] == 0 )
+				continue;
+			printf "%-5.1f\n", pingvalues[i];
+		}
+	}
+	else 
+	{
+		basetime = pingtimes[1];
+		for (i = 1; i in pingvalues; i++){
+			if( responsed && pingvalues[i] == 0 )
+				continue;
+			if( all )
+				printf "%-5d\t%-10.5f\t%-5.1f\n", i, (pingtimes[i] - basetime), pingvalues[i];	#Print icmp_sqe, date and ping.
+			else if( time )
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/project-conf.h

@@ -1,0 +1,3 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+#endif

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload.c

@@ -1,0 +1,117 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+
+#define APP_VERSION "8"
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+#define APP_NAME (("Sensorpayload_" APP_VERSION " Process"))
+
+/*---------------------------------------------------------------------------*/
+PROCESS(sensorpayload_process, APP_NAME);
+AUTOSTART_PROCESSES(&sensorpayload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+static int getvdd()
+{
+	return vdd3_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+inline void Payload()
+{
+    int data[3] = {0};
+
+    //data[0] = gettemp();
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_1.c

@@ -1,0 +1,70 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/light-sensor.h"
+
+#include <stdio.h>		/* For printf() */
+
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, "randpayload Process");
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static int gettemp()
+{
+	return ((sht11_sensor.value(SHT11_SENSOR_TEMP)));
+}
+
+static int getambientlight()
+{
+	return light_sensor.value(LIGHT_SENSOR_PHOTOSYNTHETIC);
+}
+
+inline void Payload()
+{
+    int temperature, ambientlight;
+
+    temperature = gettemp();
+    ambientlight = getambientlight();
+    printf("Temperature:%d\nAmbient Light:%d\n", temperature, ambientlight);
+
+    return;
+}
+
+PROCESS_THREAD(pingload_process, ev, data)
+{
+    static struct etimer et;
+
+
+    PROCESS_BEGIN();
+
+    printf("Hello, world\n");
+
+    leds_init();
+    SENSORS_ACTIVATE(light_sensor);
+    SENSORS_ACTIVATE(sht11_sensor);
+
+    while (1)
+      {
+	  //Periodically sleep.
+	  leds_on(LEDS_BLUE);
+	  etimer_set(&et, ((1*CLOCK_SECOND)));
+	  PROCESS_WAIT_EVENT_UNTIL(etimer_expired(&et));
+	  leds_off(LEDS_BLUE);
+	  //Do payload.
+	  leds_on(LEDS_RED);
+	  Payload();
+	  leds_off(LEDS_RED);
+      }
+
+    PROCESS_END();
+}
+
+/*---------------------------------------------------------------------------*/

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_2.c

@@ -1,0 +1,105 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, "randpayload Process");
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+inline void Payload()
+{
+    uint16_t data[2];
+
+    data[0] = gettemp();
+    data[1] = getambientlight();
+    encrypt(data, sizeof(data), mykey);
+    uip_udp_packet_sendto(client_conn, data, sizeof(data),
+                        &server_ipaddr, UIP_HTONS(UDP_SERVER_PORT));
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_3.c

@@ -1,0 +1,106 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, "randpayload Process");
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+inline void Payload()
+{
+    uint16_t data[2] = {0};
+
+    data[0] = gettemp();
+    //data[1] = getambientlight();
+    encrypt(data, sizeof(data), mykey);
+    uip_udp_packet_sendto(client_conn, data, sizeof(data),
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_4.c

@@ -1,0 +1,111 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+
+#define APP_VERSION "4"
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+#define APP_NAME (("Sensorpayload_" APP_VERSION "Process"))
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, APP_NAME);
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+inline void Payload()
+{
+    uint32_t data[2] = {0};
+
+    //data[0] = gettemp();
+    data[1] = getambientlight();
+    encrypt(data, sizeof(data), mykey);
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_5.c

@@ -1,0 +1,117 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+
+#define APP_VERSION "5"
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+#define APP_NAME (("Sensorpayload_" APP_VERSION " Process"))
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, APP_NAME);
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+static int getvdd()
+{
+	return vdd3_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+inline void Payload()
+{
+    int data[3] = {0};
+
+    //data[0] = gettemp();
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_6.c

@@ -1,0 +1,117 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+
+#define APP_VERSION "6"
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+#define APP_NAME (("Sensorpayload_" APP_VERSION " Process"))
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, APP_NAME);
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+static int getvdd()
+{
+	return vdd3_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+inline void Payload()
+{
+    int data[3] = {0};
+
+    //data[0] = gettemp();
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_7.c

@@ -1,0 +1,117 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+
+#define APP_VERSION "7"
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+#define APP_NAME (("Sensorpayload_" APP_VERSION " Process"))
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, APP_NAME);
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+static int getvdd()
+{
+	return vdd3_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+inline void Payload()
+{
+    int data[3] = {0};
+
+    data[0] = gettemp();
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_8.c

@@ -1,0 +1,117 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+
+#define APP_VERSION "8"
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+#define APP_NAME (("Sensorpayload_" APP_VERSION " Process"))
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, APP_NAME);
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+static int getvdd()
+{
+	return vdd3_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+inline void Payload()
+{
+    int data[3] = {0};
+
+    //data[0] = gettemp();
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/sensorpayload_9.c

@@ -1,0 +1,116 @@
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+//#include "watchdog.h"
+#include "random.h"
+#include "dev/leds.h"
+#include "dev/sht11/sht11-sensor.h"
+#include "dev/cc2538-sensors.h"
+#include "dev/als-sensor.h"
+#include "lib/ccm-star.h"
+
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-udp-packet.h"
+#include "net/rpl/rpl.h"
+
+#include <stdio.h>		/* For printf() */
+
+
+#define APP_VERSION "9"
+
+#define PERIOD_TIME ((CLOCK_SECOND * 2))
+
+#define UDP_CLIENT_PORT 8775
+#define UDP_SERVER_PORT 5688
+
+#define APP_NAME (("Sensorpayload_" APP_VERSION " Process"))
+
+/*---------------------------------------------------------------------------*/
+PROCESS(pingload_process, APP_NAME);
+AUTOSTART_PROCESSES(&pingload_process);
+/*---------------------------------------------------------------------------*/
+
+static struct uip_udp_conn *client_conn;
+static uip_ipaddr_t server_ipaddr;
+
+#define MY_AES_128_KEY {\
+	0x00, 0x01, 0x02, 0x03,\
+	0x04, 0x05, 0x06, 0x07,\
+	0x08, 0x09, 0x0A, 0x0B,\
+	0x0C, 0x0D, 0x0E, 0x0F\
+}
+
+static uint8_t mykey[] = MY_AES_128_KEY;
+static uint8_t nonce[16] = {0};
+
+void encrypt(void* data, size_t datalen, uint8_t *key)
+{
+	CCM_STAR.set_key(key);
+	CCM_STAR.ctr(data, datalen, nonce);
+	return;
+}
+
+static int gettemp()
+{
+	return cc2538_temp_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+static int getambientlight()
+{
+	return als_sensor.value(0);
+}
+
+static int getvdd()
+{
+	return vdd3_sensor.value(CC2538_SENSORS_VALUE_TYPE_CONVERTED);
+}
+
+inline void Payload()
+{
+    int data[3] = {0};
+
+    data[0] = gettemp();
[…]

### 2017-11-21 experiments/PingProbe/sensorpayload/udpsink.py

@@ -1,0 +1,14 @@
+#!/usr/bin/python
+
+import socket
+
+UDP_IP = "aaaa::1"
+UDP_PORT = 5688
+
+sock = socket.socket(socket.AF_INET6, # Internet
+                     socket.SOCK_DGRAM) # UDP
+sock.bind((UDP_IP, UDP_PORT))
+
+while True:
+    data, addr = sock.recvfrom(1024) # buffer size is 1024 bytes
+    print "received message."

### 2017-11-21 experiments/borderest/borderest.c

@@ -1,0 +1,413 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+/**
+ * \file
+ *         border-router
+ * \author
+ *         Niclas Finne <nfi@sics.se>
+ *         Joakim Eriksson <joakime@sics.se>
+ *         Nicolas Tsiftes <nvt@sics.se>
+ */
+
+#include "contiki.h"
[…]

### 2017-11-21 experiments/borderest/connect.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+sudo make connect-router

### 2017-11-21 experiments/borderest/resources/res-hello.c

@@ -1,0 +1,81 @@
+/*
+ * Copyright (c) 2013, Institute for Pervasive Computing, ETH Zurich
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ */
+
+/**
+ * \file
+ *      Example resource
+ * \author
+ *      Matthias Kovatsch <kovatsch@inf.ethz.ch>
+ */
+
+#include <stdlib.h>
+#include <string.h>
[…]

### 2017-11-21 experiments/borderest/resources/res-leds.c

@@ -1,0 +1,187 @@
+/*
+ * Copyright (c) 2013, Institute for Pervasive Computing, ETH Zurich
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ */
+
+/**
+ * \file
+ *      Example resource
+ * \author
+ *      Matthias Kovatsch <kovatsch@inf.ethz.ch>
[…]

### 2017-11-21 experiments/borderest/simple_border.c

@@ -1,0 +1,93 @@
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/rpl/rpl.h"
+
+#include "net/netstack.h"
+#include "dev/button-sensor.h"
+#include "dev/slip.h"
+#include "dev/leds.h"
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <ctype.h>
+
+#define DEBUG DEBUG_NONE
+#include "net/ip/uip-debug.h"
+
+static uip_ipaddr_t prefix;
+static uint8_t prefix_set;
+
+PROCESS(border_router_process, "Border router process");
+
+AUTOSTART_PROCESSES(&border_router_process);
+
+void request_prefix(void)
+{
+    /* mess up uip_buf with a dirty request... */
+    uip_buf[0] = '?';
+    uip_buf[1] = 'P';
+    uip_len = 2;
+    slip_send();
+    uip_len = 0;
+}
+
+static void print_local_addresses(void)
+{
+    int i;
+    uint8_t state;
+
+    PRINTA("Server IPv6 addresses:\n");
+    for (i = 0; i < UIP_DS6_ADDR_NB; i++)
+      {
+	  state = uip_ds6_if.addr_list[i].state;
+	  if (uip_ds6_if.addr_list[i].isused && (state == ADDR_TENTATIVE || state == ADDR_PREFERRED))
+	    {
+		PRINTA(" ");
+		uip_debug_ipaddr_print(&uip_ds6_if.addr_list[i].ipaddr);
+		PRINTA("\n");
+	    }
+      }
+}
+
+
+PROCESS_THREAD(border_router_process, ev, data)
+{
+    static struct etimer et;
+    //static uip_ipaddr_t addr;
+
+    PROCESS_BEGIN();
+
+    prefix_set = 0;
+    NETSTACK_MAC.off(0);
+
+    PROCESS_PAUSE();
+
+    SENSORS_ACTIVATE(button_sensor);
+
+    printf("RPL-Border router started\n");
+
+    while (!prefix_set)
+      {
+	  etimer_set(&et, CLOCK_SECOND);
+	  request_prefix();
+	  PROCESS_WAIT_EVENT_UNTIL(etimer_expired(&et));
+      }
+    NETSTACK_MAC.off(1);
+    print_local_address();
[…]

### 2017-11-21 experiments/borderest/upload.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+sudo make borderest.upload

### 2017-11-21 experiments/brllsec/project-conf.h

@@ -1,0 +1,78 @@
+/*
+ * Copyright (c) 2010, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
[…]

### 2017-11-21 experiments/cc2538rng/Data/bittest.py

@@ -1,0 +1,94 @@
+#!/usr/bin/python
+
+import sys;
+
+#nbit = 16;
+bitwidth = 0;
+window = 2000;
+
+
+ContikiMsg= "\
+Contiki-3.0\
+TI SmartRF06 + cc2538EM\
+ Net: sicslowpan\
+ MAC: CSMA\
+ RDC: ContikiMAC\
+Rime configured with address 00:12:4b:00:04:1e:af:c6\
+";
+
+HelpMsg= "\
+        Usage: bitest.py [HEX_FILE]\
+        ";
+
+#Parse command line arguments.
+def ParseCmdArgs(argc, argv):
+    global datafile;
+
+    if (argc < 2) or ('-h' in argv):
+        print HelpMsg;
+        exit();
+    datafile = open(argv[1]);
+
+    return;
+
+#Main function
+def main(argc, argv):
+    global datafile;
+
+    #Parse command line arguments.
+    ParseCmdArgs(argc, argv);
+
+    #Open log file.
+    #datafile = open(argv[1]);
+    rndbitstream = '';
+ 
+    bitfile = -1;
+    if argc > 2 :
+        bitfile = open(argv[2],'w');
+
+    #Read in data.
+    rndnum = 1;
+    rndlist = list();
+    while rndnum:
+        rndnum = datafile.readline();
+        if rndnum == '\n':
+            continue;
+        if rndnum in ContikiMsg:
+            continue;
+        if rndnum == '':
+            break;
+        if rndnum[0] == '#':
+            continue;
+        #Remove illegal chracters.
+        rndnum.replace('\0','');
+        rndnum.replace(' ','');
+        rndnum.replace('\n','');
+        rndnumlen = len(rndnum);
+
+        if rndnumlen > 4:
+            rndnum = rndnum[:(rndnumlen - 3)];
+        #print rndnum; #DEBUG info.
+
+        #Interpret data as heximal.
+        try:
+            nbit = len(rndnum) * 4;
+            rndval = int(rndnum,16);
+            rndlist.append(rndval);
+            rndbitstream += ('{:0'+str(nbit)+'b}').format(rndval);
+        except:
+            continue;
+
+    #Total sample size.
+    total = len(rndbitstream);
+    print '#Total: {}'.format(total);
+    nzero = rndbitstream.count('0');
+    pzero = 100 * float(nzero) / float(total)
[…]

### 2017-11-21 experiments/cc2538rng/Data/bytetest.py

@@ -1,0 +1,97 @@
+#!/usr/bin/python
+
+import sys;
+
+nbit = 16;
+bitwidth = 0;
+
+ContikiMsg= "\
+Contiki-3.0\
+TI SmartRF06 + cc2538EM\
+ Net: sicslowpan\
+ MAC: CSMA\
+ RDC: ContikiMAC\
+Rime configured with address 00:12:4b:00:04:1e:af:c6\
+";
+
+HelpMsg= "\
+        Usage: bitest.py [HEX_FILE]\
+        ";
+
+bytecount = [0] * 256;
+
+#Parse command line arguments.
+def ParseCmdArgs(argc, argv):
+    global datafile;
+
+    if (argc < 2) or ('-h' in argv):
+        print HelpMsg;
+        exit();
+    datafile = open(argv[1]);
+
+    return;
+
+#Main function
+def main(argc, argv):
+    global datafile;
+
+    #Parse command line arguments.
+    ParseCmdArgs(argc, argv);
+
+    #Open log file.
+    #datafile = open(argv[1]);
+    rndbitstream = '';
+ 
+    bitfile = -1;
+    if argc > 2 :
+        bitfile = open(argv[2],'w');
+
+    #Read in data.
+    rndnum = 1;
+    rndlist = list();
+    while rndnum:
+        rndnum = datafile.readline();
+        if rndnum == '\n':
+            continue;
+        if rndnum in ContikiMsg:
+            continue;
+        if rndnum == '':
+            break;
+        if rndnum[0] == '#':
+            continue;
+        #Remove illegal chracters.
+        rndnum.replace('\0','');
+        rndnum.replace(' ','');
+        rndnum.replace('\n','');
+        rndnumlen = len(rndnum);
+
+        if rndnumlen > 4:
+            rndnum = rndnum[:(rndnumlen - 3)];
+        #print rndnum; #DEBUG info.
+
+        #Interpret data as heximal.
+        try:
+            rndval = int(rndnum,16);
+            rndlist.append(rndval);
+            rndbitstream += ('{:0'+str(nbit)+'b}').format(rndval);
+            bytecount[rndval] += 1;
+        except:
+            continue;
+
+    #Total sample size.
+    total = len(rndbitstream);
+    print '#Total: {}'.format(total);
+    nzero = rndbitstream.count('0');
+    print '#{}/{} {:03f}%'.format(nzero, total - nzero, float(nzero)/float(total));
+
[…]

### 2017-11-21 experiments/cc2538rng/Data/consecutive0.py

@@ -1,0 +1,108 @@
+#!/usr/bin/python
+
+import sys;
+
+ContikiMsg= "\
+Contiki-3.0\
+TI SmartRF06 + cc2538EM\
+ Net: sicslowpan\
+ MAC: CSMA\
+ RDC: ContikiMAC\
+Rime configured with address 00:12:4b:00:04:1e:af:c6\
+";
+
+HelpMsg= "\
+        Usage: bitest.py [HEX_FILE]\
+        ";
+
+#Parse command line arguments.
+def ParseCmdArgs(argc, argv):
+    global datafile;
+
+    if (argc < 2) or ('-h' in argv):
+        print HelpMsg;
+        exit();
+    datafile = open(argv[1]);
+
+    return;
+
+def GetMaxConsecuiveZero(rndnum):
+    nzero = list();
+    count = 0;
+    for i in range(0,len(rndnum)):
+        if rndnum[i] == '0':
+            count += 1;
+        else:
+            nzero.append(count);
+            count = 0;
+    nzero.append(count);
+
+    return max(nzero);
+
+#Main function
+def main(argc, argv):
+    global datafile;
+
+    #Parse command line arguments.
+    ParseCmdArgs(argc, argv);
+
+    #Open log file.
+    #datafile = open(argv[1]);
+    rndbitstream = '';
+ 
+    bitfile = -1;
+    if argc > 2 :
+        bitfile = open(argv[2],'w');
+
+    #Read in data.
+    rndnum = 1;
+    rndlist = list();
+    nzerolist = list();
+    while rndnum:
+        rndnum = datafile.readline();
+        if rndnum == '\n':
+            continue;
+        if rndnum in ContikiMsg:
+            continue;
+        if rndnum == '':
+            break;
+        if rndnum[0] == '#':
+            continue;
+        #Remove illegal chracters.
+        rndnum.replace('\0',"");
+        rndnum.replace(' ',"");
+        rndnum.replace('\r',"");
+        rndnum.replace('\n','');
+        l=list(rndnum);
+        while '\n' in l:
+            l.remove('\n');
+        rndnum = ''.join(l);
+
+        #print "{}({})".format(rndnum,len(rndnum)); #DEBUG info.
+        
+        #Interpret data as heximal.
+        try:
+            nbit = len(rndnum) * 4;
+            rndval = int(rndnum,16);
+            rndlist.append(rndval);
[…]

### 2017-11-21 experiments/cc2538rng/Data/livebitplot.py

@@ -1,0 +1,53 @@
+#!/usr/bin/python
+
+import numpy as np;
+import matplotlib.pyplot as plt;
+import matplotlib.animation as animation;
+import sys;
+
+HelpMsg="Usage: Plot data from stdin."
+
+windowsize = 100; #Window size
+rndv = [0.5] * windowsize; #Initialise buffer to 0.5.
+plotwidth = 0.02;
+updateinterval = 1;
+
+def update(data):
+    line.set_ydata(data);
+    return line,
+
+def data_gen():
+    while True:
+        #Read new value from stdin.
+        newval = sys.stdin.readline();
+        #if newval[0] == '#':
+        #    continue;
+
+        try:
+            #Append the latest value to the end.            
+            rndv.append(float(newval));
+        except:
+            continue;
+        #Pop out the oldest value.
+        rndv.pop(0);
+        #print(rndv); #For debug use.
+        yield rndv;
+
+fig, ax = plt.subplots();
+ax.set_ylim(0.5 - plotwidth, 0.5 + plotwidth); #Y axis
+line, = ax.plot(np.random.rand(windowsize));
+
+def main(argc, argv):
+    global ax;
+
+    if "-h" in argv:
+        print(HelpMsg);
+        exit(0);
+
+    ani = animation.FuncAnimation(fig, update, data_gen, interval = updateinterval);
+    plt.grid(True);
+    plt.show();
+    exit(0);
+
+if __name__ == "__main__":
+     main(len(sys.argv),sys.argv);

### 2017-11-21 experiments/cc2538rng/Data/livebittest.py

@@ -1,0 +1,55 @@
+#!/usr/bin/python -u
+
+import sys;
+
+windowsize = 128 * 100;
+HelpMsg="Usage: Read stdin and computes frequency of bit 0."
+
+def ParseCmdArg(argc, argv):
+    if "-h" in argv:
+        print HelpMsg;
+        exit();
+
+    return;
+
+def main(argc, argv):
+    #Parse command line argument.
+    ParseCmdArg(argc, argv);
+
+    windowbuffer = "";
+    while 1:
+        #Read in a newline
+        newline = sys.stdin.readline();
+        if newline == '':
+            break;
+        #Skip comments and blank line.
+        if newline[0] in {'\n', '#'}:
+            continue;
+        #Compute the length of new bitstring. -1 for '\n'.
+        rndlen = 4 * (len(newline) - 1);
+
+        #Convert into binary form.
+        try:
+            rndval = int(newline, 16);
+            bitstream = ('{:0' + str(rndlen) +'b}').format(rndval);
+        except:
+            continue;
+        
+        #Push data into the beginning of windowbuffer.
+        windowbuffer = bitstream + windowbuffer;
+
+        if len(windowbuffer) < windowsize: #Not enough data.
+            print "#Waiting for more data...({}/{})".format(len(windowbuffer),windowsize);
+            continue;
+        else:   #Keep only the latest data.
+            windowbuffer = windowbuffer[:windowsize];
+        #Compute the bit frequency.
+        nzero = windowbuffer.count('0');
+        #print "{}/{}".format(nzero, windowsize);
+        #print "{:.5f}%".format(float(nzero)/float(windowsize));
+        print "{:.4f}".format(float(nzero)/float(windowsize));
+
+    return;
+
+if __name__ == "__main__":
+    main(len(sys.argv),sys.argv);

### 2017-11-21 experiments/cc2538rng/Data/nbitrssi.py

@@ -1,0 +1,26 @@
+#!/usr/bin/python
+
+import sys;
+
+nmax = 8000;
+
+def main(argc, argv):
+    datfile = open(argv[1]);
+    datline = 1;
+    while datline:
+        datline = datfile.readline();
+        if not datline:
+            break;
+
+        datfields = datline.split();
+        if datfields[0] == '#':
+            nbit = datfields[1];
+            rssi = datfields[2];
+            if int(nbit) == 8000:
+                continue;
+            print '{} {}'.format(nbit, rssi);
+
+    return;
+
+if __name__ == "__main__":
+    main(len(sys.argv),sys.argv);

### 2017-11-21 experiments/cc2538rng/biasseed.py

@@ -1,0 +1,266 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+##################################################
+# GNU Radio Python Flow Graph
+# Title: Top Block
+# Generated: Thu Oct  6 11:52:48 2016
+##################################################
+
+if __name__ == '__main__':
+    import ctypes
+    import sys
+    if sys.platform.startswith('linux'):
+        try:
+            x11 = ctypes.cdll.LoadLibrary('libX11.so')
+            x11.XInitThreads()
+        except:
+            print "Warning: failed to XInitThreads()"
+
+from PyQt4 import Qt
+from gnuradio import analog
+from gnuradio import eng_notation
+from gnuradio import gr
+from gnuradio import qtgui
+from gnuradio.eng_option import eng_option
+from gnuradio.filter import firdes
+from gnuradio.qtgui import Range, RangeWidget
+from optparse import OptionParser
+import osmosdr
+import sip
+import sys
+import time
+
+
+class top_block(gr.top_block, Qt.QWidget):
+
+    def __init__(self):
+        gr.top_block.__init__(self, "Top Block")
+        Qt.QWidget.__init__(self)
+        self.setWindowTitle("Top Block")
+        try:
+            self.setWindowIcon(Qt.QIcon.fromTheme('gnuradio-grc'))
+        except:
+            pass
+        self.top_scroll_layout = Qt.QVBoxLayout()
+        self.setLayout(self.top_scroll_layout)
+        self.top_scroll = Qt.QScrollArea()
+        self.top_scroll.setFrameStyle(Qt.QFrame.NoFrame)
+        self.top_scroll_layout.addWidget(self.top_scroll)
+        self.top_scroll.setWidgetResizable(True)
+        self.top_widget = Qt.QWidget()
+        self.top_scroll.setWidget(self.top_widget)
+        self.top_layout = Qt.QVBoxLayout(self.top_widget)
+        self.top_grid_layout = Qt.QGridLayout()
+        self.top_layout.addLayout(self.top_grid_layout)
+
+        self.settings = Qt.QSettings("GNU Radio", "top_block")
+        self.restoreGeometry(self.settings.value("geometry").toByteArray())
+
+        ##################################################
+        # Variables
[…]

### 2017-11-21 experiments/cc2538rng/cc2538seed.c

@@ -1,0 +1,192 @@
+#ifdef CONTIKI_TARGET_CC2538DK
+
+#include "contiki.h"
+#include "sys/rtimer.h"
+#include "lib/random.h"
+#include "dev/serial-line.h"
+#include "lpm.h"
+#include "dev/leds.h"
+
+#include "dev/rfcore.h"
+#include "dev/cc2538-rf.h"
+#include "dev/soc-adc.h"
+#include "dev/sys-ctrl.h"
+#include "reg.h"
+#include "net/netstack.h"
+
+#include <stdio.h>		/* For printf() */
+#include <stdlib.h>
+/*---------------------------------------------------------------------------*/
+PROCESS (prng_test_process, "PRNG test");
+AUTOSTART_PROCESSES (&prng_test_process);
+/*---------------------------------------------------------------------------*/
+
+#define VERBOSE 1
+#define WAIT_TIME ((CLOCK_SECOND * 0.1))
+#define SEEDLEN ((16))		//Seed length in bytes.
+
+static struct etimer et;
+
+unsigned short
+ReadRnd ()
+{
+  return REG (SOC_ADC_RNDL) | (REG (SOC_ADC_RNDH) << 8);
+}
+
+void
+printseed (unsigned char *seedval, size_t seedlen)
+{
+  size_t i;
+
+  if (seedlen <= 0)
+    return;
+
+  for (i = 0; i < seedlen; i++)
+    printf ("%02X", seedval[i]);
+  return;
+}
+
+void
+RfRnd (unsigned char *seed, size_t seedlen)
+{
+  int i = 0, j = 0;
+  unsigned char s = 0;
+  int overheated = 0;
+  unsigned char rndiq;
+#if VERBOSE
+  static unsigned int prnd[4] = { 0 };
+  int rssi = 0, freqest = 0;
+  unsigned char agc_gain, lna1, lna2, lna3;
+#endif
+
+  memset (seed, 0, seedlen);
+
+  /* Make sure the RNG is on */
+  REG (SOC_ADC_ADCCON1) &= ~(SOC_ADC_ADCCON1_RCTRL1 | SOC_ADC_ADCCON1_RCTRL0);
+
+  /* Enable clock for the RF Core */
+  REG (SYS_CTRL_RCGCRFC) = 1;
+
+  /* Wait for the clock ungating to take effect */
+  while (REG (SYS_CTRL_RCGCRFC) != 1);
+
[…]

### 2017-11-21 experiments/cc2538rng/genr.py

@@ -1,0 +1,67 @@
+#!/usr/bin/python
+
+import os;
+import sys;
+import subprocess;
+
+#from joblib import Parallel, delayed
+#import multiprocessing
+import multiprocessing
+from multiprocessing import Pool
+
+#Configurations
+order = 1024; #Order of cyclic PRNG group.
+parallel = 1;
+parallel_level = 4;
+
+#Lookup table.
+class KeySigPair:
+    key = 0
+    sig = 0
+
+    def __init__(self, inputkey, inputsig):
+        self.key = inputkey;
+        self.sig = inputsig;
+
+def ComputeEntry(key):
+#    key = ''.join(prngstream[idx:(idx+32)]);
+    process = subprocess.Popen(["secp256r1mult", key], stdout = subprocess.PIPE);
+    out, err = process.communicate();
+    sig = out.decode("utf-8").replace('\n','');
+    return KeySigPair(key,sig);
+   
+
+#Main()
+def main():
+    prngfile = open(sys.argv[1]);
+
+    prngstream = list();
+    prng = 1;
+    while prng:
+        prng = prngfile.readline().replace('\n','');
+        prngstream.append(prng);
+
+    keylist = list();
+    for i in range(0,order):
+        keylist.append(''.join(prngstream[i:(i+32)]));
+
+    lookuptbl = list();
+    if not parallel:
+        #Non parallel...
+        print("#Using non-parallel method...");
+        for i in range(0,order):
+           lookuptbl.append(ComputeEntry(keylist[i]));
+    else:
+        #PARALLEL!!!!!!!
+        print("#Using parallel method...");
+        num_cores = multiprocessing.cpu_count();
+        print("#Number of cores:%d" % num_cores);
+        print("#Parallel level: %d" % parallel_level);
+        pool = Pool(parallel_level);
+        lookuptbl = pool.map(ComputeEntry,keylist);
+
+    for idx,entry in enumerate(lookuptbl):
+        print("#Key %d:\n %s %s" % (idx, entry.key, entry.sig));
+
+if __name__ == "__main__":
+    main();

### 2017-11-21 experiments/cc2538rng/prngtest.c

@@ -1,0 +1,54 @@
+#include "contiki.h"
+#include "sys/rtimer.h"
+#include "lib/random.h"
+#include "dev/serial-line.h"
+#include "lpm.h"
+
+#include <stdio.h> /* For printf() */
+/*---------------------------------------------------------------------------*/
+PROCESS(prng_test_process, "PRNG test");
+AUTOSTART_PROCESSES(&prng_test_process);
+/*---------------------------------------------------------------------------*/
+
+static unsigned char appearance[8192] =  {0};
+
+unsigned short GetMark(unsigned short val)
+{
+	return (0xFFFF & (appearance[val/8] & (0x1 << (val % 8)) ));
+}
+
+void SetMark(unsigned short val)
+{
+	appearance[val/8] |= (0x1 << (val % 8));
+	return;
+}
+
+PROCESS_THREAD(prng_test_process, ev, data)
+{
+  static unsigned short rndval;
+  static unsigned int count;
+  static unsigned char *rndptr = (void*) &rndval;
+  
+  PROCESS_BEGIN();
+
+  lpm_set_max_pm(LPM_PM0);
+
+  printf("#Press Enter to start:");
+  PROCESS_WAIT_EVENT_UNTIL(ev == serial_line_event_message);
+  
+  for(count = 1; count <= 0xFFFF; count++)
+  {
+	rndval = random_rand();
+	printf("#Count: %d\n", count);
+	printf("%02X%02X\n",rndptr[0], rndptr[1]);
+	if(GetMark(rndval))
+	{
+		printf("#Collision found: ");
+		printf("%02X%02X\n",rndptr[0], rndptr[1]);
+	}
+	SetMark(rndval);
+  }
+
+  PROCESS_END();
+}
+/*---------------------------------------------------------------------------*/

### 2017-11-21 experiments/cc2538rng/project-conf.h

@@ -1,0 +1,46 @@
+/*
+ * Copyright (c) 2012, Texas Instruments Incorporated - http://www.ti.com/
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ *
+ * 3. Neither the name of the copyright holder nor the names of its
+ *    contributors may be used to endorse or promote products derived
+ *    from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * ``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS
+ * FOR A PARTICULAR PURPOSE ARE DISCLAIMED.  IN NO EVENT SHALL THE
+ * COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT,
+ * INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+ * (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
+ * SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT,
+ * STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
+ * ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED
+ * OF THE POSSIBILITY OF SUCH DAMAGE.
+ */
+/**
+ * \addtogroup cc2538-examples
+ * @{
+ *
+ * \file
[…]

### 2017-11-21 experiments/coapllsec/project-conf.h

@@ -1,0 +1,98 @@
+/*
+ * Copyright (c) 2013, Institute for Pervasive Computing, ETH Zurich
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ */
+
+/**
+ * \file
+ *      Erbium (Er) example project configuration.
+ * \author
+ *      Matthias Kovatsch <kovatsch@inf.ethz.ch>
[…]

### 2017-11-21 experiments/coaptime/er-example-server.c

@@ -1,0 +1,188 @@
+/*
+ * Copyright (c) 2013, Institute for Pervasive Computing, ETH Zurich
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ */
+
+/**
+ * \file
+ *      Erbium (Er) REST Engine example.
[…]

### 2017-11-21 experiments/coaptime/project-conf.h

@@ -1,0 +1,89 @@
+/*
+ * Copyright (c) 2013, Institute for Pervasive Computing, ETH Zurich
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ */
+
+/**
+ * \file
+ *      Erbium (Er) example project configuration.
+ * \author
[…]

### 2017-11-21 experiments/coaptime/resources/res-cc2538dksensors.c

@@ -1,0 +1,140 @@
+/*
+ * Copyright (c) 2013, Institute for Pervasive Computing, ETH Zurich
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ */
+
+/**
+ * \file
+ *      Example resource
+ * \author
+ *      Matthias Kovatsch <kovatsch@inf.ethz.ch>
+ */
+
+#include <stdlib.h>
[…]

### 2017-11-21 experiments/coaptime/resources/res-random-rand.c

@@ -1,0 +1,75 @@
+/*
+ * Copyright (c) 2013, Institute for Pervasive Computing, ETH Zurich
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ */
+
+/**
+ * \file
+ *      Example resource
+ * \author
+ *      Matthias Kovatsch <kovatsch@inf.ethz.ch>
+ */
+
+#include <stdlib.h>
+#include <string.h>
[…]

### 2017-11-21 experiments/coaptime/resources/res-timing.c

@@ -1,0 +1,72 @@
+/*
+ * Copyright (c) 2013, Institute for Pervasive Computing, ETH Zurich
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ */
+
+/**
+ * \file
+ *      Example resource
+ * \author
+ *      Matthias Kovatsch <kovatsch@inf.ethz.ch>
+ */
+
+#include <stdlib.h>
+#include <string.h>
+#include "rest-engine.h"
+//#include "timing.h"
+
[…]

### 2017-11-21 experiments/dtlsaes/aestest_fixed.c

@@ -1,0 +1,151 @@
+#include "contiki.h"
+#include "sys/rtimer.h"
+#include "sys/etimer.h"
+#include "lib/random.h"
+
+#include "aes/rijndael.h"
+
+#include <stdio.h>              /* For printf() */
+#include <string.h>
+
+#define AES_KEY_LEN 16
+#define AES_BLOCK_LEN 16
+
+#ifndef NROUND
+#define NROUND 200
+#endif
+
+#ifndef NSAMPLE
+#define NSAMPLE 100
+#endif
+
+static rijndael_ctx aes_ctx;
+
+static uint8_t Aes128Key[AES_KEY_LEN] = {
+    0x01, 0x23, 0x45, 0x67,
+    0x89, 0xab, 0xcd, 0xef,
+    0x12, 0x34, 0x56, 0x78,
+    0x9a, 0xbc, 0xde, 0xf0
+};
+
+static const uint8_t fixed_data[AES_BLOCK_LEN] = {
+    0xda, 0x39, 0xa3, 0xee,
+    0x54, 0x6b, 0x4b, 0x0d,
+    0x32, 0x55, 0xbf, 0xef,
+    0x95, 0x60, 0x18, 0x90
+};
+
+static uint8_t dummyplaintext[AES_BLOCK_LEN] = { 0 };
+static uint8_t dummyciphertext[AES_BLOCK_LEN] = { 0 };
+
+static uint8_t plaintext[NROUND][AES_BLOCK_LEN] = { {0} };
+static uint8_t ciphertext[NROUND][AES_BLOCK_LEN] = { {0} };
+
+void PrintBlock(const char *prefix, const uint8_t * block,
+                const char *appendix)
+{
+    int i;
+
+    printf(prefix);
+    for (i = 0; i < AES_KEY_LEN; i++)
+        printf("%02x ", block[i]);
+    printf(appendix);
+    return;
+}
+
+int calibrate()
+{
+    int i;
+
+    for(i = 0; i < AES_KEY_LEN; i++)
+	Aes128Key[i] ^= 0;
+    for(i = 0; i < NROUND; i++)
+	memcpy(dummyplaintext, plaintext[i], AES_BLOCK_LEN);
+
+    return 0;
+}
+
+void finalise()
+{
+    printf("#Finalise.\n");
+    
+    calibrate();
+
+    return;
+}
+
+/*---------------------------------------------------------------------------*/
+PROCESS(aestest, "aestest");
+AUTOSTART_PROCESSES(&aestest);
[…]

### 2017-11-21 experiments/dtlsaes/aestest_random.c

@@ -1,0 +1,152 @@
+#include "contiki.h"
+#include "sys/rtimer.h"
+#include "sys/etimer.h"
+#include "lib/random.h"
+
+#include "aes/rijndael.h"
+
+#include <stdio.h>              /* For printf() */
+#include <string.h>
+
+#define AES_KEY_LEN 16
+#define AES_BLOCK_LEN 16
+
+#ifndef NROUND
+#define NROUND 200
+#endif
+
+#ifndef NSAMPLE
+#define NSAMPLE 100
+#endif
+
+static rijndael_ctx aes_ctx;
+
+static uint8_t Aes128Key[AES_KEY_LEN] = {
+    0x01, 0x23, 0x45, 0x67,
+    0x89, 0xab, 0xcd, 0xef,
+    0x12, 0x34, 0x56, 0x78,
+    0x9a, 0xbc, 0xde, 0xf0
+};
+
+static const uint8_t fixed_data[AES_BLOCK_LEN] = {
+    0xda, 0x39, 0xa3, 0xee,
+    0x54, 0x6b, 0x4b, 0x0d,
+    0x32, 0x55, 0xbf, 0xef,
+    0x95, 0x60, 0x18, 0x90
+};
+
+static uint8_t dummyplaintext[AES_BLOCK_LEN] = { 0 };
+static uint8_t dummyciphertext[AES_BLOCK_LEN] = { 0 };
+
+static uint8_t plaintext[NROUND][AES_BLOCK_LEN] = { {0} };
+static uint8_t ciphertext[NROUND][AES_BLOCK_LEN] = { {0} };
+
+void PrintBlock(const char *prefix, const uint8_t * block,
+                const char *appendix)
+{
+    int i;
+
+    printf(prefix);
+    for (i = 0; i < AES_KEY_LEN; i++)
+        printf("%02x ", block[i]);
+    printf(appendix);
+    return;
+}
+
+int calibrate()
+{
+    return 0;
+}
+
+void finalise()
+{
+    int i;
+
+    printf("#Finalise.\n");
+    //Randomise the key for next round.
+    for(i = 0; i < AES_KEY_LEN; i++)
+	Aes128Key[i] ^= ciphertext[0][i];
+    //Randomise the plaintext for next round.
+    for(i = 0; i < NROUND; i++)
+	memcpy(plaintext[i], fixed_data, AES_BLOCK_LEN);
+    
+    calibrate();
+
+    return;
+}
+
[…]

### 2017-11-21 experiments/dtlsapptime/Data/rndlen/illustrateFtest.m

@@ -1,0 +1,33 @@
+% Suppose you have model 'sub' nested inside model 'full' and you want to 
+% test the statistical significance of the explanatory variables which
+% appear in 'full' but not 'sub'.
+
+% Suppose Y (column vector) is the dependent variable and Xfull, Xsub the 
+% matrices of explanatory variables for the full and nested models.
+
+% Run the regressions and store the coefficients, residuals and the tables
+% of statistics:
+[Bfull,~,Rfull,~,STATSfull] = regress(Y,Xfull);
+[Bsub,~,Rsub,~,STATSsub] = regress(Y,Xsub);
+
+% Compute the sums of squares of the residuals from both models:
+SSRESfull = sum(Rfull.^2);
+SSRESsub = sum(Rsub.^2);
+
+% Calculate the degrees of freedom for the test:
+% Difference between the numbers of parameters for the full and reduced
+% model:
+df1 = size(Xfull,2) - size(Xsub,2);
+% Difference between the number of observations and the number of
+% parameters for the full model:
+df2 = size(Y,1) - size(Xfull,2);
+
+% Compute the F-statistic:
+Fstat = ((SSRESfull - SSRESsub)./df1)./(SSRESfull./df2);
+
+% Get the critical value of the F distribution at (e.g.) the alpha=0.05 
+% significance level:
+CritVal = finv(1-0.05,df1,df2);
+
+% If Fstat > CritVal then the variables which are in the full model but not
+% the reduced one are jointly significant at the alpha=0.05 level.

### 2017-11-21 experiments/dtlsapptime/Data/rndlen/rndlen.m

@@ -1,0 +1,909 @@
+# Created by Octave 3.8.2, Tue Apr 12 09:39:24 2016 BST <yy12135@salties>
+# name: Bfull
+# type: matrix
+# rows: 6
+# columns: 1
+ 1.961633680555569
+ -0.1105199999999998
+ 0.08902499999999947
+ 0.04556770833332263
+ -0.0006799999999999272
+ -0.0009649999999994828
+
+
+# name: Bsub
+# type: matrix
+# rows: 3
+# columns: 1
+ 1.984417534722227
+ -0.1108599999999997
+ 0.08854249999999972
+
+
+# name: D
+# type: matrix
+# rows: 26
+# columns: 6
+ 5 5 87.59350000000001 84.268 4.8828125 1.557312499999995
+ 5 10 90.122 87.458 4.8828125 2.218812499999999
+ 5 15 92.5805 90.648 4.8828125 2.950312499999995
+ 5 20 95.84450000000001 93.83800000000001 4.8828125 2.876312499999997
+ 5 25 98.392 97.02800000000001 4.8828125 3.51881250000001
+ 5 30 100.848 100.218 4.8828125 4.252812500000005
+ 5 35 104.1865 103.408 4.8828125 4.104312500000006
+ 5 40 106.7365 106.598 4.8828125 4.744312499999992
+ 5 45 109.226 109.788 4.8828125 5.444812500000012
+ 15 25 104.357 102.408 4.8828125 2.933812500000002
+ 25 5 100.4255 95.02800000000001 4.8828125 -0.5146874999999937
+ 25 15 105.433 101.408 4.8828125 0.8578125000000085
+ 25 25 111.3295 107.788 4.8828125 1.341312500000015
+ 25 35 117.1 114.168 4.8828125 1.950812500000012
+ 25 45 122.089 120.548 4.8828125 3.341812500000003
+ 35 25 118.045 113.168 4.8828125 0.005812500000004661
+ 45 25 124.008 118.548 4.8828125 -0.5771874999999795
+ 5 25 118.12 97.02800000000001 24.658203125 3.566203125000001
+ 15 25 124.262 102.408 24.658203125 2.804203125000001
+ 25 5 120.22 95.02800000000001 24.658203125 -0.5337968749999931
[…]

### 2017-11-21 experiments/dtlsapptime/dtls-server-aes.c

@@ -1,0 +1,320 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
+
[…]

### 2017-11-21 experiments/dtlsapptime/dtls-server-len.c

@@ -1,0 +1,322 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
+
[…]

### 2017-11-21 experiments/dtlsapptime/dtls-server.c

@@ -1,0 +1,316 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
+
[…]

### 2017-11-21 experiments/dtlsapptime/sendrequest.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+
+REQUEST=$1
+
+while read -p "Use Ctrl^D to start sending GET:" LINE
+do
+	echo $LINE;
+done
+
+while (( 1 ))
+do
+	echo $REQUEST
+	sleep 1
+done

### 2017-11-21 experiments/dtlsbr/dtlsbr.c

@@ -1,0 +1,610 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+/**
+ * \file
+ *         border-router
+ * \author
+ *         Niclas Finne <nfi@sics.se>
[…]

### 2017-11-21 experiments/dtlsbr/project-conf.h

@@ -1,0 +1,63 @@
+/*
+ * Copyright (c) 2010, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ */
+
+#ifndef PROJECT_ROUTER_CONF_H_
[…]

### 2017-11-21 experiments/dtlsbr/slip-bridge.c

@@ -1,0 +1,156 @@
+/*
+ * Copyright (c) 2010, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ */
+
+/**
+ * \file
+ *         Slip fallback interface
+ * \author
+ *         Niclas Finne <nfi@sics.se>
+ *         Joakim Eriksson <joakime@sics.se>
+ *         Joel Hoglund <joel@sics.se>
[…]

### 2017-11-21 experiments/dtlstime/dtls-server.c

@@ -1,0 +1,313 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
[…]

### 2017-11-21 experiments/dtlstime/project-conf.h

@@ -1,0 +1,18 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+#define UIP_CONF_TCP                   0
+
+#ifdef DISABLE_PSK //Disable PSK
+#ifdef DTLS_PSK
+#undef DTLS_PSK
+#endif
+#endif
+
+#ifdef DISABLE_ECC //Disable ECC
+#ifdef DTLS_ECC
+#undef DTLS_ECC
+#endif
+#endif
+
+#endif

### 2017-11-21 experiments/dtlstime/sendrequest.sh

@@ -1,0 +1,26 @@
+#!/bin/bash
+
+#REQUEST=$1
+l1="" #1 bytes
+l7="123456" #6 bytes
+l12="12345678901" #12 bytes
+l18="12345678901234567" #18 bytes
+l23="1234567890123456789012" #23 bytes
+l29="1234567890123456789012345678" #29 bytes
+l35="1234567890123456789012345678901234" #35 bytes
+l41="1234567890123456789012345678901234567890" #41 bytes
+l46="123456789012345678901234567890123456789012345" #46 bytes
+
+REQUEST=${l46}
+
+
+while read -p "Use Ctrl^D to start sending GET:" LINE
+do
+	echo $LINE;
+done
+
+while (( 1 ))
+do
+	echo $REQUEST
+	sleep 1
+done

### 2017-11-21 experiments/dummysensor/dummysensor.c

@@ -1,0 +1,169 @@
+#include "dummysensor.h"
+
+#include "contiki.h"
+#include "sys/etimer.h"
+#include "sys/timer.h"
+#include "sys/ctimer.h"
+#include "sys/clock.h"
+#include "watchdog.h"
+#include "random.h"
+#include "net/ip/uip.h"
+#include "simple-udp.h"
+
+//#include "dev/als-sensor.h"
+
+#include <stdio.h>		/* For printf() */
+
+#define PAYLOAD	((100))
+#define IDLE	((900))
+
+#ifndef SCALE
+#ifdef SECOND
+#define SCALE CLOCK_SECOND
+#else
+#define SCALE 1
+#endif
+#endif
+
+#define EXPECTED_PAYLOAD ((PAYLOAD * SCALE))
+#define EXPECTED_IDLE ((IDLE * SCALE))
+
+#define WATCHDOG_RESET_PERIOD (( CLOCK_SECOND/2 ))
+
+//The expected payload cycle will be SCALER/GRANULARITY seconds.
+//#define SCALER 1
+//#define GRANULARITY 1
+
+#ifdef LED_INDICATOR
+#include "dev/leds.h"
+#endif
+
+/*---------------------------------------------------------------------------*/
+PROCESS(dummysensor_process, "Dummysensor Process");
+AUTOSTART_PROCESSES(&dummysensor_process);
+/*---------------------------------------------------------------------------*/
+static struct etimer idle_timer;
+static struct timer payload_timer;
+static struct ctimer resetwd_timer;
+
+static struct simple_udp_connection broadcast_connection;
+
+void MyInit()
+{
+	simple_udp_register(&broadcast_connection, 10217, NULL, 10217, NULL);
+
+	return;
+}
+
+inline void Payload()
+{
+    static clock_time_t payload_start, payload_end;
+    
+    static const unsigned int space = 1024, count = 100;
+    unsigned int i, sum, avg;
+    uip_ipaddr_t addr;
+
+    //Payload begin timeing.
+    payload_start = clock_time();
+
+    //Payload
+    for( i = 0, sum = 0; i < count; i++)
+    {
+	sum += random_rand() % space;
+    }
+    avg = sum / count;
+    printf("Average = %d\n", avg);
+    uip_create_linklocal_allnodes_mcast(&addr);
+
+    //Broadcast reading.
[…]

### 2017-11-21 experiments/dummysensor/dummysensor.h

@@ -1,0 +1,19 @@
+#ifndef DUMMYSENSOR_H
+#define DUMMYSENSOR_H
+
+//Uncomment to enable led indicator.
+#define LED_INDICATOR
+
+//Uncomment to use seconds for payload and idle instead of clock ticks.
+//#define SECOND
+
+//Uncomment to enable null_driver instead of ContikiMAC.
+//#define NULL_DRIVER
+
+//Uncomment to use randomised payload period.
+//#define RAND_PAYLOAD
+
+//Uncomment to use randomised idle period.
+#define RAND_IDLE
+
+#endif

### 2017-11-21 experiments/dummysensor/project-conf.h

@@ -1,0 +1,13 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+#define UIP_CONF_TCP                   0
+
+//#ifdef NULL_DRIVER
+//#define NETSTACK_CONF_RDC nullrdc_driver
+//#define NETSTACK_CONF_MAC nullmac_driver
+//#endif
+
+//#define NETSTACK_CONF_RDC_CHANNEL_CHECK_RATE 8
+
+#endif

### 2017-11-21 experiments/dummysensor/save.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+tar -zcf src.tgz dummysensor.c dummysensor.h project-conf.h Makefile

### 2017-11-21 experiments/ecctiming/Data/hmwfilt.m

@@ -1,0 +1,4 @@
+function [ret] = hmwfilt(datasheet, column, value)
+	idx = datasheet(:,column) == value;
+	ret = datasheet(idx);
+endfunction

### 2017-11-21 experiments/ecctiming/ecctiming.c

@@ -1,0 +1,139 @@
+/*
+ * Copyright (c) 2006, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+//This file is tuned for CC2538.
+
+#include <stdlib.h>
+#include <stdio.h>
+#include <string.h>
+#include <inttypes.h>
+
[…]

### 2017-11-21 experiments/ecctiming/ecdsatime_client.c

@@ -1,0 +1,208 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <string.h>
+
+#include "contiki.h"
+#include "dev/serial-line.h"
+#include "lpm.h"
+#include "dev/uart1.h"
+#include "dev/leds.h"
+#include "sys/rtimer.h"
+
+#include "dtls.h"
+#include "ecc/ecc.h"
+#include "tinycrypto.h"
+#include "numeric.h"
+#include "prng.h"
+
+#define HEX 16
+
+#define DTLS_CV_LENGTH (1 + 1 + 2 + 1 + 1 + 1 + 1 + DTLS_EC_KEY_SIZE + 1 + 1 + DTLS_EC_KEY_SIZE)
+
+#define LEDS_ECC_KEY_GEN LEDS_BLUE
+#define LEDS_ECDSA_SIGN LEDS_RED
+
+unsigned char signkey[DTLS_EC_KEY_SIZE] = { 0 };
+unsigned char secretkey[DTLS_EC_KEY_SIZE] = { 0 };
+
+unsigned char ephe_key_sk[DTLS_EC_KEY_SIZE] = { 0 };
+unsigned char ephe_key_pk_x[DTLS_EC_KEY_SIZE] = { 0 };
+unsigned char ephe_key_pk_y[DTLS_EC_KEY_SIZE] = { 0 };
+
+dtls_hash_ctx ecdsa_hash_e;
+
+void PrintInt256(const char *title, unsigned char *i256)
+{
+    int i;
+
+    printf("%s", title);
+    for (i = 0; i < DTLS_EC_KEY_SIZE; i++) {
+        printf("%02X", i256[i]);
+        if ((i + 1) % 4 == 0)
+            printf(" ");
+    }
+    printf("\n");
+    return;
+}
+
+void PrintNonce(uint32_t * nonce)
+{
+    int i;
+
+    for (i = 0; i < DTLS_EC_KEY_SIZE / sizeof(uint32_t); i++) {
+        printf("%08lX ", nonce[i]);
+    }
+    return;
+}
+
+void str2hex(char *str, unsigned char *hexval, size_t len)
+{
+    int nvalid = 0;
+    size_t count;
+    char *cptr;
+    char cbuf[3] = { 0 };
+
+    for (cptr = str, count = 0; count < len; count++) {
+        //Read two hex characters to cbuf.
+        for (nvalid = 0; nvalid < 2; nvalid++, cptr++) {
+            //Find the one valid character each loop.
[…]

### 2017-11-21 experiments/ecctiming/ecdsatime_server.c

@@ -1,0 +1,219 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <string.h>
+
+#include "contiki.h"
+#include "dev/serial-line.h"
+#include "lpm.h"
+#include "dev/uart1.h"
+#include "dev/leds.h"
+#include "sys/rtimer.h"
+
+#include "dtls.h"
+#include "ecc/ecc.h"
+#include "crypto.h"
+#include "numeric.h"
+#include "prng.h"
+
+#define HEX 16
+
+#define DTLS_SKEXEC_LENGTH (1 + 2 + 1 + 1 + DTLS_EC_KEY_SIZE + DTLS_EC_KEY_SIZE + 1 + 1 + 2 + 70)
+
+#define LEDS_ECC LEDS_RED
+
+unsigned char signkey[DTLS_EC_KEY_SIZE] = { 0 };
+unsigned char secretkey[DTLS_EC_KEY_SIZE] = { 0 };
+
+void PrintInt256(const char *title, unsigned char *i256)
+{
+    int i;
+
+    printf("%s", title);
+    for (i = 0; i < DTLS_EC_KEY_SIZE; i++) {
+        printf("%02X", i256[i]);
+        if ((i + 1) % 4 == 0)
+            printf(" ");
+     }
+    printf("\n");
+    return;
+}
+
+void PrintNonce(uint32_t *nonce)
+{
+        int i;
+
+	for (i = 0; i < DTLS_EC_KEY_SIZE / sizeof(uint32_t); i++) {
+	    printf("%08lX ", nonce[i]);
+	 }
+	return;
+}
+
+void str2hex(char *str, unsigned char *hexval, size_t len)
+{
+    int nvalid = 0;
+    size_t count;
+    char *cptr;
+    char cbuf[3] = { 0 };
+
+    for (cptr = str, count = 0; count < len; count++) {
+        //Read two hex characters to cbuf.
+        for (nvalid = 0; nvalid < 2; nvalid++, cptr++) {
+            //Find the one valid character each loop.
+            //Skip redundant characters.
+            for (; *cptr == ' ' || *cptr == ','; cptr++);
+            //Terminate on '\0', ',' or '\n'.
+            if (*cptr == '\0' || *cptr == '\n')
+                break;
+            //Save to cbuf.
+            cbuf[nvalid] = *cptr;
+        }
+        //Convert to integer.
[…]

### 2017-11-21 experiments/ecctiming/prngtest.c

@@ -1,0 +1,100 @@
+/*
+ * Copyright (c) 2006, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+//This file is tuned for CC2538.
+
+#include <stdlib.h>
+#include <stdio.h>
+#include <string.h>
+#include <inttypes.h>
+
+#include "contiki.h"
+#include "dev/serial-line.h"
[…]

### 2017-11-21 experiments/ecctiming/project-conf.h

@@ -1,0 +1,47 @@
+/*
+ * Copyright (c) 2012, Texas Instruments Incorporated - http://www.ti.com/
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ *
+ * 3. Neither the name of the copyright holder nor the names of its
+ *    contributors may be used to endorse or promote products derived
+ *    from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * ``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS
+ * FOR A PARTICULAR PURPOSE ARE DISCLAIMED.  IN NO EVENT SHALL THE
+ * COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT,
+ * INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+ * (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
+ * SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT,
+ * STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
+ * ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED
+ * OF THE POSSIBILITY OF SUCH DAMAGE.
+ */
+/**
+ * \addtogroup cc2538-examples
+ * @{
+ *
+ * \file
[…]

### 2017-11-21 experiments/echodtls/project-conf.h

@@ -1,0 +1,42 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+#ifdef UIP_CONF_TCP
+#undef UIP_CONF_TCP
+#define UIP_CONF_TCP                   0
+#endif
+
+//Disable Watchdog for ECC timeout
+#define WATCHDOG_CONF_ENABLE 0
+
+//Change Packet buffer setting for exceedingly large handshake packets.
+#ifndef QUEUEBUF_CONF_NUM
+#define QUEUEBUF_CONF_NUM          64
+#endif
+
+#ifndef UIP_CONF_BUFFER_SIZE
+#define UIP_CONF_BUFFER_SIZE    256
+#endif
+
+#ifndef UIP_CONF_RECEIVE_WINDOW
+#define UIP_CONF_RECEIVE_WINDOW  120
+#endif
+
+//Disable PSK
+#ifdef NO_PSK
+#ifdef DTLS_PSK
+#undef DTLS_PSK
+#endif //End of DTLS_PSK
+#endif //End of NO_PSK
+
+//Disable ECC
+#ifdef NO_ECC
+#ifdef DTLS_ECC
+#undef DTLS_ECC
+#endif //End of DTLS_ECC
+#endif //End of NO_ECC
+
+#define ECDSA_TIMING
+#define ECDSA_PRNG_ATTACK
+
+#endif

### 2017-11-21 experiments/hellollsec/hello-world.c

@@ -1,0 +1,58 @@
+/*
+ * Copyright (c) 2006, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+/**
+ * \file
+ *         A very simple Contiki application showing how Contiki programs look
+ * \author
+ *         Adam Dunkels <adam@sics.se>
+ */
+
+#include "contiki.h"
+
+#include <stdio.h> /* For printf() */
[…]

### 2017-11-21 experiments/hellollsec/project-conf.h

@@ -1,0 +1,50 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+
+#ifdef UIP_CONF_TCP
+#undef UIP_CONF_TCP
+#define UIP_CONF_TCP 0 //Disable TCP for space optimise.
+#endif //End of #ifdef UIP_CONF_TCP
+
+//RDC driver
+//#undef NETSTACK_CONF_RDC
+//#define NETSTACK_CONF_RDC nullrdc_driver
+//#define NETSTACK_CONF_RDC contikimac_driver
+
+//MAC driver
+//#undef NETSTACK_CONF_MAC
+//#define NETSTACK_CONF_MAC nullmac_driver
+
+//Channel check rate
+//#define NETSTACK_CONF_RDC_CHANNEL_CHECK_RATE 8
+
+//LLSEC configurations.
+#ifdef ENABLE_LLSEC
+
+#undef NETSTACK_CONF_LLSEC
+#define NETSTACK_CONF_LLSEC noncoresec_driver
+
+#undef LLSEC802154_CONF_SECURITY_LEVEL
+#define LLSEC802154_CONF_SECURITY_LEVEL 7
+
+#undef NONCORESEC_CONF_KEY
+#define NONCORESEC_CONF_KEY {\
+	0x00 , 0x01 , 0x02 , 0x03 ,\
+	0x04 , 0x05 , 0x06 , 0x07 ,\
+	0x08 , 0x09 , 0x0A , 0x0B ,\
+	0x0C , 0x0D , 0x0E , 0x0F \
+}
+
+//Uncomment to disable Hardware AES-128 coprosessor.
+#ifdef AES_128_CONF
+//#undef AES_128_CONF
+#endif //End of #ifdef AES_128_CONF
+
+#endif //End of #ifdef ENABLE_LLSEC
+
+#ifdef CONTIKI_TARGET_CC2538DK 
+#define PRIu32 "lu" 
+#endif //End of #ifdef CONTIKI_TARGET_CC2538DK
+
+#endif //End of #ifdef __PROJECT_CONF_H__

### 2017-11-21 experiments/keydtls/dtls-server.c

@@ -1,0 +1,204 @@
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
+
+#include <string.h>
+
+#include "tinydtls.h"
+
+#ifndef DEBUG
+#define DEBUG DEBUG_PRINT
+#endif
+#include "net/ip/uip-debug.h"
+#include "net/ip/udp-socket.h"
+
+//#include "debug.h"
+#include "dtls.h"
+
+#define UIP_IP_BUF   ((struct uip_ip_hdr *)&uip_buf[UIP_LLH_LEN])
+#define UIP_UDP_BUF  ((struct uip_udp_hdr *)&uip_buf[UIP_LLIPH_LEN])
+#define INVALID_COMMAND "INVALID COMMAND\r\n"
+
+static struct udp_socket server_conn;
+static dtls_context_t *dtls_context = NULL;
+
+void DtlsServerCb (struct udp_socket *c, void *ptr,
+		   const uip_ipaddr_t * source_addr, uint16_t source_port,
+		   const uip_ipaddr_t * dest_addr, uint16_t dest_port,
+		   const uint8_t * data, uint16_t datalen);
+
+
+/* This function is the "key store" for tinyDTLS. It is called to
+ * retrieve a key for the given identity within this particular
+ * session. */
+int
+get_psk_info(struct dtls_context_t *ctx, const session_t *session,
+	     dtls_credentials_type_t type,
+	     const unsigned char *id, size_t id_len,
+	     unsigned char *result, size_t result_length) {
+
+  struct keymap_t {
+    unsigned char *id; size_t id_length;
+    unsigned char *key; size_t key_length;
+  } psk[3] = {
+    { (unsigned char *)"Client_identity", 15,
+      (unsigned char *)"secretPSK", 9 },
+    { (unsigned char *)"default identity", 16,
+      (unsigned char *)"\x11\x22\x33", 3 },
+    { (unsigned char *)"\0", 2,
+      (unsigned char *)"", 1 }
+  };
+
+  if (type != DTLS_PSK_KEY) {
+    return 0;
+  }
+
+  if (id) {
+    int i;
+    for (i = 0; i < sizeof(psk)/sizeof(struct keymap_t); i++) {
+      if (id_len == psk[i].id_length && memcmp(id, psk[i].id, id_len) == 0) {
+	if (result_length < psk[i].key_length) {
+	  //dtls_warn("buffer too small for PSK");
[…]

### 2017-11-21 experiments/keydtls/project-conf.h

@@ -1,0 +1,21 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+#define UIP_CONF_TCP                   0
+
+//RDC driver
+#undef NETSTACK_CONF_RDC
+//#define NETSTACK_CONF_RDC nullrdc_driver
+#define NETSTACK_CONF_RDC contikimac_driver
+//#define NETSTACK_CONF_RDC sicslowmac_driver
+//#define NETSTACK_CONF_RDC cxmac_driver
+
+//MAC driver
+#if 0
+#undef NETSTACK_CONF_MAC
+#define NETSTACK_CONF_MAC nullmac_driver
+#endif
+
+//#define NETSTACK_CONF_RDC_CHANNEL_CHECK_RATE 8
+
+#endif

### 2017-11-21 experiments/llsecapps/aestest/project-conf.h

@@ -1,0 +1,52 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+
+#ifdef UIP_CONF_TCP
+#undef UIP_CONF_TCP
+#define UIP_CONF_TCP 0 //Disable TCP for space optimise.
+#endif //End of #ifdef UIP_CONF_TCP
+
+//RDC driver
+//#undef NETSTACK_CONF_RDC
+//#define NETSTACK_CONF_RDC nullrdc_driver
+//#define NETSTACK_CONF_RDC contikimac_driver
+
+//MAC driver
+//#undef NETSTACK_CONF_MAC
+//#define NETSTACK_CONF_MAC nullmac_driver
+
+//Channel check rate
+//#define NETSTACK_CONF_RDC_CHANNEL_CHECK_RATE 8
+
+//LLSEC configurations.
+#ifdef ENABLE_LLSEC
+
+#undef NETSTACK_CONF_LLSEC
+#define NETSTACK_CONF_LLSEC noncoresec_driver
+
+#undef LLSEC802154_CONF_SECURITY_LEVEL
+#define LLSEC802154_CONF_SECURITY_LEVEL 7
+
+#undef NONCORESEC_CONF_KEY
+#define NONCORESEC_CONF_KEY {\
+	0x00 , 0x01 , 0x02 , 0x03 ,\
+	0x04 , 0x05 , 0x06 , 0x07 ,\
+	0x08 , 0x09 , 0x0A , 0x0B ,\
+	0x0C , 0x0D , 0x0E , 0x0F \
+}
+
+//Disable Hardware AES-128 coprosessor. 
+#ifdef DISABLE_HW_AES
+#ifdef AES_128_CONF
+#undef AES_128_CONF
+#endif //End of #ifdef AES_128_CONF
+#endif
+
+#endif //End of #ifdef ENABLE_LLSEC
+
+#ifdef CONTIKI_TARGET_CC2538DK 
+#define PRIu32 "d" 
+#endif //End of #ifdef CONTIKI_TARGET_CC2538DK
+
+#endif //End of #ifdef __PROJECT_CONF_H__

### 2017-11-21 experiments/llsecapps/backup/aestest_fixed.c

@@ -1,0 +1,151 @@
+#include "contiki.h"
+#include "lib/aes-128.h"
+#include "sys/rtimer.h"
+#include "sys/etimer.h"
+#include "lib/random.h"
+
+#include <stdio.h>              /* For printf() */
+#include <string.h>
+
+#define AES_KEY_LEN 16
+#define AES_BLOCK_LEN 16
+
+#ifndef NROUND
+#define NROUND 200
+#endif
+
+#ifndef NSAMPLE
+#define NSAMPLE 100
+#endif
+
+static uint8_t Aes128Key[AES_KEY_LEN] = {
+    0x01, 0x23, 0x45, 0x67,
+    0x89, 0xab, 0xcd, 0xef,
+    0x12, 0x34, 0x56, 0x78,
+    0x9a, 0xbc, 0xde, 0xf0
+};
+
+static const uint8_t fixed_data[AES_BLOCK_LEN] = {
+    0xda, 0x39, 0xa3, 0xee,
+    0x54, 0x6b, 0x4b, 0x0d,
+    0x32, 0x55, 0xbf, 0xef,
+    0x95, 0x60, 0x18, 0x90
+};
+
+static uint8_t datablock[NROUND][AES_BLOCK_LEN] = { {0} };
+
+void PrintBlock(const char *prefix, const uint8_t * block,
+                const char *appendix)
+{
+    int i;
+
+    printf(prefix);
+    for (i = 0; i < AES_KEY_LEN; i++)
+        printf("%02x ", block[i]);
+    printf(appendix);
+
+    return;
+}
+
+void finalise()
+{
+    int i;
+#ifdef CONTIKI_TARGET_CC2538DK
+    static char garbage = 0;
+    uint8_t *gbg = datablock[0];
+#endif
+    
+    printf("#Finalise.\n");
+    
+    //Reset plaintext.
+    for (i = 0; i < NROUND; i++)
+    {
+        memcpy(datablock[i], fixed_data, AES_BLOCK_LEN);
+    }
+    
+#ifdef CONTIKI_TARGET_CC2538DK
+    //Do garbage operations to flush the cache.(?) For unknown reason this is needed for CC2538,  although it does not have cache. Doing the same on TelosB causes timing error.
+    for ( i = 0; i < NROUND * AES_BLOCK_LEN; i++)
+	garbage ^= *gbg++;
+	
+    if(garbage != 0)
+	return;
+#endif
+
+    return;
+}
+
[…]

### 2017-11-21 experiments/llsecapps/backup/aestest_random.c

@@ -1,0 +1,149 @@
+#include "contiki.h"
+#include "lib/aes-128.h"
+#include "sys/rtimer.h"
+#include "sys/etimer.h"
+#include "lib/random.h"
+
+#include <stdio.h>              /* For printf() */
+#include <string.h>
+
+#define AES_KEY_LEN 16
+#define AES_BLOCK_LEN 16
+
+#ifndef NROUND
+#define NROUND 200
+#endif
+
+#ifndef NSAMPLE
+#define NSAMPLE 100
+#endif
+
+static uint8_t Aes128Key[AES_KEY_LEN] = {
+    0x01, 0x23, 0x45, 0x67,
+    0x89, 0xab, 0xcd, 0xef,
+    0x12, 0x34, 0x56, 0x78,
+    0x9a, 0xbc, 0xde, 0xf0
+};
+
+static const uint8_t fixed_data[AES_BLOCK_LEN] = {
+    0xda, 0x39, 0xa3, 0xee,
+    0x54, 0x6b, 0x4b, 0x0d,
+    0x32, 0x55, 0xbf, 0xef,
+    0x95, 0x60, 0x18, 0x90
+};
+
+static uint8_t datablock[NROUND][AES_BLOCK_LEN] = { {0} };
+
+void PrintBlock(const char *prefix, const uint8_t * block,
+                const char *appendix)
+{
+    int i;
+
+    printf(prefix);
+    for (i = 0; i < AES_KEY_LEN; i++)
+        printf("%02x ", block[i]);
+    printf(appendix);
+
+    return;
+}
+
+void finalise()
+{
+    int i;
+#ifdef CONTIKI_TARGET_CC2538DK
+    static char garbage = 0;
+    uint8_t *gbg = datablock[0];
+#endif
+
+    printf("#Finalise.\n");
+    
+    //Randomise the key.
+    for (i = 0; i < AES_KEY_LEN; i++)
+        Aes128Key[i] ^= datablock[0][i];
+	
+#ifdef CONTIKI_TARGET_CC2538DK
+    //Do garbage operations to flush the cache.(?) For unknown reason this is needed for CC2538,  although it does not have cache. Doing this on TelosB causes timing error.
+    for ( i = 0; i < NROUND * AES_BLOCK_LEN; i++)
+	garbage ^= *gbg++;
+	
+    if(garbage != 0)
+	return;
+#endif
+	
+    return;
+}
+
[…]

### 2017-11-21 experiments/llsecapps/broadcast/broadcast-example.c

@@ -1,0 +1,103 @@
+/*
+ * Copyright (c) 2011, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "lib/random.h"
+#include "sys/ctimer.h"
+#include "sys/etimer.h"
+#include "net/ip/uip.h"
[…]

### 2017-11-21 experiments/llsecapps/powertrace/example-powertrace.c

@@ -1,0 +1,100 @@
+/*
+ * Copyright (c) 2007, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+/**
+ * \file
+ *         Demonstrating the powertrace application with broadcasts
+ * \author
+ *         Adam Dunkels <adam@sics.se>
+ */
+
+#include "contiki.h"
[…]

### 2017-11-21 experiments/llsecapps/unicast/unicast-receiver.c

@@ -1,0 +1,143 @@
+/*
+ * Copyright (c) 2011, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "lib/random.h"
+#include "sys/ctimer.h"
+#include "sys/etimer.h"
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
[…]

### 2017-11-21 experiments/llsecapps/unicast/unicast-sender.c

@@ -1,0 +1,142 @@
+/*
+ * Copyright (c) 2011, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "lib/random.h"
+#include "sys/ctimer.h"
+#include "sys/etimer.h"
+#include "net/ip/uip.h"
+#include "net/ipv6/uip-ds6.h"
+#include "net/ip/uip-debug.h"
+
[…]

### 2017-11-21 experiments/ping6/ping6.c

@@ -1,0 +1,136 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "contiki-lib.h"
[…]

### 2017-11-21 experiments/ping6/project-conf.h

@@ -1,0 +1,13 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+#define UIP_CONF_TCP                   0
+
+#ifdef NULL_DRIVER
+#define NETSTACK_CONF_RDC nullrdc_driver
+#define NETSTACK_CONF_MAC nullmac_driver
+#endif
+
+#define NETSTACK_CONF_RDC_CHANNEL_CHECK_RATE 8
+
+#endif

### 2017-11-21 experiments/plbroadcaster/broadcast-example.c

@@ -1,0 +1,113 @@
+/*
+ * Copyright (c) 2011, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "lib/random.h"
+#include "sys/ctimer.h"
+#include "sys/etimer.h"
+#include "net/ip/uip.h"
[…]

### 2017-11-21 experiments/relaxed-br/project-conf.h

@@ -1,0 +1,54 @@
+/*
+ * Copyright (c) 2010, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ */
+
+#ifndef PROJECT_ROUTER_CONF_H_
[…]

### 2017-11-21 experiments/rime/rime_ruc/rime-client.c

@@ -1,0 +1,99 @@
+/*
+ * Copyright (c) 2006, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+/**
+ * \file
+ *         A very simple Contiki application showing how Contiki programs look
+ * \author
+ *         Adam Dunkels <adam@sics.se>
+ */
+
+#include "contiki.h"
+
[…]

### 2017-11-21 experiments/rime/rime_ruc/rime-server.c

@@ -1,0 +1,96 @@
+/*
+ * Copyright (c) 2006, Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+/**
+ * \file
+ *         A very simple Contiki application showing how Contiki programs look
+ * \author
+ *         Adam Dunkels <adam@sics.se>
+ */
+
+#include "contiki.h"
+
+#include "sys/etimer.h"
[…]

### 2017-11-21 experiments/sensordtls/dtls-server.c

@@ -1,0 +1,338 @@
+/*
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the Institute nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE INSTITUTE AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE INSTITUTE OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ *
+ * This file is part of the Contiki operating system.
+ *
+ */
+
+#include "contiki.h"
+#include "contiki-lib.h"
+#include "contiki-net.h"
[…]

### 2017-11-21 experiments/sensordtls/project-conf.h

@@ -1,0 +1,44 @@
+#ifndef __PROJECT_CONF_H__
+#define __PROJECT_CONF_H__
+
+#ifdef UIP_CONF_TCP
+#undef UIP_CONF_TCP
+#define UIP_CONF_TCP                   0
+#endif
+
+//Disable Watchdog for ECC timeout
+#define WATCHDOG_CONF_ENABLE 0
+
+
+#ifndef QUEUEBUF_CONF_NUM
+#define QUEUEBUF_CONF_NUM          64
+#endif
+
+#ifndef UIP_CONF_BUFFER_SIZE
+#define UIP_CONF_BUFFER_SIZE    256
+#endif
+
+#ifndef UIP_CONF_RECEIVE_WINDOW
+#define UIP_CONF_RECEIVE_WINDOW  120
+#endif
+
+//RDC driver
+//#undef NETSTACK_CONF_RDC
+//#define NETSTACK_CONF_RDC nullrdc_driver
+//#define NETSTACK_CONF_RDC contikimac_driver
+//#define NETSTACK_CONF_RDC sicslowmac_driver
+//#define NETSTACK_CONF_RDC cxmac_driver
+
+//MAC driver
+#if 0
+#undef NETSTACK_CONF_MAC
+#define NETSTACK_CONF_MAC nullmac_driver
+#endif
+
+//#define NETSTACK_CONF_RDC_CHANNEL_CHECK_RATE 8
+
+//#define SERVER_RPL_DAG
+//
+
+
+#endif

### 2017-11-21 Writing/conclusion.tex

--- 2017-04-07 Writing/submission.tex
@@
-\documentclass{article}
-%\documentclass{river-journal}
-%\usepackage{rivps}
-%\usepackage[mtbold]{mathtime}
-
-\usepackage{graphicx}
-\usepackage{graphics}
-%\usepackage{subfigure}
-\usepackage{cite}
-\usepackage{url}
-\usepackage{subcaption}
-\usepackage{multirow}
-
-\input{packages}
-
-% for alternatives, see appendix of manual
-
-%\newtheorem{guess}{Conjecture}
-
-% bibliographies
-\bibliographystyle{plain}
-% also tested with natbib
-
-\title{Exploring Potential 6LoWPAN Traffic Side Channels}
-\author{Yan Yan \and Elisabeth Oswald \and Theo Tryfonas}
-
-\begin{document}
-\maketitle
-%\begin{opening}
-%\institute{University of Bristol,  \texttt{y.yan@bristol.ac.uk}}
-%\end{opening}
-
-%\runningtitle{Exploring Potential 6LoWPAN Traffic Side Channels}
-%\runningauthor{Y. Yan}
-
-\subsection*{Abstract}
-The Internet of Things has become a reality: small connected devices feature in everyday objects
-including childrens' toys, TVs, fridges, heating control units, etc. Supply chains feature sensors
-throughout, and significant investments go into researching next-generation healthcare, 
-where sensors monitor wellbeing.
-A future in which sensors and other (small) devices interact to create sophisticated applications seems just around the corner .
-All of these applications have a fundamental need for security and privacy and thus we need to deploy cryptography as part an attempt to secure them.
-In this paper we explore a particular type of flaw, namely side channel information, on the protocol level.
-Our research investigates the potential for utilising packet length and timing information (both are easily obtained) to extract interesting information from a system, despite the use of cryptography.
-
-%\keywords{6LoWPAN, Side Channels, Traffic Analysis}
-
-\section{Introduction}
-The expression `Internet of Things' (IoT) can refer to a multitude of objects and protocols, which share that they have been purposefully designed for resource constraint environments.
-Whereas the typical TCP/IP network stack produces considerable overhead to achieve quality of service for applications that are based on it, the nature of many IoT `things' is such that a full implementation of it would not be practical.
-Often `things' are sensor, which are devices that have to function on little resources (most importantly power).
-Thus a whole host of new networking protocols have been developed over the years to cater for such resource constrained devices: 6LoWPAN is the `tiny' version of IPv6, UDP tends to be used instead of TCP/IP, DTLS can be used for end-to-end security or one can directly invoke 802.15.4 Security which is part of 6LoWPAN, and finally CoAP(s) is the replacement for HTTP(s).
-Thus there are two options (802.15.4, and DTLS) to secure communications between the `things' and a server/gateway.
-
-Implementing cryptography correctly and securely has proven to be a massive challenge as evidenced by the multitude of implementation attacks over the years.
-Triggered off by research that showed how to utilise additional information via timing and power side channels\cite{DPA}, many different flavours of side channel attacks were discovered over the last decade.
-Many attacks use phyiscal information (such as low level execution timings or power consumption) to recover secret keys, but many other attacks use protocol level information (such as packet lengths, types of packets or protocol messages) to recover information about plaintexts, devices in the network, or the network itself.
-There exists a considerable body of work in the context of conventional, i.e.
-HTTPs over TCP/IP network, but the applicability of (some) of these attacks in the context of a typical IoT protocol stack is lacking.
-This is the gap that we would like to address within this submission.
-
-This paper is structured as follows: after reviewing some relevant attack paths for HTTPs over TCP/IP in the following subsection, we provide a brief introduction to the necessary protocol and network features in \Cref{sec: IotProtocols}.
-We discuss the impact of packet length leakage in \Cref{sec: PacketLen}, followed by an analysis of the response time leakage in \Cref{sec: ResponseTime}.
-We summarise our work in \Cref{sec: Conclusion}.
-
-\subsection{Related Work\label{subsec: RelatedWork}}
-%Write about attacks that exploit packet length and response times in the context of TCP/IP.
-Reflect on web applications and how the same might happen if more interesting applications might be deployed that involve IoT objects.
-
-%Literatures about Traffic Analysis...
-Traffic Analysis is well studied in the context of encrypted Internet traffic, especially for web applications based on HTTPs and TCP/IP.
-The landmark study by Chen et al.
-\cite{WebSidechannel} discussed different side channel attacks against web applications and \cite{SuggestBox} studied the practicability of an attack specifically targeted Google and Bing search boxes.
-Later work by Mather and Oswald \cite{PinpointWeb} proposed the use of Mutual Information to pinpoint the potential leakage points in web traffic.
-For non-HTTPs applications, the papers \cite{AppleMsg}, \cite{Language} and \cite{VideoTraffic} described attacks against encrypted text, voice and video traffic respectively.
-Machine learning is widely used to analyse the traffic, and behaviours of different classifiers are studied by \cite{HClassifier} and \cite{Peekaboo}.
-Based on all these published works we can conclude that two features, the packet length and response time, are the most exploited ones among all attacks.
-Different countermeasures were studied by \cite{TrafficMorphing}, \cite{HTTPOS} and \cite{FTE}.
-
-Reflecting on IoT applications, we stipulate that most of these attacks may still be applicable, as we intend to demonstrate in this paper.
-Considering the future vision that IoT devices could be indeed connected to the Internet with even more sensitive data flowing over different networks, the task of designing secure IoT applications becomes increasingly challenging.
-
-%Literatures about 6LoWPAN security
-With regard to the aspect of protocol design, the recent paper \cite{6LoWPANAtk} summarised some known flaws of 6LoWPAN, including its susceptibility to the Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}.
-In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.
-However we do not discuss further about these designing flaws as they lay into a different aspect of the security issues addressed by this paper.
-
-%\textbf{TODO: if space and time say some more about these attacks.
-At least say if they relate to the type of leakage we are exploiting or if they are completely independent (which is what I would guess).
-}
-
-\input{iotprotocols}
-%\section{A Typical IoT Protocol Stack}
-%A typical sensor network is built as described in \ref{Protocols}.
-
-%\begin{table}[!h]
-%	\centering
-%	\input{tbl/protocols.tex}
-%	\caption{Protocol stack for sensor networks. (* are optional.)\label{Protocols}}
-%\end{table}
-
-%\begin{itemize}
-%	\item Security options in 6LoWPAN: 802.15.4 Security and DTLS.
-%	\item Eavesdropping is easier for 6LoWPAN.
-%\end{itemize}
-
-%\subsection{Our experimental network}
-%Say something about devices, and choice of OS, etc.
-
-\section{Exploiting Packet Length Information\label{sec: PacketLen}}
-
-As our brief survey of traffic analysis via exploiting packet lengths showed in \Cref{subsec: RelatedWork}, the packet length has proven to be a powerful side channel for the classical Internet protocols.
-It is worth noting that this side channel is `noisy' in the classical Internet setting: websites or web applications in this setting typically feature advertisements, which impact on packet lengths; TCP/IP allows to fragment packets and then reassembles them, a feature which is not presented in UDP.
-Thus, due to the nature of UDP exploiting the packet length as side channel should be easier in the IoT setting.
-
-Clearly then, any web application style implementations involving an IoT device will thus be extremely vulnerable to attacks such as \cite{WebSidechannel}.
-In the absence of this scenario for state-of-the art IoT applications, it still sends a cautionary warning to developers: binary responses (e.g.
-`yes' vs.
-`no', or `on' vs.
-`off') must always be coded via a binary variable and not via strings because these will have different lengths, which are directly visible via the packet length.
-
-In the remainder of this section we will highlight further problems that arise if packet lengths leak information.
-
-\subsection{Distinguishing ICMP Messages}
-The Internet Control Message Protocol(ICMP)\cite{rfc4443} performs the management tasks in a network, such as link establishment and routing information exchange.
-As explained before we utilise the open source system Contiki, which supports a (sub)set of the ICMP standard (we list the supported ICMP messages in the following).
-Many ICMP messages are ideal for network discovery and exploration, although the purpose of ICMP is to send error messages to the source IP address if standard IP packets fail to be transmitted correctly.
-
-\begin{itemize}
-	\item \textbf{DAG Information Object (DIO)} \\
-	DIO contains the 6LoWPAN global information. It could be periodically broadcasted for network maintenance, or unicasted to a new joining node as a reply to DIS (see below).
-	\item \textbf{DAG Information Solicitation (DIS)} \\
-	DIS is sent by a newly started node to probe any existing 6LoWPANs. A DIO would be replied if the DIS is received by any neighbour nodes.
-	\item \textbf{Destination Advertisement Object (DAO)} \\
-	DAO is sent by a child node to its precedents (The 6LoWPAN DODAG topology is defined in \cite{rfc6550}) to propagate its routing information.
-	\item \textbf{Neighbour Solicitation (NS) and Neighbour Advertisement (NA)} \\
-	NS and NA are the ARP replacement in IPv6, where NS queries a translation and NA answers one. In addition, they are also used for local link validity check.
-	\item \textbf{Echo Request and Echo Response (PING)} \\
-	Echo Request and Echo Response are well known as the PING packets.
-They are mostly used for diagnostic purposes, such as connectivity test or Round Trip Time (RTT) estimation.
-Echo Request may contain arbitrary user defined data and Echo Response simply echoes its corresponding request.
-\end{itemize}
-
-Generally, ICMP messages can be protected by either using the secure ICMP messages as described in \cite{rfc4443}, or relying on the lower layer encryption provided by 802.15.4.
-Contiki OS does not have the former implemented, hence 802.15.4 security is the only option currently.
-We simulated a 6LoWPAN network with 802.15.4 security enabled (with strongest encryption and authentication).
-We configured the nodes to also generate random UDP packets.
-Despite the fact that all ICMP messages were encrypted, our experiments show that several ICMP messages can be identified by their packet size and MAC destination.
-\Cref{IcmpPacketFeature} summarises the packet features.
-The value $x$ denotes the size of user defined data in bytes.
-
-\begin{table}
-	\center
-	\input{tbl/icmpmeta.tex}
-	\caption{6LoWPAN Packet Features\label{IcmpPacketFeature}}
-\end{table}
-
-%First of all, a DIS has the unique smallest packet size of 85 bytes, indicating it can be easily identified.
-
-Among the unicast packets, PING and UDP have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}.
-Therefore, DAO can be uniquely identified as the shortest unicast packet of $97$ bytes.
-For the same reason NA and unicast NS can also be distinguished from other packets by filtering packets of $87$ bytes.
-Considering that NA is sent as a response to NS according to the protocol, one can always identify the first being NS and second being NA.
-
-Similarly, unicast DIO can be identified as the 123 bytes packet followed by DIS, where the later has a unique 85 byte size.
-However, there is a potential of false positive induced by carefully crafted PING or UDP packets.
-PING could be recognised by its pair-wised appearance, as the response would have nearly the same meta data as the original request, except the exchanged source and destination.
-For broadcast packets, DIS can be easily identified by its unique 85 bytes packet size.
-Others like broadcast NS can be identified by the followed characteristic NA response; and packets of 118 bytes those are periodically broadcasted are likely to be DIOs.
-
-In summary, among all the packets, DAO, NA, NS, DIS can be identified with certainty.
-DIO and PING cannot be certainly identified by they both have significant characters.
-Notice that the above contained all ICMPv6 messages supported by Contiki; therefore UDP packets can be reversely filtered, although in some cases the get mixed with DIO and PING.
-
-Although leakage in ICMP messages does not directly lead to any breach of application data, it would still be harmful by providing the adversary with information about the state of the network, including which nodes recently joined etc.
-Specifically DAO is always sent from a child to its parent and can be uniquely identified; therefore together with MAC addresses the adversary may exploit it to draw a graph that shows the parental relations in the network.
-
-%\textbf{
-%TODO: why would you get the network topology (do you mean via observing the different MAC addresses alongside what they send out)?
-AFter all the payload is still encrypted and so you don't see the actual DAO for instance??
-%}
-\subsection{Distinguishing Different Devices}
-%Gain hardware information.
-%\begin{itemize}
-%	\item Some devices can handle longer packets, some can't.
-%	\item Works on both 802.15.4 Security and DTLS.
-%\end{itemize}
-
-In the classical Internet world, ICMP has been well known for its use for OS fingerprinting\cite{OsFingerprint}.
-In the case of the IoT, this could be possible as well (as different OS support different subsets of ICMP), however an additional attack vector exists.
-This is because different IoT devices have different hardware limitations or drivers.
-We noticed that our TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.} whereas our CC2538 handles packets even up to 160 bytes.
-Therefore an adversary can immediately rule out TelosB whenever a packet larger than 127 bytes processed by the target.
-
-\section{Exploiting Response Time Information\label{sec: ResponseTime}}
-
-The response time is another major feature that has been previously exploited in Internet traffic analysis attacks.
-Like in the case of exploiting packet lengths, we would expect that the same attacks (as in the classical Internet setting) can be applied to 6LoWPAN traffic.
-Indeed, like in the previous section, we would expect that they will work even better because the accuracy of timing measurements can be greatly improved for 6LoWPAN traffic: this is because there are fewer noise sources in the traffic, the devices are physically close to each other and uses RF to communicate, the adversary can remove the RTT noises by measure the packets on the server side, and the performance of the constrained devices is low and hence gives a better resolution of the execution time.
-
-\subsection{Distinguishing Different Sensors}
-The first application of timing analysis that we describe is to distinguish between different sensors that are accessed on a device.
-For this purpose we set up an experiment on a CC2538, which has three on-board sensors: Vdd, temperature, and an Ambient Light Sensor (short ALS).
-We access these via CoAP\cite{rfc7252}, which is a protocol designed for constrained devices that provides an universal interface for accessing resources.
-CoAPs is the secure version which stands for CoAP with DTLS.
-
-Due to the different physical characteristics of the sensors, there could be a variance of time that is required for reading the measurements.
-We investigated whether such variances could be observed through the packet response latency.
-If this was the case, then an adversary could learn the nature/purpose of sensors on a network by observing their response time.
-
-We implemented thus set up an experiment on CC2538, using all three sensors from ``cc2538-demo".
-We used CoAP from the ``er-rest-example" in the Contiki OS source code, as there is no CoAPs implementation available.
-Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result will hold equally for CoAPs.
-We carefully controlled other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.
-
-\begin{table}
-	\center
-	\input{tbl/coapsensors.tex}
-	\caption{CoAP Response Latency for Sensor Readings on CC2538\label{CoapTiming}}
-\end{table}
-
-\Cref{CoapTiming} summarises the result.
-It shows that ALS takes about $2$ms longer and hence can be easily distinguished.
-Vdd and temperature have much more strongly overlapping distributions, and thus are more difficult to distinguish.
-Nevertheless these results show that our hypothesis holds: different sensors have different latencies and these leak through the response time.
-An adversary who is interested in finding out information about devices on a network might thus be able to match the (known) behaviour of `interesting' sensors to what they observe on the network.
-We remark that this could be useful even in the setting where the sensors transmit their data unencrypted: after all they might return only some reading without a unit of measurement; thus seeing their return data might not as such reveal their nature.
-
-\subsection{Distinguishing Different Devices}
-%Gain hardware information.
-%\begin{itemize}
-%	\item Different hardware has different response latency against the same message.
-%	\item For 802.15.4: Requires additional information. Can be satisfied by the previous ICMP attack.
-%	\item For DTLS: No requirement. The adversary can actively send a message, e.g. PING.
-%\end{itemize}
-
-As we observed before, different devices have different underlying hardware and thus different computational power.
-This implies that there could be the potential that different devices take different amounts of time to process the same message.
-Because ICMP messages are standardised, they are particularly suitable for this purpose.
-Among the different ICMP messages, PING is especially ideal for two reasons:
-\begin{enumerate}
-	\item It is mandatory in the ICMP standard.
-	\item It only swaps the source and destination address of the packet; thus minimises different code path in protocol processing.
-\end{enumerate}
-
-\begin{table}
-	\center
-	\input{tbl/pingresponse}
-	\caption{PING Response Latency\label{PingResponse}}
-\end{table}
-
-\Cref{PingResponse} shows the PING response latency on CC2538 and TelosB. The result confirms that these devices can be distinguished by PING response latency.
-
-\subsection{Distinguishing Programs}
-%Fingerprints the code running on a device, which leads to plaintext recovery.
-%\begin{itemize}
-%	\item Theory explained in \Cref{FingerprintTheory}.
-%	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
-%	\item Not for 802.15.4: adversary can't join the network.
-%	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
-%\end{itemize}
-
-We remarked before that the functionality of a sensor is potentially valuable information.
-For instance some sensors might be predominantly passive, e.g.
-they might read the temperature and report it back periodically, whereas some sensors might control something upon receiving commands.
-Thus knowing the functionality enables an adversary to make (more) sense of the observed traffic in the network.
-This could be done if a `fingerprint' could be produced for different programs.
-From an adversaries perspective a positive result would imply that they could `fingerprint' products which are on the market and thus use this information to infer what program is running on a target device.
-
-% program executing on the target is a valuable information in aspect of security and privacy, as it determines functionality of a device and therefore the contents of encrypted packets associated.
-For instance, knowing a target being an actuator that controls an air conditioner immediately suggests a packet directed to it might  be a controlling command.
-
-%Our study shows that the response time of packets could also be exploited to reveal information of the program target is executing.
-To be more specifically, an adversary can collect ``fingerprints'', which we explain in the following section, from products available on the market and then use this information to breach the program running on a target device.
-
-%How it works
-To illustrate why this might work, we now look at \Cref{FingerprintTheory}.
-It illustrates two sensors receiving the same service request.
-In our example, at the time of receiving the request, Sensor Node 1 was idle and hence responded immediately, whilst Sensor Node 2 postponed the request for reading a sensor.
-Clearly, the response time on Sensor Node 2 would appear longer than that of Sensor Node 1.
-
-\begin{figure}
-	\center
-	\includegraphics[width=\textwidth]{fig/PingProbe_Theory.png}
-	\caption{Variations in Response Time\label{FingerprintTheory}}
-\end{figure}
-
-In real life, most sensors are programmed in a loop; therefore the same code fragments are repeated through the life time of a sensor.
-Each code fragment takes different time to execute and hence the response times vary.
-This behaviour could be statistically analysed and the resulting distribution could be stored as a `fingerprint' .
-
-For this fingerprinting scenario, we must assume the adversary has the pre-knowledge of potential programs and can fingerprint them (or that they have access to a database that contains this information).
-To identify an unknown program running on target sensor, the adversary collects a new fingerprint and then matches it to available fingerprints.
-Clearly, to effectively launch the attack, the adversary needs to be able to send the request to a targeted sensor (requests with short predictable processing time are preferable as they induce less noise).
-
-In practice, the request can be instantiated by several messages defined in the sensor network protocols.
-PING is exceptionally ideal as it is mandatory in the ICMP standard\cite{rfc4433} and has only negligible computation.
-Other options but not excluded are Heartbeat in DTLS\cite{rfc6520}, Reset in CoAP\cite{rfc7252}, etc.
-
-\subsubsection{Extracting Fingerprints}
-We explored the feasibility of fingerprinting programs on an CC2538 running Contiki OS by using the PING command.
-
-\Cref{ExamplePri} shows an example of captured packets.
-Contiki MAC\cite{ContikiMAC} sends duplicated PING requests.
-The response time, which refers to PING Response Interval, PRI, is defined to be the time between a PING response and its last paired request.
-The highlighted Packets 205 and 203 shows such an example.
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{fig/PRI_hl.png}
-	\caption{Example PRI\label{ExamplePri}}
-\end{figure}
-
-%Since the attack extracts the information contained in the extended response time of a specific request, the first problem is to see whether such extended response time can be filtered from normal ones.
-
-\Cref{HelloworldPriNormal} shows the histogram of PRIs collected on the ``helloworld'' example from Contiki OS.
-Values $\geq$12ms are collected at 12ms.
-The result shows that most PRIs are clustered around 9.5ms which consists with our result in \Cref{PingResponse}.
-The majority, roughly ranged [9.0, 10.3]ms, corresponds to the usual response time as depicted by Sensor Node 1 in \Cref{FingerprintTheory}.
-
-\begin{figure}[!h]
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\includegraphics[width=\textwidth]{fig/helloworld_cc2538.png}
-		\caption{PRIs of helloworld\label{HelloworldPriNormal}}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\includegraphics[width=\textwidth]{fig/helloworld_cc2538_outlier.png}
-		\caption{PRIs outliers of helloworld\label{HelloworldPriOutliers}}
-	\end{subfigure}
-	\caption{helloworld PRIs\label{HelloworldPri}}
-\end{figure}
-
-We further plotted the upper outliers, mostly ranged [12, 2000]ms, in \Cref{HelloworldPriOutliers}.
-We suppose these outliers correspond to the extended response time as depicted by Sensor Node 2 in \Cref{FingerprintTheory}.
-The distribution described by \Cref{HelloworldPriOutliers} is the fingerprint of the ``helloworld'' example.
-
-The result in \Cref{HelloworldPri} shows a clear gap between the usual PRIs and extended PRIs.
-In fact other applications we experimented also showed the same property.
-This implies that an adversary can easily draw a threshold by observing the whole PRI distribution and then filter out the fingerprint.
-In our experiments the threshold is set to 12ms but any other values within the gap would also work.
-
-We collected the fingerprints for three programs taken from the Contiki OS examples:
-\begin{description}
-	\item[broadcast] This program periodically broadcasts a constant message.
-
-	\item[powertrace] This program records the power consumption and broadcasts a constant message.
-
-	\item[Sensorpayload] This program is based on the ``er-rest-example'' embedded together with sensor accesses taken from ``cc2538-demo''.
-It captures a real case scenario where three different sensors, namely Temperature, VDD and ALS, are being accessed through CoAP.
-\end{description}
-
-Specifically for ``Sensorpayload'' we collected fingerprints for 8 different scenarios where different sensors are being accessed.
-For each program we independently collected 2 fingerprints for comparison.
-
-\Cref{FingerprintApps} summarises the total 20 fingerprints we collected for the experiment.
-
-\subsubsection{Fingerprint Matching}
-%Comparing the distribution.
-
-During the experiments we realised that most of the fingerprints do not adhere to common distributions; therefore we used non parametric test, the Kolmogorov-Smirnov Distance\cite{KsTest}, as our test statistic.
-\Cref{ksdistances} summarises the relative KS distances computed on each pair of fingerprints in our experiments.
-
-Although fingerprints collected on the same application were rejected by the Kolmogorov-Smirnov Test, we noticed that their KS distance tends to be smaller comparing to fingerprints collected on different programs, as the \textbf{bold} cells marked in \Cref{ksdistances}.
-
-By adapting our distinguisher to utilise the minimum KS distance, we were able to identify 13 out of 20 fingerprints successfully.
-The `overlapping' fingerprints are mainly due to the ``Sensorpayload'' program, which access different sensors, but otherwise has identical program code.
-Thus we did expect that the different instantiations of it would lead to very similar fingerprints.
-
 \section{Conclusion\label{sec: Conclusion}}
@@
 However, the threshold must be carefully chosen to preserve the functionality of the 6LoWPAN application.
-
-\appendix
-\input{appendix}
-%And this is my Appendix.
-
-%\subsection*{Appendix Subsection}
-
-%Some text.
-
-%\nocite{*} % add all entries from sample.bib
-
-\bibliography{references,rfc}
-%\begin{thebibliography}{10}
-
-%\end{thebibliography}
-
-%\section*{Biography}
-%
-%\fbox{\parbox[t]{3cm}{Here is space for \\
-%a photograph of \\
-%the author. \\
-%\vspace*{2cm}
-%}}
-%
-%\medskip
-%\noindent
-%{\bf Author's name}. A short vitae can be included here.
-
-\end{document}

### 2017-11-21 Writing/pktlen.tex
Update

--- 2017-03-31 Writing/pktlen.tex
@@
-\section{Packet Length}
-\textit{
-\begin{itemize}
-	\item TLS Attacks still works and even better against DTLS due to protocol feature.
-\end{itemize}
-}
+\section{Exploiting Packet Length Information\label{sec: PacketLen}}
 
-\subsection{ICMP Leakage}
-%Plaintext recovery.
-%\begin{itemize}
-%	\item The attack combines packet length with MAC address information.
-%	\item Works on 802.15.4 Security. No need for DTLS (ICMP is plaintext when DTLS.)
-%\end{itemize}
+As our brief survey of traffic analysis via exploiting packet lengths showed in \Cref{subsec: RelatedWork}, the packet length has proven to be a powerful side channel for the classical Internet protocols.
+It is worth noting that this side channel is `noisy' in the classical Internet setting: websites or web applications in this setting typically feature advertisements, which impact on packet lengths; TCP/IP allows to fragment packets and then reassembles them, a feature which is not presented in UDP.
+Thus, due to the nature of UDP exploiting the packet length as side channel should be easier in the IoT setting.
 
-Internet Control Message Protocol(ICMP)\cite{rfc4443} performs the management tasks in the network, such as link establishment and routing information exchange.
-Contiki OS supports the following ICMP messages:
+Clearly then, any web application style implementations involving an IoT device will thus be extremely vulnerable to attacks such as \cite{WebSidechannel}.
+In the absence of this scenario for state-of-the art IoT applications, it still sends a cautionary warning to developers: binary responses (e.g.
+`yes' vs.
+`no', or `on' vs.
+`off') must always be coded via a binary variable and not via strings because these will have different lengths, which are directly visible via the packet length.
+
+In the remainder of this section we will highlight further problems that arise if packet lengths leak information.
+
+\subsection{Distinguishing ICMP Messages}
+The Internet Control Message Protocol(ICMP)\cite{rfc4443} performs the management tasks in a network, such as link establishment and routing information exchange.
+As explained before we utilise the open source system Contiki, which supports a (sub)set of the ICMP standard (we list the supported ICMP messages further below).
+Many ICMP messages are ideal for network discovery and exploration, although the purpose of ICMP is to send error messages to the source IP address if standard IP packets fail to be transmitted correctly.
 
@@
 	\item \textbf{Destination Advertisement Object (DAO)} \\
-	DAO is sent by a child node to its precedents\footnote{The 6LoWPAN DODAG topology is defined in \cite{rfc6550}.} to propagate its routing information.
+	DAO is sent by a child node to its precedents (The 6LoWPAN DODAG topology is defined in \cite{rfc6550}) to propagate its routing information.
 	\item \textbf{Neighbour Solicitation (NS) and Neighbour Advertisement (NA)} \\
@@
 
-Generally, ICMP messages can be protected by either using the secure ICMP messages, or relying on lower layer encryption.
-Since Contiki OS does not have the former implemented, 802.15.4 Security became the only option currently.
-
-Although leakage in ICMP messages does not directly lead to any breach of application data, it would still be harmful by providing the adversary with information including network topology.
-These informations could then be exploited to, say, identify critical targets of DoS attacks.
-
-We simulated a 6LoWPAN network with 802.15.4 Security enabled\footnote{Security level is set to the highest 0x07.}. The nodes are configured to also generate random UDP packets.
-
-Despite the ICMP messages are encrypted by 802.15.4 Security, our experiment shows that several ICMP messages can still be identified by the packet size and MAC destination.
-
-\Cref{IcmpPacketFeature} summarises the packet features. $x$ to denotes the size of user defined data in bytes.
+Generally, ICMP messages can be protected by either using the secure ICMP messages as described in \cite{rfc4443}, or relying on the lower layer encryption provided by 802.15.4.
+Contiki OS does not have the former implemented, hence 802.15.4 security is the only option currently.
+We simulated a 6LoWPAN network with 802.15.4 security enabled (with strongest encryption and authentication).
+We configured the nodes to also generate random UDP packets.
+Despite the fact that all ICMP messages were encrypted, our experiments show that several ICMP messages can be identified by their packet size and MAC destination.
+\Cref{IcmpPacketFeature} summarises the packet features.
+The value $x$ denotes the size of user defined data in bytes.
 
@@
 
-Among the unicast packets, since PING and UDP have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}, DAO can therefore uniquely identified as unicast packets of $97$ bytes.
+Among the unicast packets, PING and UDP have at least 101 and 108 bytes\footnote{PING can be sent without user defined data and UDP packets requires at least 1 byte.}.
+Therefore, DAO can be uniquely identified as the shorter unicast packet of $97$ bytes.
+For the same reason NA and unicast NS can also be distinguished from other packets by filtering packets of $87$ bytes.
+Considering that NA is sent as a response to NS according to the protocol, one can always identify the first being NS and second being NA.
 
-For the same reason NA and unicast NS can also be distinguished from other packets by filtering packets of $87$ bytes.
-Considering NA is sent as a response to NS according to the protocol, one can always identify the first being NS and second NA.
-
-Similarly, unicast DIO can be identified as the 123 bytes packet followed by DIS, where the later has a unique 85 bytes size.
-However, there is a potential of false positive induced by carefully crafted PING or UDP packets.
-
+Similarly, unicast DIO can be identified as the 123 bytes packet followed by DIS, where the later has a unique 85 byte size.
+However, there is a potential of false positive induced by PING or UDP packets with user defined data crafted to have the same packet length\footnote{22 bytes for PING and 16 bytes for UDP.}.
 PING could be recognised by its pair-wised appearance, as the response would have nearly the same meta data as the original request, except the exchanged source and destination.
-
 For broadcast packets, DIS can be easily identified by its unique 85 bytes packet size.
@@
 
-In summary, among all the packets, DAO, NA, NS, DIS can be identified with certain.
-DIO and PING cannot be certainly identified by they both have significant characters.
-Notice that the above contained all ICMPv6 messages supported; therefore UDP packets can be reversely filtered, although in some cases mixed with DIO and PING.
+In summary, among all the packets, DAO, NA, NS, DIS can be identified with certainty.
+DIO and PING cannot be certainly identified but they both have significant characters.
+Notice that the above contained all ICMPv6 messages supported by Contiki; therefore UDP packets can be reversely filtered, although in some cases they get mixed with DIO and PING.
 
-\subsection{Hardware Leakage}
+Although leakage in ICMP messages does not directly lead to any breach of application data, it would still be harmful by providing the adversary with information about the state of the network, including which nodes recently joined etc.
+Specifically DAO is always sent from a child to its parent and can be uniquely identified; therefore together with MAC addresses the adversary may exploit it to draw a graph that shows the parental relations in the network.
+In addition, these information can also be exploited by attacks as in \cite{WsnIcmp}.
+
+%\textbf{
+%TODO: why would you get the network topology (do you mean via observing the different MAC addresses alongside what they send out)?
+AFter all the payload is still encrypted and so you don't see the actual DAO for instance??
+%}
+\subsection{Distinguishing Different Devices}
 %Gain hardware information.
@@
 %\end{itemize}
-Sometimes the packet length could also leak hardware information, mostly due to hardware limitations or different drivers.
-For instance, TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.} whereas CC2538 handles packets even up to 160 bytes.
+
+In the classical Internet world, ICMP has been well known for its use for OS fingerprinting\cite{OsFingerprint}.
+In the case of the IoT, this could be possible as well (as different OS support different subsets of ICMP), however an additional attack vector exists.
+This is because different IoT devices have different hardware limitations or drivers.
+We noticed that our TelosB\cite{TelosB} discards all packets exceeding 127 bytes\footnote{MTU specified by 802.15.4 standard.} whereas our CC2538 handles packets even up to 160 bytes.
 Therefore an adversary can immediately rule out TelosB whenever a packet larger than 127 bytes processed by the target.

### 2017-11-21 Writing/riversubmission.tex

--- 2017-04-07 Writing/submission.tex
@@
-\documentclass{article}
-%\documentclass{river-journal}
-%\usepackage{rivps}
-%\usepackage[mtbold]{mathtime}
+\documentclass{river-journal}
+\usepackage{rivps}
+%\usepackage[mtbold]{mathtime} %Unable to find a compilable one...
 
@@
 \usepackage{graphics}
-%\usepackage{subfigure}
+\usepackage{subfigure}
 \usepackage{cite}
-\usepackage{url}
-\usepackage{subcaption}
-\usepackage{multirow}
 
+%\usepackage{url}
+%\usepackage{subcaption}
+%\usepackage{multirow}
 \input{packages}
@@
 
-%\newtheorem{guess}{Conjecture}
+\newtheorem{guess}{Conjecture}
 
@@
 
-\title{Exploring Potential 6LoWPAN Traffic Side Channels}
-\author{Yan Yan \and Elisabeth Oswald \and Theo Tryfonas}
+\raggedbottom
+\sloppy\par
+
+%\title{Exploring Potential 6LoWPAN Traffic Side Channels}
+%\author{Yan Yan \and Elisabeth Oswald \and Theo Tryfonas}
 
 \begin{document}
-\maketitle
-%\begin{opening}
-%\institute{University of Bristol,  \texttt{y.yan@bristol.ac.uk}}
-%\end{opening}
+\begin{opening}
+	\title{Exploring Potential 6LoWPAN Traffic Side Channels}
+	\author{Yan Yan, Elisabeth Oswald, Theo Tryfonas}
+	\institute{University of Bristol,  \texttt{\{y.yan elisabeth.oswald theo.tryfonas\}@bristol.ac.uk}}
+\end{opening}
 
-%\runningtitle{Exploring Potential 6LoWPAN Traffic Side Channels}
-%\runningauthor{Y. Yan}
+\runningtitle{Exploring Potential 6LoWPAN Traffic Side Channels}
+\runningauthor{Y. Yan, E. Oswald, T. Tryfonas}
 
@@
 
-%\keywords{6LoWPAN, Side Channels, Traffic Analysis}
+\keywords{6LoWPAN, Side Channels, Traffic Analysis}
 
@@
 
-\subsection{Our experimental network}
+\subsection{Our Experimental Network}
 %Say something about devices, and choice of OS, etc.
@@
 
-\begin{table}[!h]
+\begin{table}
 	\centering
+	\caption{Protocol stack for our experiments(* is optinal)\label{Protocols}}
 	\begin{tabular}{|c|c|}
@@
 	\end{tabular}
-
-	\caption{Protocol stack for our experiments(* is optinal)\label{Protocols}}
 \end{table}
@@
 	\center
+	\caption{6LoWPAN Packet Features\label{IcmpPacketFeature}}
 	\input{tbl/icmpmeta.tex}
-	\caption{6LoWPAN Packet Features\label{IcmpPacketFeature}}
 \end{table}
@@
 	\center
+	\caption{CoAP Response Latency for Sensor Readings on CC2538\label{CoapTiming}}
 	\input{tbl/coapsensors.tex}
-	\caption{CoAP Response Latency for Sensor Readings on CC2538\label{CoapTiming}}
 \end{table}
@@
 \begin{table}
-	\center
+	\centering
+	\caption{PING Response Latency\label{PingResponse}}
 	\input{tbl/pingresponse}
-	\caption{PING Response Latency\label{PingResponse}}
 \end{table}
@@
 	\center
-	\includegraphics[width=\textwidth]{fig/PingProbe_Theory.png}
 	\caption{Variations in Response Time\label{FingerprintTheory}}
+	\centerline{\includegraphics[width=\textwidth]{fig/PingProbe_Theory.png}}
 \end{figure}
@@
 
-\begin{figure}[!h]
+\begin{figure}
 	\centering
-	\includegraphics[width=\textwidth]{fig/PRI_hl.png}
 	\caption{Example PRI\label{ExamplePri}}
+	\centerline{\includegraphics[width=\textwidth]{fig/PRI_hl.png}}
 \end{figure}
@@
 
-\begin{figure}[!h]
+%\begin{figure}
+%	\centering
+%	\begin{subfigure}{width=0.45\textwidth}
+%		\includegraphics[width=\textwidth]{fig/helloworld_cc2538.png}
+%		\caption{PRIs of helloworld\label{HelloworldPriNormal}}
+%	\end{subfigure}
+%	\begin{subfigure}{0.45\textwidth}
+%		\includegraphics[width=\textwidth]{fig/helloworld_cc2538_outlier.png}
+%		\caption{PRIs outliers of helloworld\label{HelloworldPriOutliers}}
+%	\end{subfigure}
+%	\caption{helloworld PRIs\label{HelloworldPri}}
+%\end{figure}
+
+\begin{figure}
 	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\includegraphics[width=\textwidth]{fig/helloworld_cc2538.png}
-		\caption{PRIs of helloworld\label{HelloworldPriNormal}}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\includegraphics[width=\textwidth]{fig/helloworld_cc2538_outlier.png}
-		\caption{PRIs outliers of helloworld\label{HelloworldPriOutliers}}
-	\end{subfigure}
+	\subfigure[PRIs of helloworld\label{HelloworldPriNormal}]
+	{
+		\includegraphics[width=0.45\textwidth]{fig/helloworld_cc2538.png}
+	}
+	\subfigure[PRIs outliers of helloworld\label{HelloworldPriOutliers}]
+	{
+		\includegraphics[width=0.45\textwidth]{fig/helloworld_cc2538_outlier.png}
+	}
+%	\begin{subfigure}{0.45\textwidth}
+%		\includegraphics[width=\textwidth]{fig/helloworld_cc2538_outlier.png}
+%		\caption{PRIs outliers of helloworld\label{HelloworldPriOutliers}}
+%	\end{subfigure}
 	\caption{helloworld PRIs\label{HelloworldPri}}
@@
 \appendix
-\input{appendix}
 %And this is my Appendix.
@@
 %\nocite{*} % add all entries from sample.bib
+
+\subsection*{Fingerprint Experiment Programs}
+\FloatBarrier
+\begin{table}
+	\centering
+	\caption{Fingerprint Experiment Programs \label{FingerprintApps}}
+	\input{tbl/PingProbeExperiments.tex}
+\end{table}
+\FloatBarrier
+
+\subsection*{Fingerprint Experiment Relative KS-Distances}
+\FloatBarrier
+\begin{sidewaystable}
+	%\footnotesize
+	\centering
+	\caption{
+		Relative KS-Distances of Experimented Fingerprints (Multiplied by 100 for readability. Indexes refer to \Cref{FingerprintApps} 
+		Minimum in each row marked as \textbf{bold}.) \label{ksdistances}
+	}
+	\input{tbl/ksdistance.tex}
+\end{sidewaystable}
+\FloatBarrier
 

### 2017-11-21 Writing/rsptime.tex

--- 2017-04-05 Writing/rsptime.tex
@@
-\section{Response Time}
-Response time is another major feature exploited in Internet traffic analysis attack.
-Again we would expect the same attacks can be applied to 6LoWPAN traffic and works even better than their counterparts against Internet traffic, as the accuracy of timing measurements can be greatly improved for 6LoWPAN traffic.
+\section{Exploiting Response Time Information\label{sec: ResponseTime}}
 
-Firstly, the devices are physically close to each other and uses RF to communicate. The adversary can remove the RTT noises by measure the packets on the server side.
+The response time is another major feature that has been previously exploited in Internet traffic analysis attacks.
+Like in the case of exploiting packet lengths, we would expect that the same attacks (as in the classical Internet setting) can be applied to 6LoWPAN traffic.
+Indeed, like in the previous section, we would expect that they will work even better because the accuracy of timing measurements can be greatly improved for 6LoWPAN traffic: this is because there are fewer noise sources in the traffic, the devices are physically close to each other and uses RF to communicate, the adversary can remove the RTT noises by measure the packets on the server side, and the performance of the constrained devices is low and hence gives a better resolution of the execution time.
 
-Secondly, performance of the constrained devices are low; hence gives a better resolution on timing code execution.
+\subsection{Distinguishing Different Sensors}
+The first application of timing analysis that we describe is to distinguish between different sensors that are accessed on a device.
+For this purpose we set up an experiment on a CC2538, which has three on-board sensors: Vdd, temperature, and an Ambient Light Sensor (short ALS).
+We access these via CoAP\cite{rfc7252}, which is a protocol designed for constrained devices that provides an universal interface for accessing resources.
+CoAPs is the secure version which stands for CoAP with DTLS.
 
-\subsection{Different Sensors}
-%Plaintext recovery.
-%\begin{itemize}
-%	\item Reading different sensors takes different time.
-%	\item Requirement: needs to identify CoAPS packets.
-%	\item Works on both 802.15.4 Seuciryt and DTLS, if the requirement is met. 
-%\end{itemize}
+Due to the different physical characteristics of the sensors, there could be a variance of time that is required for reading the measurements.
+We investigated whether such variances could be observed through the packet response latency.
+If this was the case, then an adversary could learn the nature/purpose of sensors on a network by observing their response time.
 
-CoAP\cite{rfc7252} is a protocol designed for constraied devices that provides an universal interface for accessing resources. CoAPs is the secure version which stands for CoAP with DTLS.
-
-Due to the different physical characters of sensors, there could be a variance of time when reading the measurements.
-The idea is to investigate whether such variance can be observed through the packet response latency.
-
-We implemented the experiment on CC2538, using all three sensors from ``cc2538-demo", namely Vdd, temperature and Ambient Light Sensor (ALS).
+We thus set up an experiment on CC2538, using all three sensors from ``cc2538-demo".
 We used CoAP from the ``er-rest-example" in the Contiki OS source code, as there is no CoAPs implementation available.
-
-Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result would hold even in case of CoAPs.
-
-We have carefully crafted other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.
+Although DTLS processing would definitely have an impact on the response latency, we argue that such impact would be independent to the sensors being accessed; hence similar result can be equally expected for CoAPs.
+We carefully controlled other factors, including URIs, data representation and code flow, to be uniform for all three sensors in order to guarantee a controlled environment.
 
@@
 \Cref{CoapTiming} summarises the result.
-It is shown that ALS takes about $2$ms longer and hence can be easily distinguished.
-Vdd and temperature might be difficult to distinguish by response latency as they have similar results.
+It shows that ALS takes about $2$ms longer and hence can be easily distinguished.
+Vdd and temperature have much more strongly overlapping distributions, and thus are more difficult to distinguish.
+Nevertheless these results confirm  our hypothesis: different sensors have different latencies and these leak through the response time.
+An adversary who is interested in finding out information about devices on a network might thus be able to match the (known) behaviour of `interesting' sensors to what they observe on the network.
+We remark that this could be useful even in the setting where the sensors transmit their data unencrypted: after all they might return only some reading without a unit of measurement; thus seeing their return data might not as such reveal their nature.
 
-\subsection{Different Hardware}
+\subsection{Distinguishing Different Devices}
 %Gain hardware information.
@@
 
-A more general leakage is the response latency to a specific message, as different processors would have different computational power and thus different time to process a same message.
-The ICMP messages turns out to be suitable for this attack since they are standardised and thus universally supported.
-Among the ICMP messages, PING is especially ideal for two reasons:
+As we observed before, different devices have different underlying hardware and thus different computational power.
+This implies that there could be the potential that different devices take different amounts of time to process the same message.
+Because ICMP messages are standardised, they are particularly suitable for this purpose.
+Among the different ICMP messages, PING is especially ideal for two reasons:
 \begin{enumerate}
@@
 
-\subsection{Running Code Fingerprint}
+\subsection{Distinguishing Programs}
 %Fingerprints the code running on a device, which leads to plaintext recovery.
@@
 %\end{itemize}
-The response time of packets could also be exploited to fingerprint the code running on a specific device.
 
-\subsubsection{Hypothesis}
+We remarked before that the functionality of a sensor is potentially valuable information.
+For instance some sensors might be predominantly passive, e.g.
+they might read the temperature and report it back periodically, whereas some sensors might control something upon receiving commands.
+Thus knowing the functionality enables an adversary to make (more) sense of the observed traffic in the network.
+This could be done if a `fingerprint' could be produced for different programs.
+From an adversary's perspective a positive result would imply that they could `fingerprint' products which are on the market and thus use this information to infer what program is running on a target device.
+
+% program executing on the target is a valuable information in aspect of security and privacy, as it determines functionality of a device and therefore the contents of encrypted packets associated.
+For instance, knowing a target being an actuator that controls an air conditioner immediately suggests a packet directed to it might  be a controlling command.
+
+%Our study shows that the response time of packets could also be exploited to reveal information of the program target is executing.
+To be more specifically, an adversary can collect ``fingerprints'', which we explain in the following section, from products available on the market and then use this information to breach the program running on a target device.
+
 %How it works
-\Cref{FingerprintTheory} illustrates two sensors receiving a same service request.
-Sensor Node 1 was idle and hence responded immediately, whilst Sensor Node 2 postponed the request for reading a sensor.
-From the aspect of packets, the response time on Sensor Node 2 would appear longer than that of Sensor Node 1.
+To illustrate why this might work, we now look at \Cref{FingerprintTheory}.
+It illustrates two sensors receiving the same service request.
+In our example, at the time of receiving the request, Sensor Node 1 was idle and hence responded immediately, whilst Sensor Node 2 postponed the request for reading a sensor.
+Clearly, the response time on Sensor Node 2 would appear longer than that of Sensor Node 1.
 
@@
 
-Most sensors are programmed in a loop; therefore the same code fragments are repeated through the life time of a sensor.
-Each code fragment takes different time to execute and hence extends response time differently.
+In real life, most sensors are programmed in a loop; therefore the same code fragments are repeated through the life time of a sensor.
+Each code fragment takes different time to execute and hence the response times vary.
+This behaviour could be statistically analysed and the resulting distribution could be stored as a `fingerprint' .
 
-The code fingerprinting attack exploits this phenomenon by statically analysing the distribution of extended response time to reveal information of the program.
-
-\begin{definition}
-	We refer the distribution of extended response time as a \textbf{``fingerprint''} to the program running on the sensor node.
-\end{definition}
-
-For this attack, we assume the adversary has the pre-knowledge of potential programs, together with a database of all their fingerprints.
-To identify an unknown program running on target sensor, the adversary collects its fingerprint and then matches it to the database.
-
-To effectively launch the attack, the adversary also needs to be able to send the requests. Further more, requests with short predictable processing time are preferable as they induce less noise.
+For this fingerprinting scenario, we must assume the adversary has the pre-knowledge of potential programs and can fingerprint them (or that they have access to a database that contains this information).
+To identify an unknown program running on target sensor, the adversary collects a new fingerprint and then matches it to available fingerprints.
+Clearly, to effectively launch the attack, the adversary needs to be able to send the request to a targeted sensor (requests with short predictable processing time are preferable as they induce less noise).
 
@@
 
-\subsubsection{Extracting Fingerprint}
-The first task of the attack is to construct a fingerprint of a program. We experimented with PING on CC2538 running Contiki OS.
+\subsubsection{Extracting Fingerprints}
+We explored the feasibility of fingerprinting programs on an CC2538 running Contiki OS by using the PING command.
 
@@
 Contiki MAC\cite{ContikiMAC} sends duplicated PING requests.
-The response time, refers to PING Response Interval, PRI, is defined to be the time between a PING response and its last paired request.
-The highlighted Packet 205 and Packet 203 shows such an example.
+The response time, which refers to PING Response Interval, PRI, is defined to be the time between a PING response and its last paired request.
+The highlighted Packets 205 and 203 shows such an example.
 
@@
 We further plotted the upper outliers, mostly ranged [12, 2000]ms, in \Cref{HelloworldPriOutliers}.
-We suppose these outliers corresponds to the extended response time as depicted by Sensor Node 2 in \Cref{FingerprintTheory}.
-According to the hypothesis, the distribution described by \Cref{HelloworldPriOutliers} is the fingerprint of the ``helloworld'' example.
+Unfortunately we do not have a solution to investigate the exact cause of such delay, as we were unable to control the code execution that requires environmental interaction within a timing critical context.
+Nevertheless, we suppose these outliers correspond to the extended response time as depicted by Sensor Node 2 in \Cref{FingerprintTheory}.
+The distribution described by \Cref{HelloworldPriOutliers} is the fingerprint of the ``helloworld'' example.
 
-The result in \Cref{HelloworldPri} showed a clear gap between the usual PRIs and extended PRIs.
+The result in \Cref{HelloworldPri} shows a clear gap between the usual PRIs and extended PRIs.
 In fact other applications we experimented also showed the same property.
-This implies that an adversary can easily draw a threshold by observing the whole PRI distribution and then filters the fingerprint.
+This implies that an adversary can easily draw a threshold by observing the whole PRI distribution and then filter out the fingerprint.
 In our experiments the threshold is set to 12ms but any other values within the gap would also work.
+
+We collected the fingerprints for three programs taken from the Contiki OS examples:
+\begin{description}
+	\item[broadcast] This program periodically broadcasts a constant message.
+
+	\item[powertrace] This program records the power consumption and broadcasts a constant message.
+
+	\item[Sensorpayload] This program is based on the ``er-rest-example'' embedded together with sensor accesses taken from ``cc2538-demo''.
+It captures a real case scenario where three different sensors, namely Temperature, Vdd and ALS, are being accessed through CoAP.
+\end{description}
+
+Specifically for ``Sensorpayload'' we collected fingerprints for 8 different scenarios where different sensors are being accessed.
+For each program we independently collected 2 fingerprints for comparison.
+
+\Cref{FingerprintApps} summarises the total 20 fingerprints we collected for the experiment.
 
@@
 %Comparing the distribution.
-Following the hypothesis, we expect a distinctive outlier PRI distribution for each different program running on the target device which can be used as a fingerprint to the program being ran.
-To identify an unknown program r
+
+During the experiments we realised that most of the fingerprints do not adhere to common distributions; therefore we used a non parametric test, the Kolmogorov-Smirnov Distance\cite{KsTest}, as our test statistic.
+This is a well understood statistic with previous uses in side channel analysis\cite{KsDistanceDistinguisher}.
+\Cref{ksdistances} summarises the relative KS distances computed on each pair of fingerprints in our experiments.
+
+Although fingerprints collected on the same application were rejected by the Kolmogorov-Smirnov Test, we noticed that their KS distance tends to be smaller comparing to fingerprints collected on different programs, as the \textbf{bold} cells marked in \Cref{ksdistances}.
+
+By adapting our distinguisher to utilise the minimum KS distance, we were able to identify 13 out of 20 fingerprints successfully.
+The `overlapping' fingerprints are mainly due to the ``Sensorpayload'' program, which access different sensors, but otherwise has identical program code.
+Thus we did expect that the different instantiations of it would lead to very similar fingerprints.
